---
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    citation_package: natbib
    keep_tex: true
    includes:
      after_body: appendix.md
papersize: a4
mainfont: Times New Roman
bibliography: Bibliography.bib
biblio-style: chicagoa
csl: journal-of-financial-economics.csl
link-citations: yes
fontsize: 12pt
geometry: [top=3cm, bottom=2.5cm, right=2.5cm, left=2.5cm]
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{dcolumn}
- \usepackage{amsmath,amsthm}
- \usepackage{rotating}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{caption}
- \usepackage{tabularx}
- \usepackage{hhline}
- \usepackage{fixltx2e}
- \usepackage{hyperref}
- \usepackage{tocloft}
- \usepackage{appendix}
- \usepackage{hyperref}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{mwe}
---

\captionsetup{labelfont=bf}
\newcommand\mycaption[2]{\caption{\textbf{#1}\newline\scriptsize#2}}

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

```
\pagenumbering{roman}
\setcounter{page}{3}
\renewcommand*{\contentsname}{Table of Contents}
\tableofcontents
\renewcommand\cftlottitlefont{\normalsize\bfseries}
\renewcommand\cfttabfont{\small}
\renewcommand{\cfttabpresnum}{Table }
\setlength{\cfttabnumwidth}{5em}
\renewcommand\cfttabpagefont{\small}
\listoftables
\renewcommand\cftloftitlefont{\normalsize\bfseries}
\renewcommand{\cftfigfont}{\small}
\renewcommand{\cftfigpresnum}{Figure }
\setlength{\cftfignumwidth}{5em}
\renewcommand{\cftfigpagefont}{\small}
\listoffigures
\clearpage
\pagenumbering{arabic}

# 1 Introduction

Information asymmetry is a fundamentally important concept in finance and economics, since it influences most interactions between market participants, especially in cases of adverse selection and moral hazard. It is of particular interest to financial economists, as the fundamental purpose of financial markets is to aggregate dispersed information into market prices. Hence, it is crucial to understand the effects of information asymmetry on trading behavior of investors and as a result, on the outcomes and operation of securities markets.

The presence of foreign investors has increased prominently in recent decades. For instance, according to the NYSE Fact Book, foreign ownership in US stocks has grown from 3% in 1970 to 11% in 2001. As a result, foreign ownership has drawn an interest from researchers and the existing literature provides studies of the effects of foreign investments on productivity, investment and growth of invested firms [@henry2000stock; @bekaert2005does; @bekaert2011financial] and also on stock price properties like liquidity, return volatility and the cost of capital [e.g. @bekaert2000foreign; @bae2004investibility; @bekaert2007liquidity]. Most of the existing literature finds an inverse relation between asymmetric information and foreign ownership [e.g. @jiang2004foreign; @baik2013liability; @batten2015foreign]. Furthermore, foreign investors tend to prefer stocks that have characteristics associated with low information asymmetry, such as large size and low leverage [@kang1997there; @dahlquist2001direct; @batten2015foreign].

Despite the findings of the relationship between information asymmetry and foreign ownership, there are different interpretations of the causal effects of these two variables. For instance, in the inverse relationship case, @jiang2004foreign argue that foreign investors are attracted to stocks with low information asymmetry, since they avoid stocks with cross-corporate holdings. In contrast, @choi2013foreign argue that the positive relationship of these variables is due to large foreign shareholders' positive contribution to stock price informativeness. However, the studies lack a credible identification strategy of the causal effect and thus, this thesis is a first attempt, to the best of my knowledge, to examine the causality, using the quasi-natural setting of brokerage closures by  @kelly2012testing. Accordingly, I construct a difference-in-differences estimation, using the findings of @kelly2012testing and @derrien2013real that an exogenous decrease in analyst coverage due to these brokerage closures increase the asymmetric information of the covered firms. As a dependent variable, I use various proxies for information asymmetry suggested by the existing literature.

# 2 Literature review

## 2.1 Information asymmetry and analyst coverage

Earlier literature studies asymmetric information in financial markets by examining the strategic behavior of investors. @kyle1985continuous studies the strategic behavior of investors by a market microstructure model in which uninformed trades follow Brownian motion and market makers see only the order imbalance which they fill with matching orders that are crossed at the market-clearing price. Orders are batched and therefore there are no bid and ask prices. The optimal trading behavior for the single informed investor is to exploit his information on trades gradually. In contrast, @glosten1985bid propose a microstructure model in which uninformed orders arrive as a Poisson process and orders are executed individually by market makers. They argue that due to informed investors, there is a positive bid-ask spread even when the market maker is risk-neutral and makes zero profits. 

Several researchers have developed various measures to estimate the magnitude of information asymmetry. Easley et al. (1996) use a market microstructure model inspired by @glosten1985bid in which trade order flows affect the beliefs of market participants. The information of trade order flow is analyzed to estimate the magnitude to which trade order flows convey different information for different securities. As a result, they construct the well-known measure of the probability of informed trading (PIN) of which different researchers have developed various versions [e.g.  @brown2004conference; @brown2007disclosure; @duarte2009pin; @easley2010factoring]. @johnson2017simple assume that informed investors trade more in options than uninformed investors. Based on the premise, they construct the multimarket information asymmetry (MIA) measure with daily trading volume data of stocks and options. @lof2018asymmetric propose an easily computed measure of volume coefficient variation (VCV). They argue that orders of uninformed (informed) liquidity seekers are uncorrelated (perfectly correlated) and informed orders need to be matched by market makers. From the distribution of total trading volume, they construct functions of the proportion of informed trade and show that the coefficient of variation (the ratio of standard deviation to the mean) of trading volume increases monotonically in the proportion of informed trade.

A great amount of literature finds that equity research analysts produce relevant and valuable information for investors and firms [e.g., @womack1996brokerage; @barber2001can; @jegadeesh2004analyzing; @loh2010analyst]. Furthermore, as providers of information of the covered firms, analysts are also monitoring these firms [@moyer1989security; @chung1996impact] and they help to reduce information asymmetry [@bushman2001financial; @healy2001information]. Accordingly, @kelly2012testing find in a quasi-natural research setting that an exogenous decrease in analyst coverage of a firm results in an increase of information asymmetry. Subsequently, many researchers have applied the setting of @kelly2012testing to study the effects of exogenous variation in analyst coverage on corporate policies [@derrien2013real], innovation [@he2013dark] and corporate tax aggressiveness [@allen2016analyst].

## 2.2 Foreign ownership and information asymmetry

Foreign investors are generally thought to be less informed of local stock markets than local investors among finance practitioners and academics. Domestic investors are found to have better information and support from regulators. For instance, the home bias, the volatility of capital flows and herding among foreign investors are explained to be due to superior information of domestic investors as well as to regulators’ bias against foreign investors [@choe2005domestic]. Although the literature of early 2000s provides some opposite evidence of information asymmetry between domestic and foreign investors [@grinblatt2000investment; @seasholes2000smart], the most recent studies support the traditional view that foreign investors are at an information disadvantage compared to domestic investors [@hau2001location; @choe2005domestic; @dvovrak2005domestic]. 

Compared to large literature of describing information advantages of domestic and foreign investors, the relationship of foreign ownership and information asymmetry is less studied. @choi2013foreign report that high foreign ownership is associated with high information asymmetry in Chinese markets using a bid-ask spread as a proxy for information asymmetry. Similarly, @he2013large use a well-known measure of the probability of informed trading (PIN) and price non-synchronicity as proxies for information asymmetry when examining the connection between foreign ownership and information asymmetry with a cross-sectional data set of firms in 40 markets in 2002. They find, as well, that firms with large foreign ownership typically have more information-intensive stock prices (i.e. high information asymmetry). Based on their theoretical arguments and informal Granger causality test of one-year cross-sectional setting, authors argue that large foreign ownership contributes to information asymmetry. 

In contrast to the positive relation between foreign ownership and asymmetric information, @kang1997there find that in Japanese markets foreign investors prefer significantly less smaller firms than domestic investors, which they argue to be due to larger information asymmetry in small stocks between foreign and domestic investors. Similarly, @dahlquist2001direct find in Swedish markets that foreign investors prefer relatively more firms with comfortable characteristics such as large size due to information asymmetry factors. Furthermore, @jiang2004foreign find evidence of inverse relation between foreign ownership and information asymmetry in Japanese markets. They focus on the relation between the level of foreign shareholdings and a measurable consequence of information asymmetry of which they use the timing and magnitude of intertemporal return-earnings associations. Moreover, they provide evidence that foreign investors tend to avoid stocks with high cross-corporate holdings. 

Most recently, @batten2015foreign find evidence of the inverse relation between foreign ownership and asymmetric information in Vietnamese markets. They find similarly as @kang1997there and @dahlquist2001direct supporting evidence of foreign investors holding shares in firms with familiar attributes to overcome information asymmetries. Moreover, @baik2013liability find foreign investors' stronger preference for low information asymmetry stocks in the US markets. They measure information asymmetry based on a firm's size, return volatility, analyst forecast dispersion and R&D intensity of which they construct a single asymmetric information factor by principal component analysis.

I contribute to the existing literature by examining the relationship of foreign ownership and information asymmetry not just with a panel regression but also with a difference-in-differences research setting of brokerage closures [@kelly2012testing] which cause an exogenous shock to the analyst coverage of a firm’s stock. @kelly2012testing and @derrien2013real argue that an exogenous decrease in analyst coverage causes an increase in information asymmetry of the covered firm. As a result, the research setting of brokerage closures enables me to assess the causal effect between information asymmetry and foreign ownership. Previous studies of information asymmetry and foreign ownership [@jiang2004foreign; @choi2013foreign; @he2013large] do not examine causality profoundly, which makes this thesis a first attempt, to the best of my knowledge, to study the causal effect of information asymmetry on foreign ownership. In addition, I test the general relationship of these two with panel regressions by using various proxies for information asymmetry such as PIN by various researchers [@brown2004conference; @brown2007disclosure; @duarte2009pin; @easley2010factoring], MIA [@johnson2017simple] and VCV [@lof2018asymmetric].


# 3 Hypotheses

In this thesis, I study the effect of information asymmetry on foreign ownership in US stock markets. In particular, I examine how the foreign ownership of US stocks are affected by an exogenous reduction in analyst coverage using a credible quasi-natural experiment of brokerage closures [@kelly2012testing]. Moreover, I test the general relationship of foreign ownership and information asymmetry with alternative proxy measures for information asymmetry in a panel regression setting. Based on these research settings, I construct the following hypotheses:

*H1: Stocks with higher information asymmetry are associated with low foreign ownership*

*H2: An exogenous increase in information asymmetry of stocks results in a decrease of foreign ownership*

*H3: The reduction of foreign ownership due to an exogenous information asymmetry shock is emphasized in stocks with low institutional ownership and analyst coverage*

The first hypothesis is mainly supported by the existing literature. @kang1997there and @dahlquist2001direct find that foreign investors prefer relatively more firms with characteristics associated with low information asymmetry, such as firm size. @jiang2004foreign find an inverse connection between foreign ownership and information asymmetry using the timing and magnitude of intertemporal return-earnings associations in Japanese markets. Moreover, recent studies by @baik2013liability and @batten2015foreign find inverse relation between the variables in the US and Vietnamese markets, respectively.

Although the existing literature supports the hypothesis of the inverse relation between information asymmetry and foreign ownership, few studies address the causal relationship of these two variables directly as described in the second hypothesis. Based on their overall results, @jiang2004foreign argue that foreign investors are attracted to firms with low information asymmetry in Japanese markets. @he2013large provide opposing results of positive relation and interpret these results to be due to a view that foreign investors contribute positively to the informativeness of stock prices. However, they point out that the potential reverse causality may drive their results but find it conceptually less likely. They argue that foreign investors could improve corporate governance and disclosure policies of firms of the invested firms. In the spirit of Granger causality test, they run a predictive regression with a one-year lag of dependent variable and find results to be consistent with foreign ownership Granger-causing price informativeness. @batten2015foreign find in Vietnamese markets that foreign investors prefer firms of which characteristics are associated with low information asymmetry, such as large size, low leverage and high book-to-market ratio to overcome the information disadvantage compared to domestic investors. Furthermore, their finding is in line with previous studies of home bias that find foreign investors preferring firms with comfortable characteristics like large size or low leverage [@kang1997there; @dahlquist2001direct].

The existing literature finds that institutional investors can act as active monitors of management by directly intervening in a firm’s operations [@shleifer1986large; @gillan2003corporate; @ferreira2008colors]. As a result of monitoring, information asymmetry of a stock is reduced. Accordingly, less uninformed investors like foreign investors consider institutional ownership as a convincing signal that information asymmetry risk of a given stock is mitigated [@luong2015]. Similarly, @lof2018asymmetric argue that an exogenous decrease of analyst coverage is a greater shock for a firm that initially has a low analyst coverage. Hence, the third hypothesis is largely supported by existing literature.

# 4 Data

In this section, I describe how I select and construct the variables of the baseline sample which is used in examining the general relation between foreign ownership and information asymmetry. In addition, I describe the data processing of quasi-natural experiment sample which is used in testing the causal effect between the aforementioned variables. I also provide summary statistics of these.

## 4.1 Sample selection

The baseline sample examined in this study includes US listed firms during the period of 1997-2017. Data for foreign, domestic and institutional shareholdings is retrieved from Thomson Reuters institutional holdings (form 13F) database. To calculate the stock price related control variables, the information asymmetry proxies *BA_SPREAD*, *VCV* as well as foreign and institutional ownership measures, I gather stock price information from the Center for Research in Security Prices (CRSP). Accounting related control variables are collected from COMPUSTAT. The 13F data is merged with CRSP by matching the 8-digit CUSIP identifier from 13F to the 8-digit NCUSIP from CRSP. I use CRSP-COMPUSTAT Merged Database (CCM) to merge CRSP and COMPUSTAT datasets. Firm-year estimates of information asymmetry proxies *PIN~BHL~* [@brown2004conference], *PIN~BH~* [@brown2007disclosure], *PIN~EHO~* [@easley2010factoring], *PIN~DY~* [@duarte2009pin], *PIN~DY_ADJ~*, *PSOS~DY~* and firm-day estimates of *MIA* [@johnson2017simple] are collected from the cited authors’ websites [^1]. Information asymmetry measures are merged with the baseline sample by using the CRSP’s Permanent Issue Number (PERMNO) as a linking identifier. The baseline sample selection process ends up with firm-year observations.

[^1]:Firm-year observations of *PIN~BHL~*, *PIN~BH~*, *PIN~DY~*, *PIN~DY_ADJ~*, *PSOS~DY~* and *PIN~EHO~* are made available
by Stephen Brown (http://scholar.rhsmith.umd.edu/sbrown/pin-data), Jefferson Duarte (http://www.owlnet.rice.edu/~jd10/) and Søren Hvidkjær (https://sites.google.com/site/hvidkjaer/data), respectively. Daily firm-level observations of *MIA* are made available by Travis Johnson (http://travislakejohnson.com/data.html).

The quasi-natural experiment sample includes US listed firms during the period of 1997-2010. Similar to baseline setting, I collect institutional ownership data from 13F, stock price related variables from CRSP and accounting related variables from COMPUSTAT. In addition, I use the list of brokerage closures in Appendix A of @kelly2012testing and analyst coverage data from Institutional Brokers’ Estimate System (IBES) to identify stocks that experience exogenous reductions in analyst coverage due to these brokerage closures. Since the quasi-natural experiment sample does not involve aforementioned information asymmetry measures, the sample selection process ends up with firm-quarter observations.

## 4.2 Constructing the variables

I extract foreign ownership data from Thomson Reuters institutional holdings (form 13F) s34 master file. I define firm-quarter level shareholdings as foreign by taking the sum of all the institutional shareholdings where the institution's country is other than the US. Then, I follow @glushkov2009institutional to match the 13F data with CRSP's monthly file and taking into account the adjustments for shares outstanding from CRSP. Similarly, I define institutional ownership variables of CRSP stocks with no 13F data as zero. Finally, I define two variables *FOR_OWN* and *FOR_BREADTH* of which the former is defined as an annual average of the shares of a firm held by foreign institution at the end of each quarter divided by the firm’s total shares outstanding (CRSP) at the end of each quarter. The latter is defined as an annual average of the number of distinct foreign institutions holding shares in the firm at the end of each quarter divided the total number of institutions in the 13F database at the end of each quarter [@chen2002breadth; @lof2018asymmetric]. I also construct the variables for total institutional ownership *INST_OWN* and *INST_BREADTH* in a similar manner.

In addition to these market level ownership measures, I define two variables to examine foreign institutional investors' ownership against total institutional investors' ownership. *FOR_TO_INST_OWN* is defined as an annual average of a firm's shares held by foreign institution at the end of each quarter divided by shares held by total institutions at the end of each quarter. *FOR_TO_INST_BREADTH* is defined as an annual average of the number of foreign institutions holding shares in the firm at the end of each quarter divided by the number of total institutions holding shares in the firm at the end of each quarter. 

I notice that there are some observations of *INST_OWN* and *FOR_OWN* where the shares held by institutions exceeds shares outstanding. This is a known limitation of the 13F data. Institutional investors are not required to report their short selling positions, which is a plausible explanation for the issue [@lewellen2011institutional]. To mitigate the problem, I follow @lewellen2011institutional and winsorize all the ownership variables at the top to a maximum of 1. In comparison of the firm-year level data set in the baseline research setting, I construct the variables for the quasi-natural research sample similarly but at the firm-quarter level.  

I obtain data for information asymmetry measures of annual firm-level PIN (*PIN~BHL~*, *PIN~BH~*, *PIN~EHO~*, *PIN~DY~* and *PIN~DY_ADJ~*), *PSOS~DY~* and daily firm-level *MIA* observations from the cited researchers’ publicly available websites and CRSP. I construct the firm-year observations of *MIA* by calculating the annual average of daily observations for each firm. Data for bid-ask spread is collected from CRSP and I define *BA_SPREAD* as the annual average of the daily observations of difference in ask and bid price divided by closing price. Data for proxy measure VCV is retrieved from CRSP daily stock file. Following Lof and van Bommel (2018), I construct the annual firm-level observations of VCV by computing the fraction of the annual standard deviation of daily trading volumes and the annual average of daily trading volumes. I require firms to have at least 200 days with a positive trading volume in a year. Similarly, I calculate the *VCV* using three different measures of trading volume: volume in US dollars (*VCV~USD~*), volume market shares (*VCV~MKT~*) and turnover (*VCV~TO~*).

I gather control variables data from COMPUSTAT quarter fundamentals and CRSP monthly stock files. To make CRSP and COMPUSTAT variables comparable, I convert monthly CRSP data to quarter level by taking the last non-missing estimate for a stock in each quarter of the given variable. Using CRSP, I compute *LOG_MKT_CAP* by multiplying market price of each stock by the shares outstanding at the end of each quarter, converting it to an annual average and taking the logarithm of this measure. Accounting related control variables are gathered from COMPUSTAT. *BM_RATIO* is an annual average of the stock's book value of equity divided by the market value at the end of each quarter. *LEVERAGE* is an annual average of the stock's total debt divided by total assets at the end of each quarter. *ROA* is an annual average of the stock's net income divided by total assets at the end of each quarter. I use two-digit SIC codes from CRSP to capture the corresponding industry for each stock. I report a detailed list of variables and definitions in Table \ref{table_variable_definitions} in Appendix.

## 4.3 Identification of the quasi-natural experiment

For the quasi-natural experiment, I limit the time period of the baseline sample to 1997-2010 to cover the time period of 22 distinct brokerage closures from June 2000 until November 2007 listed in Appendix A of @kelly2012testing plus three years of pre- and
post-treatment periods. I identify stocks that lose an analyst covering the firm because of the brokerage closures which provide a source of exogenous variation for the analyst coverage. The list is matched with an analyst coverage data retrieved from the Institutional Brokers’ Estimate System (IBES) detail file. 

The identification strategy of the quasi-natural experiment setting by @kelly2012testing is based on argument that in addition to genuine financial distress reasons, brokerage firms respond to adverse changes in revenue making by downsizing or closing their research operations. Hence, the decisions to close research department is driven by business strategy rather than by the characteristics of the firms covered by their analysts. Therefore, the brokerage closure events provide a robust quasi-experimental setting of exogenous reductions in analyst coverage. I also rely on the findings of @kelly2012testing and @derrien2013real that an exogenous decrease in analyst coverage causes an increase in information asymmetry
of the covered firm. @kelly2012testing include also events of the brokerage mergers which require a thorough data processing to eliminate potential endogeneity problems. Dealing with these endogeneity issues is crucial in order to use merger events as a source of exogenous variation. Due to data availability and potential endogeneity issues, I limit my sample of events to include only brokerage closures.

To construct the sample of treated firms, I filter out firms that are not covered by analysts employed in the brokerage houses listed in Appendix A of @kelly2012testing. Following @derrien2013real, I require for the treated firms to be covered by an analyst at least one year before the disappearance dates to filter out firms that are not actively covered by the analysts. Furthermore, following @kelly2012testing and @derrien2013real, I only retain firms for which the analyst has not “stopped” his estimate before the corresponding broker disappearance date to eliminate the potential endogeneity problem. For instance, if an analyst terminates the coverage of firms unrelated to the brokerage closure before the disappearance date (e.g. anticipating changes in corporate policies), the decision is endogenous. I collect the data for stopped estimates from IBES stop file. 

I start the identification of control firms by gathering all distinct firms from IBES detail file. To make groups comparable, I require similarly the potential control firms to be covered by an analyst one year before the disappearance dates to keep only actively covered firms. Second, based on the treatment group, I identify firms that, for a given event, are not affected by the reductions in analyst coverage. Then, I merge IBES data with CRSP, COMPUSTAT and 13F and have a data set of treated and potential control stocks with variables of institutional ownership, stock price and accounting related measures. Moreover, I define the variable *ANALYST_COVERAGE* as the number of distinct analysts covering a firm (source: IBES) in a given quarter.

To construct the final sample of control firms, I follow recent studies [e.g. @allen2016analyst; @bena2017foreign] and use propensity score matching (nearest neighbor) to match each treatment firm to three control firms. *TREATED* is a dummy variable that equals one if a firm is affected by a brokerage closure and zero otherwise. For each brokerage closure, I estimate a logistic regression model with *TREATED* as a dependent variable and averages of three-year pre-event measures of the logarithm of market capitalization (*LOG_MKT_CAP*), book-to-market ratio (*BM_RATIO*) and the number of distinct analysts (*ANALYST_COVERAGE*) as explanatory variables. 

Since brokerage closures tend to extend over several months, the dates listed by @kelly2012testing and corresponding disappearance dates do not coincide completely. Hence, I follow @derrien2013real, @he2013dark and @lof2018asymmetric to construct a three-month gap before and after the event date. As a result, I estimate the dependent variables and explanatory variables for each stock in a given quarter by subtracting (adding) three months from the event date and finding the previous (next) available quarter value for before and after measures, respectively. 

## 4.4 Summary statistics

In this section, I report the summary statistics of sample variables. First, I report the summary statistics of the main variables in baseline setting. Then, I examine the time series development of ownership-specific variables during baseline sample period. Finally, I present the summary statistics of the quasi-natural experiment sample. 

Table \ref{table_summary_baseline} presents the summary statistics of sample variables used in the baseline setting. I report the mean, standard deviation, minimum, first quartile, median, third quartile and maximum of firm-year observations of ownership-specific, control and information asymmetry variables.

```{r, results='asis', message = FALSE, warning=FALSE, eval = FALSE}
library(tidyverse)
library(stargazer)
library(kableExtra)
baseline_regression_raw <- read_rds("results/baseline_regression_raw.rds")

baseline_regression_summary <- baseline_regression_raw %>% 
  select(FOR_OWN, FOR_BREADTH,  INST_OWN, INST_BREADTH, FOR_TO_INST_OWN, FOR_TO_INST_BREADTH,
         LOG_MKT_CAP, BM_RATIO, LEVERAGE, ROA,
         BA_SPREAD, PIN_DY, PIN_DY_ADJ, PSOS_DY, PIN_EHO, PIN_BHL, PIN_BH,
         MIA, VCV_USD, VCV_MKT, VCV_TO) %>% 
  as.data.frame()

stargazer(baseline_regression_summary,
          header = F,
          label = "table_summary_baseline",
          median = T,
          #omit.summary.stat = c("p25", "p75"),
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          column.sep.width = "0pt",
          #no.space = T,
          title = "\\textbf{Summary statistics of the baseline sample}\\newline\\small This table reports summary statistics of firm-year observations of baseline sample variables. Ownership-specific variables are winsorized at the top to a maximun of 1. Control variables, bid-ask spread (\\textit{BA\\_SPREAD})  and different VCV measures are winsorized at the top and bottom by 1\\%. Table \\ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors’ websites.", 
          type = "latex")

```

\renewcommand{\topfraction}{.85}
 \renewcommand{\bottomfraction}{.7}
 \renewcommand{\textfraction}{.15}
 \renewcommand{\floatpagefraction}{.66}
 \renewcommand{\dbltopfraction}{.66}
 \renewcommand{\dblfloatpagefraction}{.66}

\renewcommand\arraystretch{0.70}
\captionsetup{width=1.01\linewidth}
\footnotesize
\begin{longtable}{@{\extracolsep{2pt}}lcccccccc}
  \caption[Summary statistics of the baseline sample]{\textbf{Summary statistics of the baseline sample}\newline\footnotesize This table reports summary statistics of firm-year observations of baseline sample variables. Ownership-specific variables are winsorized at the top to a maximum of 1. Control variables, bid-ask spread (\textit{BA\_SPREAD}) and different VCV measures are winsorized at the top and bottom by 1\%. Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors’ websites.} 
  \label{table_summary_baseline} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{P25} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{P75} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
FOR\_OWN & 110,819 & 0.033 & 0.056 & 0.000 & 0.001 & 0.016 & 0.043 & 1.000 \\ 
FOR\_BREADTH & 110,819 & 0.003 & 0.006 & 0.000 & 0.0005 & 0.001 & 0.004 & 0.060 \\ 
INST\_OWN & 110,819 & 0.438 & 0.316 & 0.000 & 0.140 & 0.409 & 0.718 & 1.000 \\ 
INST\_BREADTH & 110,819 & 0.040 & 0.060 & 0.000 & 0.006 & 0.021 & 0.049 & 0.673 \\ 
FOR\_TO\_INST\_OWN & 109,907 & 0.077 & 0.122 & 0.000 & 0.009 & 0.043 & 0.089 & 1.000 \\ 
FOR\_TO\_INST\_BREADTH & 109,907 & 0.085 & 0.089 & 0.000 & 0.038 & 0.067 & 0.106 & 1.000 \\ 
LOG\_MKT\_CAP & 110,819 & 5.701 & 2.048 & 1.301 & 4.200 & 5.630 & 7.108 & 10.785 \\ 
BM\_RATIO & 110,819 & 0.714 & 0.612 & 0.034 & 0.318 & 0.563 & 0.907 & 3.931 \\ 
LEVERAGE & 110,819 & 0.529 & 0.261 & 0.035 & 0.316 & 0.534 & 0.743 & 1.140 \\ 
ROA & 110,819 & $-$0.012 & 0.064 & $-$0.425 & $-$0.010 & 0.004 & 0.015 & 0.105 \\ 
BA\_SPREAD & 110,819 & 0.046 & 0.030 & 0.003 & 0.024 & 0.037 & 0.059 & 0.175 \\ 
PIN\textsubscript{BHL} & 78,226 & 0.196 & 0.118 & 0.000 & 0.105 & 0.197 & 0.273 & 1.000 \\ 
PIN\textsubscript{BH} & 78,335 & 0.233 & 0.134 & 0.000 & 0.131 & 0.202 & 0.304 & 1.000 \\ 
PIN\textsubscript{DY} & 15,025 & 0.203 & 0.119 & 0.00000 & 0.121 & 0.167 & 0.244 & 1.000 \\ 
PIN\textsubscript{DY\_ADJ} & 15,025 & 0.162 & 0.086 & 0.000 & 0.103 & 0.140 & 0.197 & 0.903 \\ 
PSOS\textsubscript{DY} & 15,025 & 0.284 & 0.156 & 0.000 & 0.177 & 0.233 & 0.346 & 1.000 \\ 
PIN\textsubscript{EHO} & 9,498 & 0.188 & 0.091 & 0.000 & 0.120 & 0.166 & 0.234 & 0.895 \\ 
MIA & 20,813 & 0.416 & 0.106 & 0.014 & 0.351 & 0.422 & 0.477 & 1.000 \\ 
VCV\textsubscript{USD} & 94,888 & 1.305 & 0.854 & 0.370 & 0.704 & 1.081 & 1.614 & 4.986 \\ 
VCV\textsubscript{MKT} & 94,888 & 1.282 & 0.862 & 0.328 & 0.675 & 1.062 & 1.598 & 5.021 \\ 
VCV\textsubscript{TO} & 94,888 & 1.252 & 0.792 & 0.377 & 0.690 & 1.039 & 1.546 & 4.558 \\  
\hline \\[-1.8ex] 
\multicolumn{9}{l}{} \\ 
\end{longtable}
\normalsize

As shown in Table \ref{table_summary_baseline}, the mean and median of foreign institutional ownership (*FOR_OWN*) are 3.3% and 1.6%, respectively. The corresponding measures for total institutional ownership (*INST_OWN*) are 43.8% and 40.9%. The results are mainly in line with the findings of @baik2013liability, who report the mean (median) of 2.62% (2.48%) for foreign ownership and 40.0% (36.5%) for institutional ownership. They use similarly 13F data, but they compute ownership variables with 13F and COMPUSTAT data, compared to 13F and CRSP data in my sample. Moreover, their sample period is 1990-2007 and they report the summary statistics with firm-quarter observations. Hence, our samples are not perfectly comparable. Notably, the minimum (0.0%) and first quartile (14.0%) compared to the third quartile (71.8%) and maximum (100.0%), along with the standard deviation (31.6%), indicate a high variability of institutional ownership. Foreign ownership has similar, but lower variability between firm-quarter observations. 

The summary statistics of information asymmetry are also similar with previous studies. The mean and median of different PIN measures are both approximately 0.20 and the corresponding measures for MIA are 0.416 and 0.422, respectively, which are consistent with the findings of @lof2018asymmetric. Moreover, the means (medians) of different VCV measures are approximately 1.3 and 1.1, respectively, which are consistent with their findings. The control variables are in line with the recent studies that use COMPUSTAT or CRSP data with similar variables and definitions [e.g. @baik2013liability; @allen2016analyst; @lof2018asymmetric]. It is important to note that there are some outliers such as the winsorized maximum (114.0%) of leverage ratio (*LEVERAGE*), which supports the methodology of winsorizing control variables to mitigate the effect of these outliers in regression analysis.

Next, I examine the time series development of foreign and institutional ownership during the sample period of 1997-2017, by plotting the mean of firm-quarter observations of these variables. Figure \ref{figure_baseline_development} presents the results. 

```{r, results='asis', message = FALSE, warning=FALSE, eval = FALSE}
library(tidyverse)

thirteenf_crsp_compustat <- read_rds("results/thirteenf_crsp_compustat.rds")

thirteenf_crsp_compustat %>% 
  mutate(FOR_OWN = foreign_own) %>% 
  group_by(report_date) %>% 
  summarise(FOR_OWN = mean(FOR_OWN)) %>% 
  ungroup() %>% 
  ggplot(aes(x = report_date)) +
  ggtitle("Panel A: Foreign ownership") +
  geom_line(aes(y = FOR_OWN)) +
  labs(x = "Report date", color = "") +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/baseline_development_a.pdf", 
       width = 8, height = 4, units = "in")

thirteenf_crsp_compustat %>% 
  mutate(INST_OWN = institutional_own) %>% 
  group_by(report_date) %>% 
  summarise(INST_OWN = mean(INST_OWN)) %>% 
  ungroup() %>% 
  ggplot(aes(x = report_date)) +
  ggtitle("Panel B: Institutional ownership") +
  geom_line(aes(y = INST_OWN)) +
  labs(x = "Report date", color = "") +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/baseline_development_b.pdf", 
       width = 8, height = 4, units = "in")

thirteenf_crsp_compustat %>% 
  mutate(FOR_BREADTH = foreign_breadth) %>% 
  group_by(report_date) %>% 
  summarise(FOR_BREADTH = mean(FOR_BREADTH)) %>% 
  ungroup() %>% 
  ggplot(aes(x = report_date)) +
  ggtitle("Panel C: Foreign breadth") +
  geom_line(aes(y = FOR_BREADTH)) +
  labs(x = "Report date", color = "") +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/baseline_development_c.pdf", 
       width = 8, height = 4, units = "in")

```

\captionsetup{width=1.0\linewidth}
\begin{figure}[!htb]
\centering
\includegraphics[width = \linewidth]{figures/baseline_development_a.pdf}
\includegraphics[width = \linewidth]{figures/baseline_development_b.pdf}
\caption[Development of foreign and institutional ownership during baseline sample period]{\textbf{Time series development of foreign and institutional ownership during baseline sample period}\newline\small This figure presents the evolution of the mean of firm-quarter observations of foreign ownership (\textit{FOR\_OWN}) in Panel A and institutional ownership (\textit{INST\_OWN}) in Panel B during the baseline sample period of 1997-2017. Firm-quarter observations of these variables are winsorized at the top to a maximum of 1. Sources: CRSP and 13F.}
\label{figure_baseline_development}
\end{figure}

As shown in Panel A, the mean of foreign ownership increases from under 2% in 1997 to almost 6% in 2009, which is followed by a steep decline to approximately 3%. After 2009, foreign ownership increases steadily to ca. 5% in 2017. In Panel B, the mean of institutional ownership increases from 30% in 1997 to approximately 55% in 2008, which is followed by a slight downturn. After 2011, institutional ownership increases steadily to over 55%. Interestingly in Panel A, there is an abrupt drop in foreign ownership during the last quarter of 2003 and a immediate bounce back in the next quarter. In Panel B, there is a similar but relatively much smaller drop during the same quarter. This finding, as well as the overall trend, is in line with the results of @glushkov2009institutional. They present the time series development of the mean of institutional ownership classified into five different size quintiles. The drop in the last quarter of 2003 is more affected in the largest bin of stocks, which is consistent with my findings that foreign investors invest more in larger firms.

Nest, I examine the relation between the sample variables used in baseline setting by a correlation matrix. Table \ref{table_cor_matrix} reports correlations of annual firm-level estimates between the variables used in baseline setting. Each value is a time-series average of within-year correlations (Pearson), which mitigates the effect of potential time series trends between variables. The total sample time period extends from 1997 to 2017. However, this holds true for all variables except *PIN~BH~* (1997-2010), *PIN~DY_ADJ~* (1997-2004), *PIN~EHO~* (1997-2001) and *MIA* (1997-2015).

Variable *FOR_OWN* is negatively correlated with all information asymmetry measures, which is consistent with the first hypothesis. The negative relation is the strongest with the different probability of informed trading measures and the least strong with *MIA*. Moreover, the correlations of *FOR_OWN* with the control variables of different firm characteristics are intuitive and in line with the existing literature. Foreign investors tend to own firms with larger market capitalizations, greater profitability and smaller book-to-market ratios (i.e. value stocks). However, foreign ownership has a positive relation with leverage, implying a preference of more in-debt firms. The relation between foreign ownership and total institutional ownership is positive, indicating that foreign investors have similar stockholdings with institutional investors in general. Accordingly, *FOR_BREADTH* has similar but stronger correlations with other variables than *FOR_OWN*. 

\begingroup
\renewcommand\arraystretch{2.4}
\captionsetup{width=1.51\linewidth}
```{r, results='asis', message = FALSE, warning=FALSE, eval = TRUE}
library(tidyverse)
library(stargazer)
library(kableExtra)
library(huxtable)
baseline_regression_raw <- read_rds("results/baseline_regression_raw.rds")
cor_raw <- baseline_regression_raw %>% 
  select(year, FOR_OWN, FOR_TO_INST_OWN, FOR_BREADTH, FOR_TO_INST_BREADTH, INST_OWN, INST_BREADTH,
         LOG_MKT_CAP:ROA, BA_SPREAD, PIN_BH, PIN_DY_ADJ, PIN_EHO, MIA, VCV_USD) %>%
  mutate(year = as.integer(year))

years <- cor_raw %>% transmute(year = as.integer(year)) %>% distinct() %>% flatten_chr()

filter1 <- function (df, years){
  df %>% 
    filter(year == years) %>% 
    select(-year)
}

cor_dfs_raw <- map(years, ~filter1(cor_raw, .x))

map_na_function <- function(df){
  df %>% 
  map(~.x) %>% 
    discard(~all(is.na(.x))) %>%
    map_df(~.x)
}

cor_dfs <- map(cor_dfs_raw, ~map_na_function(.x))

cor_matrices <- map(cor_dfs_raw, ~cor(.x, use = "pairwise.complete.obs"))

arr <- array(unlist(cor_matrices), c(dim(cor_matrices[[1]]), length(cor_matrices)))

cor_matrices_mean <- round(rowMeans(x = arr, dims = 2, na.rm = T), 2)

cols <- cor_raw %>% select(-year) %>% colnames()

rownames(cor_matrices_mean) <- cols

colnames(cor_matrices_mean) <- cols

cor_matrices_mean[upper.tri(cor_matrices_mean)] <- ""

cor_matrix <- cor_matrices_mean

rownames(cor_matrix) <- c("FOR\\_OWN", "FOR\\_TO\\_INST\\_OWN",
                          "FOR\\_BREADTH","FOR\\_TO\\_INST\\_BREADTH",
                          "INST\\_OWN", "INST\\_BREADTH", "LOG\\_MKT\\_CAP", "BM\\_RATIO", "LEVERAGE",
                          "ROA", "BA\\_SPREAD", "PIN\\textsubscript{BH}", "PIN\\textsubscript{DY\\_ADJ}",
                          "PIN\\textsubscript{EHO}", "MIA", "VCV\\textsubscript{USD}")

kable(cor_matrix, "latex", linesep = "", caption.short = "Correlations between baseline sample variables", caption = "\\textbf{Correlations between baseline sample variables}\\newline\\scriptsize This table reports the correlations between different ownership-specific, information asymmetry and firm-characteristic control variables of the baseline sample. Each correlation estimate is the annual average of the within-year of (Pearson) correlations. Of the information asymmetry measures, I include PIN\\textsubscript{BH}, PIN\\textsubscript{DY\\_ADJ}, PIN\\textsubscript{EHO}, MIA and VCV\\textsubscript{USD}. Ownership-specific variables are winsorized at the top to a maximum of 1 and control variables are winsorized at the top and bottom 1\\%. Table \\ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors' websites. \\label{table_cor_matrix}",
      booktabs = T, align = "c",
      col.names = c("FOR\\_OWN", "FOR\\_TO\\_INST\\_OWN", "FOR\\_BREADTH", "FOR\\_TO\\_INST\\_BREADTH",
                    "INST\\_OWN", "INST\\_BREADTH", "LOG\\_MKT\\_CAP", "BM\\_RATIO", "LEVERAGE",
                    "ROA", "BA\\_SPREAD", "PIN\\textsubscript{BH}", "PIN\\textsubscript{DY\\_ADJ}",
                    "PIN\\textsubscript{EHO}", "MIA", "VCV\\textsubscript{USD}"),
      row.names = T,
      escape = F) %>%
  kable_styling(latex_options = c("scale_down", "hold position"), position = "left") %>%
  landscape()
```
\endgroup

Information asymmetry measures are strongly positively correlated with each other, which is consistent and implies that they capture similar explanatory characteristics. All control variables except *LOG_MKT_CAP* have relatively weak correlations with the information asymmetry measures, which enables me to use them as explanatory variables in a regression model with a low risk of multicollinearity. As a result, I choose to exclude *LOG_MKT_CAP* from subsequent regression models due to a potential risk of multicollinearity. 

Finally, I present the summary statistics of sample variables used in the quasi-natural experiment. Table \ref{table_summary_did} presents the summary statistics of sample variables used in the quasi-natural experiment. I report the mean, standard deviation, minimum, first quartile, median, third quartile and maximum of firm-quarter observations of ownership-specific, control and analyst coverage variables for each group of treatment, control and a whole sample of firms. 

```{r, results='asis', message = FALSE, warning=FALSE, eval = FALSE}
library(tidyverse)
library(stargazer)
library(kableExtra)

did_regression_matched_raw <- read_rds("results/did_regression_matched_raw.rds")

did_regression_summary_treated <- did_regression_matched_raw %>% 
  filter(TREATED == 1) %>% 
    select(FOR_OWN, FOR_BREADTH,  INST_OWN, INST_BREADTH, FOR_TO_INST_OWN, FOR_TO_INST_BREADTH,
         LOG_MKT_CAP, BM_RATIO, LEVERAGE, ROA, ANALYST_COVERAGE) %>% 
  as.data.frame()

stargazer(did_regression_summary_treated,
          header = F,
          label = "table_summary_did",
          median = T,
          #omit.summary.stat = c("p25", "p75"),
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          column.sep.width = "0pt",
          #no.space = T,
          title = "\\textbf{Summary statistics of the quasi-natural experiment sample}\\newline\\small This table reports summary statistics of firm-quarter observations of the quasi-natural experiment sample variables. Control variables are winsorized at the top and bottom 1\\%. Table \\ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.", 
          type = "latex")

did_regression_summary_control <- did_regression_matched_raw %>% 
  filter(TREATED == 0) %>% 
    select(FOR_OWN, FOR_BREADTH,  INST_OWN, INST_BREADTH, FOR_TO_INST_OWN, FOR_TO_INST_BREADTH,
         LOG_MKT_CAP, BM_RATIO, LEVERAGE, ROA, ANALYST_COVERAGE) %>% 
  as.data.frame()

stargazer(did_regression_summary_control,
          header = F,
          label = "table_summary_did",
          median = T,
          #omit.summary.stat = c("p25", "p75"),
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          column.sep.width = "0pt",
          #no.space = T,
          title = "\\textbf{Summary statistics of the quasi-natural experiment sample}\\newline\\small This table reports summary statistics of firm-quarter observations of the quasi-natural experiment sample variables. Control variables are winsorized at the top and bottom 1\\%. Table \\ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.", 
          type = "latex")

did_regression_summary_all <- did_regression_matched_raw %>% 
    select(FOR_OWN, FOR_BREADTH,  INST_OWN, INST_BREADTH, FOR_TO_INST_OWN, FOR_TO_INST_BREADTH,
         LOG_MKT_CAP, BM_RATIO, LEVERAGE, ROA, ANALYST_COVERAGE) %>% 
  as.data.frame()

stargazer(did_regression_summary_all,
          header = F,
          label = "table_summary_did",
          median = T,
          #omit.summary.stat = c("p25", "p75"),
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          column.sep.width = "0pt",
          #no.space = T,
          title = "\\textbf{Summary statistics of the quasi-natural experiment sample}\\newline\\small This table reports summary statistics of firm-quarter observations of the quasi-natural experiment sample variables. Control variables are winsorized at the top and bottom 1\\%. Table \\ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.", 
          type = "latex")

```

\renewcommand\arraystretch{1.0}
\footnotesize
\captionsetup{width=1.0\linewidth}
\begin{longtable}{@{\extracolsep{2pt}}lcccccccc} 
  \caption[Summary statistics of the quasi-natural experiment sample]{\textbf{Summary statistics of the quasi-natural experiment sample}\newline\small This table reports summary statistics of firm-quarter observations of the quasi-natural experiment sample variables. Ownership-specific variables are winsorized at the top to a maximum of 1. Control variables are winsorized at the top and bottom by 1\%. Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.} 
  \label{table_summary_did} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Variable & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{P25} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{P75} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
\multicolumn{9}{@{} l}{\textit{Panel A: All firms}}\\
FOR\_OWN & 231,318 & 0.047 & 0.044 & 0.000 & 0.020 & 0.040 & 0.061 & 1.000 \\ 
FOR\_BREADTH & 231,318 & 0.007 & 0.007 & 0.000 & 0.002 & 0.004 & 0.010 & 0.054 \\ 
INST\_OWN & 231,318 & 0.613 & 0.253 & 0.00000 & 0.437 & 0.652 & 0.812 & 1.000 \\ 
INST\_BREADTH & 231,318 & 0.099 & 0.102 & 0.0003 & 0.036 & 0.068 & 0.124 & 0.684 \\ 
FOR\_TO\_INST\_OWN & 231,318 & 0.079 & 0.075 & 0.000 & 0.039 & 0.065 & 0.096 & 1.000 \\ 
FOR\_TO\_INST\_BREADTH & 231,318 & 0.069 & 0.046 & 0.000 & 0.044 & 0.061 & 0.083 & 1.000 \\ 
LOG\_MKT\_CAP & 231,318 & 7.279 & 1.797 & 1.301 & 6.091 & 7.280 & 8.518 & 10.785 \\ 
BM\_RATIO & 231,318 & 0.555 & 0.485 & 0.034 & 0.262 & 0.441 & 0.693 & 3.931 \\ 
LEVERAGE & 231,318 & 0.530 & 0.250 & 0.035 & 0.330 & 0.537 & 0.722 & 1.000 \\ 
ROA & 231,318 & 0.001 & 0.052 & $-$0.425 & 0.001 & 0.009 & 0.021 & 0.105 \\ 
ANALYST\_COVERAGE & 231,318 & 10.038 & 8.133 & 0 & 4 & 8 & 15 & 50 \\ 
\hline \\[-1.8ex]
\multicolumn{9}{@{} l}{\textit{Panel B: Treated firms}}\\
FOR\_OWN & 58,634 & 0.047 & 0.039 & 0.000 & 0.022 & 0.042 & 0.062 & 1.000 \\ 
FOR\_BREADTH & 58,634 & 0.008 & 0.007 & 0.000 & 0.002 & 0.005 & 0.013 & 0.051 \\ 
INST\_OWN & 58,634 & 0.634 & 0.235 & 0.00000 & 0.484 & 0.672 & 0.813 & 1.000 \\ 
INST\_BREADTH & 58,634 & 0.120 & 0.119 & 0.0004 & 0.042 & 0.080 & 0.154 & 0.684 \\ 
FOR\_TO\_INST\_OWN & 58,634 & 0.075 & 0.061 & 0.000 & 0.041 & 0.065 & 0.095 & 1.000 \\ 
FOR\_TO\_INST\_BREADTH & 58,634 & 0.068 & 0.040 & 0.000 & 0.045 & 0.061 & 0.083 & 1.000 \\ 
LOG\_MKT\_CAP & 58,634 & 7.580 & 1.865 & 1.301 & 6.248 & 7.562 & 8.988 & 10.785 \\ 
BM\_RATIO & 58,634 & 0.551 & 0.506 & 0.034 & 0.248 & 0.425 & 0.686 & 3.931 \\ 
LEVERAGE & 58,634 & 0.512 & 0.249 & 0.035 & 0.309 & 0.517 & 0.698 & 1.000 \\ 
ROA & 58,634 & 0.001 & 0.051 & $-$0.425 & 0.0002 & 0.009 & 0.021 & 0.105 \\ 
ANALYST\_COVERAGE & 58,634 & 12.224 & 9.039 & 0 & 5 & 11 & 18 & 50 \\ 
\hline \\[-1.8ex] 
\multicolumn{9}{@{} l}{\textit{Panel C: Control firms}}\\
FOR\_OWN & 172,684 & 0.047 & 0.046 & 0.000 & 0.019 & 0.039 & 0.061 & 1.000 \\ 
FOR\_BREADTH & 172,684 & 0.006 & 0.006 & 0.000 & 0.002 & 0.004 & 0.009 & 0.054 \\ 
INST\_OWN & 172,684 & 0.605 & 0.259 & 0.00000 & 0.419 & 0.644 & 0.811 & 1.000 \\ 
INST\_BREADTH & 172,684 & 0.092 & 0.094 & 0.0003 & 0.035 & 0.064 & 0.115 & 0.684 \\ 
FOR\_TO\_INST\_OWN & 172,684 & 0.080 & 0.079 & 0.000 & 0.039 & 0.064 & 0.097 & 1.000 \\ 
FOR\_TO\_INST\_BREADTH & 172,684 & 0.069 & 0.048 & 0.000 & 0.043 & 0.060 & 0.083 & 1.000 \\ 
LOG\_MKT\_CAP & 172,684 & 7.176 & 1.761 & 1.301 & 6.032 & 7.205 & 8.354 & 10.785 \\ 
BM\_RATIO & 172,684 & 0.556 & 0.477 & 0.034 & 0.268 & 0.446 & 0.695 & 3.931 \\ 
LEVERAGE & 172,684 & 0.536 & 0.250 & 0.035 & 0.337 & 0.544 & 0.729 & 1.000 \\ 
ROA & 172,684 & 0.001 & 0.052 & $-$0.425 & 0.001 & 0.009 & 0.021 & 0.105 \\ 
ANALYST\_COVERAGE & 172,684 & 9.296 & 7.661 & 0 & 3 & 8 & 14 & 49 \\ 
\hline \\[-1.8ex] 
\multicolumn{9}{l}{} \\ 
\end{longtable}
\normalsize

As shown in Panel A of Table \ref{table_summary_did}, the mean and median of foreign institutional ownership (*FOR_OWN*) are 4.7% and 4.0%, respectively. The corresponding measures for total institutional ownership (*INST_OWN*) are 61.3% and 65.2%, respectively. The estimates are notably higher than in the baseline setting. This is largely explained by the fact that the exogenous reductions in analyst coverage are more affected by larger firms which have higher share of foreign ownership. Furthermore, the control firms are matched with a ratio of three by similar firm characteristics. Hence, it is consistent that *LOG_MKT_CAP* has higher mean, *BM_RATIO* lower mean and *ROA* higher mean than in the baseline setting. There is no essential difference in *LEVERAGE* between Tables \ref{table_summary_baseline} and \ref{table_summary_did}. *ANALYST_COVERAGE* has a mean of 10.038, with a minimum of 0 and a maximum of 50, indicating large variation between firm-quarter observations.

Based on Panels B and C, there are no large differences in ownership-specific variables between the treatment and control groups. *FOR_OWN* is 4.7% for both groups, although the median is higher for the treatment group (4.2%) than the control group (3.9%). Institutional ownership is slightly higher in the treatment group both in dollar terms (*INST_OWN*) and in numbers (*INST_BREADTH*). Moreover, the differences in control variables between the groups are almost to zero, except the variables *LOG_MKT_CAP* and *ANALYST_COVERAGE*. Although the control group is matched by these covariates and *BM_RATIO*, this finding suggests that treated firms are persistently larger firms and highly covered by analysts.

# 5 Methodology

To empirically examine the first hypothesis of the thesis, I use a panel regression model for the baseline sample. A difference-in-differences regression model is employed with the quasi-natural experiment sample to test the second and third hypotheses. 

## 5.1 The panel regression model

I test the relation of foreign ownership and information asymmetry by using the following panel regression model (OLS) of firm-year observations with fixed effects:

\begin{equation}\label{eq_baseline}
\begin{aligned}
FOREIGN_{i,t} &= \beta_{0} + \beta_{1}IA\_MEASURE_{i,t} + \beta_{2}BM\_RATIO_{i,t}\\ &+ \beta_{3}LEVERAGE_{i,t}+ \beta_{4}ROA_{i,t}\\ &+ YEAR_{t}+ INDUSTRY_{n} + \varepsilon_{i,t}
\end{aligned}
\end{equation}

where *FOREIGN~i,t~* is measured by either of the four ownership-specific variables: *FOR_OWN*, *FOR_BREADTH*, *FOR_TO_INST_OWN* and *FOR_TO_INST_BREADTH*. *IA_MEASURE~i,t~* is, similarly, measured by one of the various proxy variables of information asymmetry: *BA_SPREAD*, *PIN~BHL~*, *PIN~BH~*, *PIN~EHO~*, *PIN~DY~*, *PIN~DY_ADJ~*, *MIA*, *VCV~USD~*, *VCV~MKT~* and *VCV~TO~*. *BM_RATIO~i,t~*, *LEVERAGE~i,t~* and *ROA~i,t~* are control variables of firm-characteristics. *YEAR~t~* and *INDUSTRY~n~* control for year and industry specific fixed effects and *\(\varepsilon\)~i,t~* is the residual term. The detailed list of variables and definitions is provided in Table \ref{table_variable_definitions} in Appendix.

Based on the first hypothesis, I want to examine the effect of information asymmetry on foreign ownership. Hence, I include an ownership-specific variable as the dependent variable and an information asymmetry measure as the main explanatory variable. The main challenge in the model specification of the baseline setting is to include control variables that explain variation in foreign ownership, but are not correlated with information asymmetry measures. Following previous studies of foreign and institutional ownership, I first filter the potential group of control variables by selecting only the most commonly used variables that explain variation in foreign or institutional ownership. @kang1997there, @dahlquist2001direct, @jiang2004foreign and @baik2013liability find in Japanese, Swedish and the US markets that foreign investors prefer firms with large market capitalization and low book-to-market ratio. Furthermore, @kang1997there and @jiang2004foreign find that leverage has a negative effect on foreign ownership, whereas return on assets (ROA) has positive.

Next, based on the correlation results in Table \ref{table_cor_matrix}, I decide to exclude the logarithm of market capitalization (*LOG_MKT_CAP*), as it has approximately over -0.60 correlation between information asymmetry measures. Otherwise, there is a potential risk of multicollinearity, which may result in invalid coefficients of other explanatory variables and large standard errors. Other control variables have relatively small or moderate correlations with information asymmetry measures and are therefore kept in the regression model.

I also include fixed effects for year and industry to control for time variation and firm characteristics unrelated to information asymmetry or control variables. @baik2013liability find that foreign ownership increases substantially in the US markets between 1990 and 2007 and I find similar trend in my data set during 1997-2017. Also @duarte2017does and @lof2018asymmetric find that information asymmetry decreases over time. Thus, a pooled panel regression model does not capture this time-specific variation and can lead to biased and inconsistent estimators due to omitted variable bias. Following a recent study of foreign ownership by @bena2017foreign, I include industry fixed effects to control for unobservable firm-specific characteristics.

## 5.2 The difference-in-differences regression model

I examine the effect of an exogenous increase in information asymmetry on foreign ownership by using the following difference-in-differences regression of firm-quarter observations with fixed effects:

\begin{equation}
\label{eq_didh2}
\begin{aligned}
FOREIGN_{i,t} &= \beta_0 + \beta_{1}TREATED_{i} + \beta_{2}AFTER_{t} + \beta_{3}AFTER\times TREATED_{i,t}\\ &+ \beta_{4}LOG\_MKT\_CAP_{i,t} + \beta_{5}BM\_RATIO_{i,t} + \beta_{6}LEVERAGE_{i,t}\\ &+ \beta_{7}ROA_{i,t} + YEAR_{t}+ INDUSTRY_{n} + \varepsilon_{i,t}
\end{aligned}
\end{equation}

where *FOREIGN~i,t~* is, similarly as in Equation \ref{eq_baseline}, measured by either of the four ownership-specific variables: *FOR_OWN*, *FOR_BREADTH*, *FOR_TO_INST_OWN* and *FOR_TO_INST_BREADTH*. *FOR_OWN* and *FOR_BREADTH*. *TREATED* is a dummy variable indicating observations of firms that are in the treatment group. *AFTER* is defined as a dummy variable for observations that occur after each brokerage closure event. The variable of interest is the interaction term of these two variables *AFTER\texttimes TREATED* or the difference-in-differences estimator which captures the effect of treatment. I include same control variables of firm-characteristics *BM_RATIO~i,t~*, *LEVERAGE~i,t~* and *ROA~i,t~*, as in the baseline setting and the logarithm of market capitalization (*LOG_MKT_CAP*). Since there is no potential risk of multicollinearity due to the model not including an information asymmetry measure as an explanatory variable, I decide to include *LOG_MKT_CAP* to the model. *YEAR~t~* and *INDUSTRY~n~* control for year and industry specific fixed effects and *\(\varepsilon\)~i,t~* is the residual term. The detailed list of variables and definitions is provided in Table \ref{table_variable_definitions} in Appendix.

Since I want to test the causal effect of information asymmetry in hypotheses 2 and 3, I choose a difference-in-differences approach in the model specification. It ensures that the difference in foreign ownership between treatment and control groups is not due to cross-sectional heterogeneity or time series patterns affecting both groups. Rather, the model enables to examine whether the changes in foreign ownership are caused by exogenous shocks in asymmetric information, if the treatment and control groups are similar before the event. The crucial assumption here is the pre-treatment parallel trend between the groups, which I examine along with the results in Section 6. I also rely on the findings of @kelly2012testing and @derrien2013real that an exogenous decrease in analyst coverage due to the brokerage closures causes an increase in information asymmetry of the covered firm.

# 6 Results

In this section, I report the empirical results of the effect of information asymmetry on foreign ownership. First in Section 6.1, I present the results of the general relation between foreign ownership and information asymmetry with the baseline panel regression setting (Hypothesis 1). Second in Section 6.2, I study the causal effect of the exogenous increase in information asymmetry on foreign ownership by difference-in-differences panel regression setting (Hypothesis 2). Then, I examine the second hypothesis more in-depth by a subset analysis of the different institutional investor types. Finally, in Section 6.3 I test the causal effect in cases of low analyst coverage and low institutional ownership (Hypothesis 3).

## 6.1 The results of the baseline setting

In this section, I report the results of the baseline setting. First, I examine the effect of information asymmetry on foreign ownership in a panel regression setting The dependent variable in every regression model *FOR_OWN* is the annual average of the foreign ownership for each stock. Different information asymmetry measures are used separately as explanatory variables. The control variables are different measures of firm characteristics. I also include industry and year fixed effects. Table \ref{table_h1_base} reports the results.

Similar to the findings of correlations in Table \ref{table_cor_matrix}, the empirical results of the panel regression models in Table \ref{table_h1_base} support Hypothesis 1 and the findings by @jiang2004foreign, @baik2013liability and @batten2015foreign of the negative relation between foreign ownership and asymmetric information. In Panel A, The regression coefficients of information asymmetry measures are negative and statistically significant at the 1% level in all regression models. Based on column (5), a 1 percentage point increase in information asymmetry (*PIN~DY_ADJ~*) leads to a decrease of about 0.10 percentage points in foreign ownership *ceteris paribus*. Based on all models, a 1 percentage point increase in information asymmetry results, on average, in a decrease of about 0.07 percentage points in foreign ownership. Overall, the negative relation is stronger with the probability of informed trading measures than with multimarket information asymmetry or volume coefficient of variation. Based on the results of adjusted R^2^, models with different probability of informed trading measures and *MIA* have the best explanatory power.

The control variables in Panel A are mainly statistically significant and in line with the existing literature. Book-to-market ratio (*BM_RATIO*) is negative and statistically significant at the 1% level in all regression models except in the model with *MIA* as the explanatory variable. This implies that foreign investors are driven away of the stocks with relatively high book-to-market ratio (i.e. value stocks). Book-to-market ratio is used as a measure of risk in many asset pricing models [e.g., @fama1993common; @carhart1997persistence; @pastor2003liquidity], which, in addition to my results, supports the findings of @ko2007characteristics and @lin2003foreign that foreign investors avoid riskier firms with high book-to-market ratios. Moreover, the regression coefficients of *ROA* are positive and statistically significant at the 1% level in all models, implying that foreign investors prefer firms with positive probability. The regression coefficients of leverage are mainly positive. *LEVERAGE* is positive and statistically significant in six out of eleven models and positive and statistically insignificant in five out of eleven models. Hence, an increase in leverage is mostly associated with an increase in foreign ownership. The results mostly contradicts the findings of foreign investors' preference on low debt ratio firms by @kang1997there and @dahlquist2001direct.

```{r, results='asis', message = FALSE, warning=FALSE, eval = FALSE}
## baseline regression table h1 panel a: FOR_OWN and panel b:FOR_BREADTH
## code chunk produces tex file which is used in output
library(tidyverse)
library(stargazer)
library(lfe)
library(kableExtra)
library(starpolishr)
baseline_regression_raw <- read_rds("results/baseline_regression_raw.rds")

baseline_regression <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_OWN) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

baseline_regression2 <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_BREADTH) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

rnm <- function(df, ia_meas, dep_meas) {
  rnm_list <- set_names(c("ia_measure", "dep_measure"), syms(c(ia_meas, dep_meas)))
  rename(df, !!!rnm_list)
}

model_function <- function(df, ia_meas, dep_meas) {
  f <- dep_measure ~ ia_measure + BM_RATIO + LEVERAGE +
    ROA |year + sic_code|0|year + sic_code
  f[[2]] <- sym(dep_meas)
  f[[3]][[2]][[2]][[2]][[2]][[2]][[2]] <- sym(ia_meas)
  felm(f, data = df)
}

baseline_names <- mutate(baseline_regression,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))

baseline_names2 <- mutate(baseline_regression2,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))


 star1 <-  stargazer(baseline_names$model,
           header = F,
           column.labels =c("FOR\\_OWN"),
           label = "table_h1_base",
           dep.var.labels.include = F,
           notes.label = "",
           notes.append = F,
           notes = "",
           column.separate = c(11),
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign ownership", type = "latex")

 star2 <- stargazer(baseline_names2$model,
           header = F,
           #label = "table_h1_for_breadth",
           notes.label = "",
           notes.append = F,
           notes = "",
           column.labels =c("FOR_BREADTH"),
           dep.var.labels.include = F,
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign breadth", type = "latex")

a <- star_panel(star1, star2,
                        panel.names = c("Foreign ownership", "Foreign breadth"), same.summary.stats = F)

starpolishr::star_tex_write(a, file = "my_tex_file2.tex", headers = TRUE)

```

\begingroup
\renewcommand\arraystretch{0.63}
\begin{landscape}
\captionsetup{width=0.95\linewidth}
\scriptsize
\begin{longtable}{@{\extracolsep{5pt}}lccccccccccc}
  \caption[Panel regression analysis of foreign ownership and foreign breadth]{\textbf{Panel regression analysis of foreign ownership and foreign breadth}\newline\scriptsize This table reports the results of the annual firm-level panel regression models. In Panel A, the dependent variable is foreign ownership (\textit{FOR\_OWN}). In Panel B, the dependent variable is foreign breadth (\textit{FOR\_BREADTH}). The explanatory variables of main interest are the various annual firm-level estimates of information asymmetry. Other explanatory variables are firm-characteristic control variables. Ownership-specific variables are winsorized at the top to a maximum of 1. Control variables are winsorized at the top and bottom by 1\%. Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. I include industry and year fixed effects in all regressions. Standard errors are clustered by the industry and year level and reported in parentheses. *, ** and *** denote the statistical significance at the 10\%, 5\% and 1\% level, respectively. Sample period: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors' websites.}
   \label{table_h1_base} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
  & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_OWN} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.8ex] 
\\[-2.0ex] \multicolumn{12}{@{} l}{\textit{Panel A: Foreign ownership}}
 \\
 \\[-1.5ex]
BA\_SPREAD & $-$0.265$^{***}$ &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.040) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BHL} &  & $-$0.077$^{***}$ &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.017)  &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BH} &  &  & $-$0.079$^{***}$ &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.014) &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{DY} &  &  &  & $-$0.074$^{***}$ &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.013) &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{DY\_ADJ} &  &  &  &  & $-$0.097$^{***}$ &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.016) &  &  &  &  &  &  \\ 
  PSOS\textsubscript{DY} &  &  &  &  &  & $-$0.042$^{***}$ &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.010) &  &  &  &  &  \\ 
  PIN\textsubscript{EHO} &  &  &  &  &  &  & $-$0.089$^{***}$ &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.013) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.035$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.007) &  &  &  \\ 
  VCV\textsubscript{USD} &  &  &  &  &  &  &  &  & $-$0.011$^{***}$ &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.001) &  &  \\ 
  VCV\textsubscript{MKT} &  &  &  &  &  &  &  &  &  & $-$0.011$^{***}$ &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.001) &  \\ 
  VCV\textsubscript{TO} &  &  &  &  &  &  &  &  &  &  & $-$0.012$^{***}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.001) \\ 
  BM\_RATIO & $-$0.006$^{***}$ & $-$0.003$^{***}$ & $-$0.003$^{***}$ & $-$0.005$^{***}$ & $-$0.003$^{***}$ & $-$0.005$^{***}$ & $-$0.003$^{***}$ & $-$0.0001 & $-$0.006$^{***}$ & $-$0.006$^{***}$ & $-$0.006$^{***}$ \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  LEVERAGE & 0.005 & 0.008$^{***}$ & 0.008$^{***}$ & 0.008$^{***}$ & 0.004$^{***}$ & 0.003 & 0.005$^{**}$ & 0.011$^{***}$ & 0.003 & 0.003 & 0.004 \\ 
  & (0.003) & (0.002) & (0.002) & (0.002) & (0.001) & (0.002) & (0.002) & (0.004) & (0.003) & (0.003) & (0.003) \\ 
  ROA & 0.052$^{***}$ & 0.080$^{***}$ & 0.082$^{***}$ & 0.080$^{***}$ & 0.064$^{***}$ & 0.074$^{***}$ & 0.074$^{***}$ & 0.093$^{***}$ & 0.079$^{***}$ & 0.079$^{***}$ & 0.084$^{***}$ \\ 
  & (0.008) & (0.009) & (0.009) & (0.009) & (0.008) & (0.009) & (0.009) & (0.012) & (0.008) & (0.008) & (0.008) \\ 
\cline{2-12} \\[-2.0ex]
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 109,907 & 78,009 & 78,118 & 15,021 & 15,021 & 15,021 & 9,496 & 20,717 & 94,298 & 94,298 & 94,298 \\ 
Adjusted R$^{2}$ & 0.156 & 0.190 & 0.199 & 0.349 & 0.343 & 0.312 & 0.331 & 0.262 & 0.177 & 0.177 & 0.176 \\ 
\hline \\[-1.8ex]
\\[-1.83ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_BREADTH} \\ 
\\[-1.83ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.83ex]
\\[-2.0ex] \multicolumn{12}{@{} l}{\textit{Panel B: Foreign breadth}}
 \\
 \\[-1.5ex]
 BA\_SPREAD & $-$0.036$^{***}$ &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.009) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BHL} &  & $-$0.013$^{***}$ &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.002) &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BH} &  &  & $-$0.013$^{***}$ &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.002) &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{DY} &  &  &  & $-$0.014$^{***}$ &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.003) &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{DY\_ADJ} &  &  &  &  & $-$0.021$^{***}$ &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.003) &  &  &  &  &  &  \\ 
  PSOS\textsubscript{DY} &  &  &  &  &  & $-$0.007$^{***}$ &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.002) &  &  &  &  &  \\ 
  PIN\textsubscript{EHO} &  &  &  &  &  &  & $-$0.018$^{***}$ &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.002) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.033$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.003) &  &  &  \\ 
  VCV\textsubscript{USD} &  &  &  &  &  &  &  &  & $-$0.002$^{***}$ &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.0002) &  &  \\ 
  VCV\textsubscript{MKT} &  &  &  &  &  &  &  &  &  & $-$0.002$^{***}$ &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.0002) &  \\ 
  VCV\textsubscript{TO} &  &  &  &  &  &  &  &  &  &  & $-$0.002$^{***}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.0002) \\ 
  BM\_RATIO & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.0003$^{***}$ & $-$0.0003 & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ \\ 
  & (0.0001) & (0.0002) & (0.0002) & (0.0002) & (0.0001) & (0.0001) & (0.0001) & (0.0003) & (0.0001) & (0.0001) & (0.0001) \\ 
  LEVERAGE & 0.003$^{***}$ & 0.003$^{***}$ & 0.003$^{***}$ & 0.003$^{***}$ & 0.002$^{***}$ & 0.001$^{***}$ & 0.002$^{***}$ & 0.005$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ \\ 
  & (0.0005) & (0.001) & (0.001) & (0.001) & (0.0003) & (0.0002) & (0.0003) & (0.001) & (0.0004) & (0.0004) & (0.0004) \\ 
  ROA & 0.007$^{***}$ & 0.013$^{***}$ & 0.014$^{***}$ & 0.014$^{***}$ & 0.009$^{***}$ & 0.006$^{***}$ & 0.008$^{***}$ & 0.022$^{***}$ & 0.010$^{***}$ & 0.009$^{***}$ & 0.010$^{***}$ \\ 
  & (0.001) & (0.002) & (0.002) & (0.002) & (0.002) & (0.001) & (0.001) & (0.004) & (0.002) & (0.002) & (0.002) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 109,907 & 78,009 & 78,118 & 15,021 & 15,021 & 15,021 & 9,496 & 20,717 & 94,298 & 94,298 & 94,298 \\ 
Adjusted R$^{2}$ & 0.267 & 0.375 & 0.365 & 0.406 & 0.426 & 0.342 & 0.449 & 0.488 & 0.311 & 0.313 & 0.311 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{12}{r}{} \\ 
\end{longtable}  
\end{landscape}
\endgroup

Panel B reports the results of regressing foreign breadth on information asymmetry measures. The results follow similar pattern with foreign ownership results in Panel A. The regression coefficients of information asymmetry are negative and statistically significant at the 1% level in all models. Based on column (8), a 100 basis point increase in information asymmetry (*MIA*) is associated with a ca. 3 basis point decrease in foreign breadth. In general, a 100 basis point increase in information asymmetry results in 0.2 - 4 basis points decrease of foreign breadth. Based on adjusted R^2^, the explanatory power is, in general, better than with models in Panel A. Notably, the model with *MIA* clearly explains variation better than other models, which differs from the results in Panel A. 

In addition to information asymmetry measures, the control variables in Panel B follow similar pattern with Panel A. Book-to-market ratio is negative and statistically significant at the 1% level in all models, except with *MIA* as explanatory variable, leverage is positive and statistically significant in all models and return on assets is positive and statistically significant at the 1% level in all models. Similar to Panel A, the results support the findings of @ko2007characteristics and @lin2003foreign that foreign investors seek stocks with comfortable characteristics, except the results of leverage. In general, the results of Table \ref{table_h1_base} support strongly the first hypothesis of inverse relation between foreign ownership and information asymmetry.

In addition to inspecting general market-level foreign ownership and breadth measures, I extend the analysis by comparing foreign ownership against institutional ownership for a given stock in a given time. In particular, I define a variable *FOR_TO_INST_OWN* which is a measure of the annual average of the firm's shares held by foreign institutions at the end of each quarter divided by the firm's shares held by total institutions at the end of each quarter. This enables me to examine whether foreign institutional shareholders have stronger or weaker dislike of information intensive stocks than institutional shareholders in general. Similarly, I define a variable *FOR_TO_INST_BREADTH* which is a measure of the annual average of the number of the firm's distinct foreign institutional shareholders at the end of each quarter divided by the number of the firm's of distinct institutional shareholders at the end of each quarter. I test the dependent variables with the same panel regression models as in Table \ref{table_h1_base}. Table \ref{table_h1_for_to_inst} reports the results.


``` {r, results='asis', message = FALSE, warning=FALSE, eval = FALSE}
library(tidyverse)
library(stargazer)
library(lfe)
library(kableExtra)
library(starpolishr)

baseline_regression_raw <- read_rds("results/baseline_regression_raw.rds")

baseline_regression <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_TO_INST_OWN) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

baseline_regression2 <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_TO_INST_BREADTH) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

rnm <- function(df, ia_meas, dep_meas) {
  rnm_list <- set_names(c("ia_measure", "dep_measure"), syms(c(ia_meas, dep_meas)))
  rename(df, !!!rnm_list)
}

model_function <- function(df, ia_meas, dep_meas) {
  f <- dep_measure ~ ia_measure + BM_RATIO + LEVERAGE +
    ROA |year + sic_code|0|year + sic_code
  f[[2]] <- sym(dep_meas)
  f[[3]][[2]][[2]][[2]][[2]][[2]][[2]] <- sym(ia_meas)
  felm(f, data = df)
}

baseline_names <- mutate(baseline_regression,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))

baseline_names2 <- mutate(baseline_regression2,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))

star1 <-  stargazer(baseline_names$model,
           header = F,
           column.labels =c("FOR\\_TO\\_INST\\_OWN"),
           label = "table_h1_for_to_inst",
           dep.var.labels.include = F,
           notes.label = "",
           notes.append = F,
           notes = "",
           column.separate = c(11),
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign-to-institution ownership and breadth ratios", type = "latex")

 star2 <- stargazer(baseline_names2$model,
           header = F,
           column.labels =c("FOR\\_TO\\_INST\\_BREADTH"),
           notes.label = "",
           notes.append = F,
           notes = "",
           dep.var.labels.include = F,
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign-to-institution breadth ratio ", type = "latex")

a <- star_panel(star1, star2,
                        panel.names = c("Foreign-to-institution ownership ratio", "Foreign-to-institution breadth ratio"), same.summary.stats = F)


starpolishr::star_tex_write(a, file = "my_tex_file3.tex", headers = TRUE)

```

\begingroup
\renewcommand\arraystretch{0.63}
\begin{landscape}
\captionsetup{width=0.94\linewidth}
\scriptsize
\begin{longtable}{@{\extracolsep{5pt}}lccccccccccc}
  \caption[Panel regression analysis of foreign-to-institution ownership and breadth ratios]{\textbf{Panel regression analysis of foreign-to-institution ownership and breadth ratios}\newline\scriptsize This table reports the results of the annual firm-level panel regression models. In Panel A, the dependent variable is foreign-to-institution ownership (\textit{FOR\_TO\_INST\_OWN}). In Panel B, the dependent variable is foreign-to-institution breadth (\textit{FOR\_TO\_INST\_BREADTH}). The explanatory variables of main interest are the various annual firm-level estimates of information asymmetry. Other explanatory variables are firm-characteristic control variables. Ownership-specific variables are winsorized at the top to a maximum of 1. Control variables are winsorized at the top and bottom by 1\%. Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. I include industry and year fixed effects in all regressions. Standard errors are clustered by the industry and year level and reported in parentheses. *, ** and *** denote the statistical significance at the 10\%, 5\% and 1\% level, respectively. Sample period: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors' websites.}
  \label{table_h1_for_to_inst} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_TO\_INST\_OWN} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.8ex] 
\\[-2.0ex] \multicolumn{12}{@{} l}{\textit{Panel A: Foreign-to-institution ownership ratio}}
 \\
 \\[-1.5ex]
 BA\_SPREAD & $-$0.024 &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.076) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BHL} &  & $-$0.023 &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.021) &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BH} &  &  & $-$0.021 &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.030) &  &  &  &  &  &  &  &  \\
  PIN\textsubscript{DY} &  &  &  & 0.001 &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.043) &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{DY\_ADJ} &  &  &  &  & $-$0.014 &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.051) &  &  &  &  &  &  \\ 
  PSOS\textsubscript{DY} &  &  &  &  &  & 0.007 &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.022) &  &  &  &  &  \\ 
  PIN\textsubscript{EHO} &  &  &  &  &  &  & 0.071 &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.070) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.057$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.012) &  &  &  \\ 
  VCV\textsubscript{USD} &  &  &  &  &  &  &  &  & $-$0.008$^{***}$ &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.002) &  &  \\ 
  VCV\textsubscript{MKT} &  &  &  &  &  &  &  &  &  & $-$0.007$^{***}$ &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.002) &  \\ 
  VCV\textsubscript{TO} &  &  &  &  &  &  &  &  &  &  & $-$0.010$^{***}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.002) \\ 
  BM\_RATIO & $-$0.010$^{***}$ & $-$0.007$^{***}$ & $-$0.006$^{**}$ & $-$0.007$^{**}$ & $-$0.009$^{***}$ & $-$0.011$^{***}$ & $-$0.010$^{***}$ & 0.004 & $-$0.010$^{***}$ & $-$0.010$^{***}$ & $-$0.009$^{***}$ \\ 
  & (0.002) & (0.002) & (0.002) & (0.003) & (0.003) & (0.002) & (0.002) & (0.003) & (0.002) & (0.002) & (0.002) \\ 
  LEVERAGE & $-$0.002 & 0.002 & 0.002 & 0.002 & $-$0.001 & $-$0.004 & $-$0.003 & 0.006 & $-$0.004 & $-$0.004 & $-$0.004 \\ 
  & (0.006) & (0.004) & (0.004) & (0.004) & (0.006) & (0.006) & (0.005) & (0.007) & (0.006) & (0.006) & (0.006) \\ 
  ROA & $-$0.005 & $-$0.028 & $-$0.029 & $-$0.026 & $-$0.032 & $-$0.053$^{***}$ & $-$0.054$^{***}$ & $-$0.030 & $-$0.033 & $-$0.032 & $-$0.033 \\ 
  & (0.020) & (0.036) & (0.037) & (0.037) & (0.049) & (0.018) & (0.017) & (0.034) & (0.025) & (0.025) & (0.025) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 109,907 & 78,009 & 78,118 & 15,021 & 15,021 & 15,021 & 9,496 & 20,717 & 94,298 & 94,298 & 94,298 \\ 
Adjusted R$^{2}$ & 0.086 & 0.087 & 0.086 & 0.083 & 0.083 & 0.083 & 0.101 & 0.209 & 0.100 & 0.100 & 0.101 \\ 
\hline \\[-1.8ex]
\\[-1.83ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_TO\_INST\_BREADTH} \\ 
\\[-1.83ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.83ex]
\\[-2.0ex] \multicolumn{12}{@{} l}{\textit{Panel B: Foreign-to-institution breadth ratio}}
 \\
 \\[-1.5ex]
BA\_SPREAD & $-$0.071 &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.074) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BHL} &  & 0.020 &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.021) &  &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{BH} &  &  & 0.050 &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.034) &  &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{DY} &  &  &  & 0.094$^{**}$ &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.037) &  &  &  &  &  &  &  \\ 
  PIN\textsubscript{DY\_ADJ} &  &  &  &  & 0.105$^{**}$ &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.042) &  &  &  &  &  &  \\ 
  PSOS\textsubscript{DY} &  &  &  &  &  & 0.056$^{***}$ &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.021) &  &  &  &  &  \\ 
  PIN\textsubscript{EHO} &  &  &  &  &  &  & 0.190$^{***}$ &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.058) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.025$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.009) &  &  &  \\ 
  VCV\textsubscript{USD} &  &  &  &  &  &  &  &  & $-$0.006 &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.004) &  &  \\ 
  VCV\textsubscript{MKT} &  &  &  &  &  &  &  &  &  & $-$0.005 &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.004) &  \\ 
  VCV\textsubscript{TO} &  &  &  &  &  &  &  &  &  &  & $-$0.007$^{*}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.004) \\ 
  BM\_RATIO & $-$0.004$^{*}$ & 0.001 & 0.002 & 0.003 & $-$0.003 & $-$0.001 & $-$0.003$^{*}$ & 0.004$^{**}$ & $-$0.004$^{**}$ & $-$0.004$^{**}$ & $-$0.004$^{**}$ \\ 
  & (0.002) & (0.002) & (0.002) & (0.003) & (0.003) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) \\ 
  LEVERAGE & 0.004 & 0.003 & 0.003 & 0.002 & $-$0.002 & $-$0.0004 & 0.0002 & 0.013$^{***}$ & 0.003 & 0.003 & 0.003 \\ 
  & (0.004) & (0.004) & (0.004) & (0.004) & (0.004) & (0.004) & (0.004) & (0.005) & (0.004) & (0.004) & (0.004) \\ 
  ROA & $-$0.019 & $-$0.048$^{*}$ & $-$0.053$^{*}$ & $-$0.047$^{*}$ & $-$0.043 & $-$0.060$^{***}$ & $-$0.054$^{***}$ & $-$0.0002 & $-$0.027 & $-$0.027 & $-$0.026 \\ 
  & (0.020) & (0.028) & (0.029) & (0.028) & (0.040) & (0.018) & (0.017) & (0.022) & (0.021) & (0.021) & (0.022) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 109,907 & 78,009 & 78,118 & 15,021 & 15,021 & 15,021 & 9,496 & 20,717 & 94,298 & 94,298 & 94,298 \\ 
Adjusted R$^{2}$ & 0.095 & 0.079 & 0.081 & 0.110 & 0.103 & 0.103 & 0.164 & 0.433 & 0.126 & 0.126 & 0.126 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{12}{r}{} \\ 
\end{longtable}  
\end{landscape}
\endgroup

In Panel A, the regression coefficients of asymmetric information variables are all negative, except the models with *PIN_DY*, *PSOS_DY* and *PIN~EHO~* as explanatory variables. The results are statistically significant at the 1% level in models with *MIA* and all *VCV* variables as explanatory variables. The results give more supporting evidence of the negative relation between foreign ownership and information asymmetry. Based on the results, foreign investors are more prone to avoid information intensive stocks compared to institutional investors on average. Based on column (8), a 1 percentage point increase in information asymmetry is associated with 0.06 percentage point decrease in ownership of foreign institutions against total institutions. The models with statistically significant results (*MIA* and *VCV*) have the best explanatory power according to the results of adjusted R^2^.

The results of the control variable coefficients are mixed. Book-to-market ratio (*BM_RATIO*) is negative and statistically significant at the 1% level in all regression models except with *MIA* as the explanatory variable. The results are mainly in line with the previous results and existing literature, implying that foreign institutional investors prefer more non-value stocks compared to institutional investors on average. The coefficients of *LEVERAGE* are mainly statistically insignificant, positive in four out eleven models and negative in seven out of eleven models. Hence, the results of *LEVERAGE* provide nothing conclusive. The results of *ROA* are to some extent surprising. The coefficients are negative in all models and statistically significant at the 1% level in two models. The results imply that foreign institutional investors are more prone to hold less profitable stocks compared to institutional investors on average.

In Panel B, the regression coefficients of asymmetric information variables provide mixed results. The coefficients are positive and statistically significant with models of *PIN~DY~*, *PIN~DY_ADJ~*, *PSOS~DY~* and *PIN~EHO~* and negative and statistically significant with models of *MIA* and *VCV~TO~*. Hence, it is difficult to derive solid conclusions of the results. However, according to adjusted R^2^, the models with *MIA* and different *VCV* measures as explanatory variables have better explanatory power. In particular, the model with *MIA* has adjusted R^2^ of 0.433 which is clearly better than any other model. Moreover, the sample sizes in models with *MIA* and *VCV* are notably larger than with *PIN~DY~*, *PIN~DY_ADJ~*, *PSOS~DY~* and *PIN~EHO~*. 

Control variables in Panel B provide mixed results. *BM_RATIO* is negative in seven out of eleven models and statistically significant in five out of eleven models. It is positive and statistically significant once. Hence, the results primarily suggests that foreign institutional investors are relatively more driven away of the value stocks than institutional investors in general. *LEVERAGE* is positive and statistically significant once and otherwise insignificant, implying foreign institutional investors' relatively larger tendency towards more levered stocks than institutional investors in general. This is counterintuitive in the light of the results by @kang1997there and @dahlquist2001direct that foreign investors prefer low debt ratio firms. The regression coefficients of *ROA* follow a similar negative and statistically significant pattern than in Panel B. This finding suggests that foreign institutional investors hold relatively less profitable stocks than institutional investors in general.

## 6.2 The main results of the quasi-natural experiment

In this section, I report the main results of the quasi-natural experiment. First, I examine the evolution of the dependent variables foreign ownership (*FOR_OWN*), foreign breadth (*FOR_BREADTH*), foreign-to-institution ownership (*FOR_TO_INST_OWN*) and foreign-to-institution breadth (*FOR_TO_INST_BREADTH*) between the treatment and control groups in the twelve quarters (i.e. three years) before and after the brokerage closures. The treated firms are firms that lose an analyst due to these brokerage closures. The control firms are selected using propensity score matching that matches each treatment firm to three control firms (nearest neighbor) on multiple covariates (twelve quarter before the event): logarithm of market capitalization, book-to-market ratio and analyst coverage. Figure \ref{fig_parallel_trend1} presents the results.

``` {r parallel_trend1, message = FALSE, warning=FALSE, eval=FALSE}

library(tidyverse)

parallel_trend1 <- read_rds("results/did_regression_matched_raw.rds") %>% 
  mutate(TREATED = if_else(TREATED == 1, "Treated", "Control")) %>% 
  group_by(TREATED, quarter_index) %>% 
  summarise(FOR_OWN = mean(FOR_OWN),
            FOR_BREADTH = mean(FOR_BREADTH),
            FOR_TO_INST_OWN = mean(FOR_TO_INST_OWN),
            FOR_TO_INST_BREADTH = mean(FOR_TO_INST_BREADTH)) %>% 
  ungroup()

ggplot(parallel_trend1, aes(quarter_index, FOR_OWN, color = TREATED)) +
  ggtitle("Panel A: Foreign ownership") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend1a.pdf", 
       width = 8, height = 6, units = "in")

ggplot(parallel_trend1, aes(quarter_index, FOR_BREADTH, color = TREATED)) +
  ggtitle("Panel B: Foreign breadth") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend1b.pdf", 
       width = 8, height = 6, units = "in")

ggplot(parallel_trend1, aes(quarter_index, FOR_TO_INST_OWN, color = TREATED)) +
  ggtitle("Panel C: Foreign-to-institution ownership") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend2a.pdf", 
       width = 8, height = 6, units = "in")

ggplot(parallel_trend1, aes(quarter_index, FOR_TO_INST_BREADTH, color = TREATED)) +
  ggtitle("Panel D: Foreign-to-institution breadth") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend2b.pdf", 
       width = 8, height = 6, units = "in")
  
```

\begin{figure}[!htb]
\centering
\begin{subfigure}{.475\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figures/parallel_trend1a.pdf}
\end{subfigure}
\hfill
\begin{subfigure}{.475\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figures/parallel_trend1b.pdf}
\end{subfigure}
\hfill
\begin{subfigure}{.475\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figures/parallel_trend2a.pdf}
\end{subfigure}
\hfill
\begin{subfigure}{.475\textwidth}
  \centering
  \includegraphics[width=\textwidth]{figures/parallel_trend2b.pdf}
\end{subfigure}
\hfill
\caption[Foreign ownership-specific variables between the treatment and control groups around brokerage closures]{\textbf{Foreign ownership-specific variables between the treatment and control groups around brokerage closures}\newline\scriptsize This figure presents the evolution of the mean of firm-quarter observations of ownership-specific variables during the twelve quarters (i.e. three years) before and after an exogenous decrease in analyst coverage due to the 22 distinct brokerage closures listed by \citet{kelly2012testing}. I impose a three-month gap over the events so that foreign ownership estimates are from quarters [-12,-1] and [1,12], with the brokerage closure occurring in the quarter 0. Control firms are matched using propensity score matching (nearest neighbor) that matches each treatment firm to three control firms by multiple covariates (twelve quarters before the event): logarithm of market capitalization (\textit{LOG\_MKT\_CAP}), book-to-market ratio (\textit{BM\_RATIO}) and number of distinct analysts covering the firm (\textit{ANALYST\_COVERAGE}). Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.}
\label{fig_parallel_trend1}
\end{figure}

As shown in Panel A, foreign ownership between the treatment and control groups follow an increasing but parallel trend before the event. This validates the assumption of pre-treatment parallel trend between treatment and control groups. Foreign ownership of the control group increases quite prominently during the event occurring quarter and surpasses that of the treatment group after the event whereas the treatment group stays put during the event occurring quarter. However, there is no significant persistent decline in foreign ownership for the treatment group after the event. Hence, there is no robust evidence of a significant post-treatment difference in mean between the two groups. Foreign ownership of both groups continue increasing and are approximately at the same level constantly after the event. Abrupt changes in foreign ownership during the event quarters 5 and 10 are largely caused by changes in foreign ownership during the last quarter of 2003. These changes are further illustrated in Figure \ref{fig_parallel_trend1_facet} in Appendix with event-specific plots.

Panel B provides the results of the evolution of foreign breadth between the treatment and control groups. Similar to Panel A, foreign breadth follows an increasing but parallel trend between the groups before the event, which validates the assumption of pre-treatment parallel trend. The increasing and parallel trend follows also after the event and there is a slightly larger decrease in foreign ownership for the treatment group, but the decrease is not significantly larger compared to the control group. 

Panels C and D provide evidence of the development of foreign institutional investors' ownership (*FOR_TO_INST_OWN*) and breadth (*FOR_TO_INST_BREADTH*) against total institutional investors between treatment and control groups. In both panels, the pre-treatment parallel trend is is mostly satisfied. In Panel C, there is a slight drop in ownership ratio in the treatment group after the quarter 0, but the decrease is not significantly larger compared to the control group. On the other hand, in Panel D, the breadth ratio of the treatment group increases more after the event compared to the control group. Based on overall results, the results of Figure \ref{fig_parallel_trend1} do not give strong support for the second hypothesis that an exogenous increase in information asymmetry results in a decrease of foreign ownership.

I extend the analysis of the quasi-experimental setting by implementing a difference-in-differences regression analysis of foreign ownership and foreign breadth. Compared to results in Figure \ref{fig_parallel_trend1}, this enables me to control for other variables and include year and industry fixed effects. Similar to Figure \ref{fig_parallel_trend1}, I identify treatment group as stocks that lose an analyst covering the firm due to the brokerage closures and control firms are matched using the propensity score matching. In addition, I impose a three-month gap before and after the event and therefore I calculate averages of the dependent and control variables over the quarters [-4,-1] and [1,4], [-8,-1] and [1,8] and [-12,-1] and [1,12], with the brokerage closure occurring in the quarter 0. When computing the averages, I require for each stock to have at least one observation of the dependent and control variables before and after each event. The explanatory variables are dummy variables indicating observations in the post-closure period (\textit{AFTER}), in the treatment group (\textit{TREATED}) and their interaction term (\textit{AFTER}\texttimes\textit{TREATED}). Table \ref{table_h2_1} reports the results.

``` {r, results='asis', echo = FALSE, eval=FALSE}

library(tidyverse)
library(lfe)
library(stargazer)

did_regression_matched1 <- read_rds("results/did_regression_matched1.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER,
         sic_code =str_sub(sic_code, 1, 2))
did_regression_matched2 <- read_rds("results/did_regression_matched2.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER,
         sic_code =str_sub(sic_code, 1, 2))
did_regression_matched3 <- read_rds("results/did_regression_matched3.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER,
         sic_code =str_sub(sic_code, 1, 2))

did_model1 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model2 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model3 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_model7 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model8 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model9 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_list <- list(did_model1, did_model2, did_model3, did_model7, did_model8, did_model9)

treated_obs <- map_dbl(list(did_regression_matched1, did_regression_matched2, did_regression_matched3), ~  .x %>% filter(TREATED == 1) %>% 
  group_by(TREATED) %>% summarise(n = n()) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

control_obs <- map_dbl(list(did_regression_matched1, did_regression_matched2, did_regression_matched3), ~  .x %>% filter(TREATED == 0) %>% 
  group_by(TREATED) %>% summarise(n = n()) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

treated_distinct <- map_dbl(list(did_regression_matched1, did_regression_matched2, did_regression_matched3), ~  .x %>% filter(TREATED == 1) %>% 
  group_by(TREATED) %>% summarise(n = n_distinct(permno)) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

control_distinct <- map_dbl(list(did_regression_matched1, did_regression_matched2, did_regression_matched3), ~  .x %>% filter(TREATED == 0) %>% 
  group_by(TREATED) %>% summarise(n = n_distinct(permno)) %>% ungroup() %>% pluck("n")) %>%
  format(big.mark = ",")

obs <- map_dbl(list(did_regression_matched1, did_regression_matched2, did_regression_matched3), ~  .x %>%
 summarise(n = n()) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

stargazer(did_list, title = "\\textbf{Difference-in-differences regression analysis of foreign ownership and breadth}\\newline\\small This table reports the results of the difference-in-differences regression analysis of foreign ownership and breadth. The explanatory variables are \\textit{AFTER}.",
          label = "table_h2_1",
          header = F,
          dep.var.labels =c("FOR\\_OWN", "FOR\\_BREADTH"),
          column.labels = rep(c("[-1,1] years", "[-2,2] years", "[-3,3] years"), times = 2),
          covariate.labels = c("AFTER", "TREATED", "AFTER\\texttimes TREATED", "LOG\\_MKT\\_CAP", "BM\\_RATIO", "LEVERAGE", "ROA"),
          omit.stat = c("ser", "rsq", "n"),
          add.lines = list(c("Industry fixed effects", rep("Yes", times = 6)),
                           c("Year fixed effects", rep("Yes", times = 6)),
                           c("Treated firm obs.", rep(treated_obs, times = 2)),
                           c("Control firm obs.", rep(control_obs, times = 2)),
                           c("Distinct treated firms", rep(treated_distinct, times = 2)),
                           c("Distinct control firms", rep(control_distinct, times = 2)),
                           c("Observations", rep(obs, times = 2))),
          type = 'latex',
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          no.space = T)

did_model1 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model2 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model3 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_model7 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model8 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model9 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_list <- list(did_model1, did_model2, did_model3, did_model7, did_model8, did_model9)

stargazer(did_list, title = "\\textbf{Difference-in-differences regression analysis of foreign ownership and breadth}\\newline\\small This table reports the results of the difference-in-differences regression analysis of foreign ownership and breadth. The explanatory variables are \\textit{AFTER}.",
          label = "table_h2_1",
          header = F,
          dep.var.labels =c("FOR\\_TO\\_INST\\_OWN", "FOR\\_TO\\_INST\\_BREADTH"),
          column.labels = rep(c("[-1,1] years", "[-2,2] years", "[-3,3] years"), times = 2),
          covariate.labels = c("AFTER", "TREATED", "AFTER\\texttimes TREATED", "LOG\\_MKT\\_CAP", "BM\\_RATIO", "LEVERAGE", "ROA"),
          omit.stat = c("ser", "rsq", "n"),
          add.lines = list(c("Industry fixed effects", rep("Yes", times = 6)),
                           c("Year fixed effects", rep("Yes", times = 6)),
                           c("Treated firm obs.", rep(treated_obs, times = 2)),
                           c("Control firm obs.", rep(control_obs, times = 2)),
                           c("Distinct treated firms", rep(treated_distinct, times = 2)),
                           c("Distinct control firms", rep(control_distinct, times = 2)),
                           c("Observations", rep(obs, times = 2))),
          type = 'latex',
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          no.space = T)

```

\clearpage
\renewcommand\arraystretch{0.55}
\captionsetup{width=1.0\linewidth}
\footnotesize
\begin{longtable}{@{\extracolsep{5pt}}lcccccc}
  \caption[Difference-in-differences regression analysis of foreign ownership-specific variables]{\textbf{Difference-in-differences regression analysis of foreign ownership-specific variables}\newline\scriptsize This table reports the results of the difference-in-differences regression analysis of ownership-specific variables. In Panel A, the dependent variables are foreign ownership (\textit{FOR\_OWN}) and foreign breadth (\textit{FOR\_BREADTH}). In Panel B, the dependent variables are foreign-to-institution ownership (\textit{FOR\_TO\_INST\_OWN}) and foreign-to-institution breadth (\textit{FOR\_TO\_INST\_BREADTH}). The treatment group is determined as stocks that lose a covering analyst due to 22 distinct brokerage closures listed by \citet{kelly2012testing}. Control firms are matched using propensity score matching (nearest neighbor) that matches each treatment firm to three control firms by multiple covariates (twelve quarters before the event): logarithm of market capitalization (\textit{LOG\_MKT\_CAP}), book-to-market ratio (\textit{BM\_RATIO}) and number of distinct analysts covering the firm (\textit{ANALYST\_COVERAGE}). For all stocks, I compute averages of the dependent variables and control variables in columns (1) and (4) over the quarters [-4,-1] and over the quarters [1,4], with the brokerage closure occurring in quarter 0. In columns (2) and  (5) the dependent variables are computed over the quarters [-8,-1] and [1,8] and in columns (3) and (6) over the quarters [-12,-1] and [1,12]. The explanatory variables are dummy variables indicating the treatment group (\textit{TREATED}), the post-event period (\textit{AFTER}) and their interaction (\textit{AFTER}\texttimes\textit{TREATED}). The control variables are book-to-market ratio (\textit{BM\_RATIO}), leverage (\textit{LEVERAGE}) and return on assets (\textit{ROA}). I include industry and year fixed effects in all regressions. Standard errors are clustered by the industry and year level and reported in parentheses. \textit{FOR\_OWN} and \textit{FOR\_BREADTH} are winsorized at the top to a maximum of 1. Control variables are winsorized at the top and bottom 1\%. Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. *, ** and *** denote the statistical significance at the 10\%, 5\% and 1\% level, respectively. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.} 
  \label{table_h2_1} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & \multicolumn{3}{c}{FOR\_OWN} & \multicolumn{3}{c}{FOR\_BREADTH} \\ 
 & [-1,1] years & [-2,2] years & [-3,3] years & [-1,1] years & [-2,2] years & [-3,3] years \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline
\multicolumn{6}{@{} l}{\textit{Panel A: Foreign ownership and breadth}}
\\
\\
 AFTER & 0.008$^{***}$ & 0.011$^{***}$ & 0.014$^{***}$ & 0.001$^{***}$ & 0.001$^{***}$ & 0.001$^{***}$ \\ 
  & (0.003) & (0.004) & (0.003) & (0.0002) & (0.0001) & (0.0001) \\ 
  TREATED & $-$0.001 & $-$0.002 & $-$0.002 & 0.0004 & 0.0004 & 0.0003 \\ 
  & (0.001) & (0.001) & (0.001) & (0.0004) & (0.0004) & (0.0004) \\ 
  AFTER\texttimes TREATED & $-$0.001 & $-$0.0002 & 0.0004 & 0.00004 & 0.0002 & 0.0004$^{*}$ \\ 
  & (0.001) & (0.002) & (0.002) & (0.0001) & (0.0002) & (0.0002) \\ 
  LOG\_MKT\_CAP & 0.005$^{***}$ & 0.005$^{***}$ & 0.005$^{***}$ & 0.003$^{***}$ & 0.003$^{***}$ & 0.003$^{***}$ \\ 
  & (0.001) & (0.001) & (0.001) & (0.0003) & (0.0003) & (0.0003) \\ 
  BM\_RATIO & 0.001 & 0.002 & 0.001 & 0.001$^{***}$ & 0.001$^{***}$ & 0.001$^{***}$ \\ 
  & (0.002) & (0.002) & (0.002) & (0.0003) & (0.0002) & (0.0002) \\ 
  LEVERAGE & 0.001 & 0.002 & 0.002 & 0.001$^{*}$ & 0.001$^{**}$ & 0.001$^{**}$ \\ 
  & (0.003) & (0.002) & (0.002) & (0.001) & (0.0004) & (0.0004) \\ 
  ROA & 0.064$^{***}$ & 0.082$^{***}$ & 0.086$^{***}$ & $-$0.010$^{***}$ & $-$0.009$^{***}$ & $-$0.010$^{***}$ \\ 
  & (0.012) & (0.013) & (0.009) & (0.003) & (0.003) & (0.003) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Treated firm obs. & 5,424 & 5,444 & 5,470 & 5,424 & 5,444 & 5,470 \\ 
Control firm obs. & 16,176 & 16,318 & 16,410 & 16,176 & 16,318 & 16,410 \\ 
Distinct treated firms & 1,651 & 1,657 & 1,658 & 1,651 & 1,657 & 1,658 \\ 
Distinct control firms & 3,558 & 3,577 & 3,590 & 3,558 & 3,577 & 3,590 \\ 
Observations & 21,600 & 21,762 & 21,880 & 21,600 & 21,762 & 21,880 \\ 
Adjusted R$^{2}$ & 0.179 & 0.199 & 0.209 & 0.727 & 0.733 & 0.734 \\ 
\hline \\[-1.8ex]
\\[-1.83ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & \multicolumn{3}{c}{FOR\_TO\_INST\_OWN} & \multicolumn{3}{c}{FOR\_TO\_INST\_BREADTH} \\ 
 & [-1,1] years & [-2,2] years & [-3,3] years & [-1,1] years & [-2,2] years & [-3,3] years \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
\multicolumn{6}{@{} l}{\textit{Panel B: Foreign-to-institution ownership and breadth}}
\\
\\
 AFTER & 0.007$^{*}$ & 0.008 & 0.011$^{***}$ & 0.003 & 0.006 & 0.011$^{***}$ \\ 
  & (0.004) & (0.006) & (0.004) & (0.004) & (0.004) & (0.004) \\ 
  TREATED & $-$0.005$^{***}$ & $-$0.006$^{***}$ & $-$0.007$^{***}$ & $-$0.004$^{***}$ & $-$0.004$^{***}$ & $-$0.004$^{***}$ \\ 
  & (0.001) & (0.002) & (0.002) & (0.001) & (0.001) & (0.001) \\ 
  AFTER\texttimes TREATED & 0.0001 & 0.002 & 0.002 & 0.003$^{***}$ & 0.004$^{**}$ & 0.004$^{**}$ \\ 
  & (0.001) & (0.003) & (0.002) & (0.001) & (0.001) & (0.001) \\ 
  LOG\_MKT\_CAP & 0.004$^{***}$ & 0.004$^{***}$ & 0.004$^{***}$ & 0.0004 & 0.001 & 0.001 \\ 
  & (0.001) & (0.001) & (0.001) & (0.002) & (0.002) & (0.002) \\ 
  BM\_RATIO & 0.0001 & $-$0.0002 & $-$0.002 & 0.003 & 0.002 & 0.001 \\ 
  & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) \\ 
  LEVERAGE & $-$0.002 & $-$0.003 & $-$0.002 & $-$0.002 & $-$0.003 & $-$0.003 \\ 
  & (0.004) & (0.003) & (0.003) & (0.003) & (0.003) & (0.002) \\ 
  ROA & $-$0.047$^{**}$ & $-$0.042 & $-$0.042 & $-$0.043$^{**}$ & $-$0.045$^{***}$ & $-$0.045$^{**}$ \\ 
  & (0.022) & (0.026) & (0.029) & (0.017) & (0.017) & (0.019) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Treated firm obs. & 5,424 & 5,444 & 5,470 & 5,424 & 5,444 & 5,470 \\ 
Control firm obs. & 16,176 & 16,318 & 16,410 & 16,176 & 16,318 & 16,410 \\ 
Distinct treated firms & 1,651 & 1,657 & 1,658 & 1,651 & 1,657 & 1,658 \\ 
Distinct control firms & 3,558 & 3,577 & 3,590 & 3,558 & 3,577 & 3,590 \\ 
Observations & 21,600 & 21,762 & 21,880 & 21,600 & 21,762 & 21,880 \\ 
Adjusted R$^{2}$ & 0.098 & 0.108 & 0.105 & 0.127 & 0.144 & 0.151 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{6}{r}{} \\ 
\end{longtable}
\normalsize

In Panel A, the difference-in-differences regression results of foreign ownership (*FOR_OWN*) for the one-year, two-year and three-year pre- and post-closure period are reported in columns (1)-(3), respectively. The regression coefficients of *AFTER* are positive and statistically significant in all three columns. In addition, the coefficient is the largest in the three-year window and the smallest in the one-year window. Although the regression models contain year fixed effects, these findings are consistent with the increasing trend of foreign ownership for both groups in Figure \ref{fig_parallel_trend1}, as the foreign ownership has an increasing pattern even within-year period. Moreover, the coefficients of *TREATED* are negative but close to zero and statistically insignificant in all three columns, indicating that there is no significant difference of foreign ownership between treatment and control firms. The coefficients of the variable of main interest \textit{AFTER}\texttimes\textit{TREATED} are negative in columns (1)-(2) and statistically insignificant. In column (3), the coefficient is positive and statistically insignificant. Hence, the results do not provide support for the second hypothesis that an exogenous increase in information asymmetry causes a decline in foreign ownership. The control variables have similar results as in the baseline setting, with notably positive and statistically significant results for *ROA*. Compared to baseline setting, the additional control variable *LOG_MKT_CAP* is positive and statistically significant in all three columns, which is intuitive and in line with the correlation matrix results in Table \ref{table_cor_matrix}. Based on adjusted R^2^, the models explain variation relatively well compared to the baseline results.

The results of foreign breadth (*FOR_BREADTH*) in Panel A are similarly reported in columns (4)-(6). The regression coefficients of *AFTER* are similarly positive and statistically significant in columns (1)-(3), although with slightly smaller estimates. The coefficients of *TREATED* are, on the contrary, positive and statistically insignificant. The coefficients of \textit{AFTER}\texttimes\textit{TREATED} are positive and statistically insignificant in all three columns. Hence, the results of foreign breadth do neither provide evidence for the second hypothesis. Interestingly, the coefficients of control variables are somewhat inconsistent with the previous results. *LOG_MKT_CAP* and *LEVERAGE* are still positive and statistically significant in all three columns, but *BM_RATIO* is positive and statistically significant and *ROA* is negative and statistically significant. Adjusted R^2^ is, on average, 0.73, implying relatively high explanatory power of the models and notably higher than in the case of foreign ownership. 

In Panel B, the regression coefficients of *AFTER* are positive for both *FOR_TO_INST_OWN* and *FOR_TO_INST_BREADTH* in all six columns and statistically significant in columns (1), (3) and (6), which implies an increasing trend in the dollar amount and number of foreign institutional investors, compared to all institutional investors. On the other hand, *TREATED* is negative and statistically significant in all six columns, implying that treated firms have relatively low dollar amount and number of foreign institutional investors compared to all institutionals. \textit{AFTER}\texttimes\textit{TREATED} is positive in all six columns, statistically insignificant in columns (1)-(3) and statistically significant in columns (4)-(6). Hence, the results do not provide support for the second hypothesis in columns (1)-(3) and in columns (4)-(6) the results provide even opposing results. Nonetheless, these opposing results are to some extent downgraded in Figure \ref{fig_parallel_trend1}, in which the treatment group slightly catches the control group, but there is no clear drop in breadth measure for either groups. The control variables are mainly statistically insignificant, with the exception of statistically significant negative coefficients of *ROA*. Adjusted R^2^ is ca. 0.12 and hence models do not explain a lot of variation.

Overall, the results of Table \ref{table_h2_1} give no evidence of the negative causal effect of information asymmetry on foreign ownership. In fact, the results provide even some opposing evidence of positive causal effect of information asymmetry on the number of foreign institutional investors compared to all institutional investors. Nonetheless, I do not find opposing results significant enough, when compared to the results in Panel A and of Figure \ref{fig_parallel_trend1}.

## 6.3 The results of the quasi-natural experiment by investor type

In this section, I study the causal effect of asymmetric information on foreign ownership more in-depth by using different types of foreign institutional investors. I identify informed and non-informed foreign investors by using classifications by @bushee2001institutional, who define different institutional investors in 13F data as either "dedicated", "transient" or "quasi-indexing" investors. Dedicated investors are the most informed ones of these and prefer large and stable holdings in a small number of firms. Transient investors have highly diversified portfolios and are focused on short-term earnings and therefore their portfolios have high turnover. Quasi-indexing investors have highly diversified and low turnover portfolios, with a passive buy-and-hold strategy.

Based on these classifications, I compute the same foreign-ownership specific variables for classification groups "Quasi", including quasi-indexing foreign investors, and "Non-quasi", including both transient and dedicated foreign investors. Since there are not enough observations for dedicated foreign investors, I include only two classification groups. These classification groups affect only the nominator of these variables. For instance, *FOR_OWN* for dedicated investors is defined as the number of a firm’s shares held by foreign dedicated institutions divided by the firm’s total shares outstanding (CRSP) at the end of a quarter. With these variables, I compute similar difference-in-differences regression analysis than in the section 6.2, with dependent and control variables calculated for one-year before and after brokerage closures. Table \ref{table_h2_2} presents the results.

Based on the results of Table \ref{table_h2_2}, the regression coefficients of *AFTER* and *TREATED* are mainly insignificant in the columns of *FOR_OWN* and *FOR_BREADTH*, indicating minor differences between the groups. Interestingly, *LOG_MKT_CAP* is positive and statistically significant for quasi but not non-quasi foreign investors  in columns (1) and (2). This is intuitive, as the holdings of quasi-investors are concentrated on large firms due to value-weighted indices. Moreover, quasi investors invest more in profitable firms than non-quasi ones. Nonetheless, there are no significant results for \textit{AFTER\texttimes TREATED} in columns (1)-(4). Based on Adjusted R^2^, explanatory power of the first four models are similar to the main quasi-natural results, but the model of *FOR_OWN* for non-quasi investors is relatively low.

``` {r, results='asis', echo = FALSE, eval=FALSE}

library(tidyverse)
library(lfe)
library(stargazer)

did_regression_matched1 <- read_rds("results/did_regression_matched1.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER,
         sic_code = str_sub(sic_code, 1, 4),
         FOR_OWN_NONQUASI = FOR_OWN_DEDICATED + FOR_OWN_TRANSIENT,
         FOR_BREADTH_NONQUASI = FOR_BREADTH_DEDICATED + FOR_BREADTH_TRANSIENT,
         FOR_TO_INST_OWN_NONQUASI = FOR_TO_INST_OWN_DEDICATED + FOR_TO_INST_OWN_TRANSIENT,
         FOR_TO_INST_BREADTH_NONQUASI = FOR_TO_INST_BREADTH_DEDICATED + FOR_TO_INST_BREADTH_TRANSIENT)

did_model1 <- felm(FOR_OWN_QUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model2 <- felm(FOR_OWN_NONQUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model3 <- felm(FOR_BREADTH_QUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model4 <- felm(FOR_BREADTH_NONQUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model5 <- felm(FOR_TO_INST_OWN_QUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model6 <- felm(FOR_TO_INST_OWN_NONQUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model7 <- felm(FOR_TO_INST_BREADTH_QUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model8 <- felm(FOR_TO_INST_BREADTH_NONQUASI ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO + LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)


did_list <- list(did_model1, did_model2, did_model3, did_model4,
                 did_model5, did_model6, did_model7, did_model8)

treated_obs <- did_regression_matched1 %>% filter(TREATED == 1) %>% 
  group_by(TREATED) %>% summarise(n = n()) %>% ungroup() %>% pluck("n") %>% 
  format(big.mark = ",")

control_obs <- did_regression_matched1 %>% filter(TREATED == 0) %>% 
  group_by(TREATED) %>% summarise(n = n()) %>% ungroup() %>% pluck("n") %>% 
  format(big.mark = ",")

treated_distinct <- did_regression_matched1 %>% filter(TREATED == 1) %>% 
  group_by(TREATED) %>% summarise(n = n_distinct(permno)) %>% ungroup() %>% pluck("n") %>% 
  format(big.mark = ",")

control_distinct <- did_regression_matched1 %>% filter(TREATED == 0) %>% 
  group_by(TREATED) %>% summarise(n = n_distinct(permno)) %>% ungroup() %>% pluck("n") %>% 
  format(big.mark = ",")

obs <- did_regression_matched1 %>%
  summarise(n = n()) %>% ungroup() %>% pluck("n") %>% 
  format(big.mark = ",")

stargazer(did_list, title = "\\textbf{Difference-in-differences regression analysis of foreign ownership and breadth by institutional ownership and analyst coverage}\\newline\\scriptsize This table reports the results",
          label = "table_h2_2",
          header = F,
          dep.var.labels.include = F,
          dep.var.labels =c("FOR\\_OWN", "FOR\\_BREADTH"),
          column.labels = rep(c("Quasi", "Non-quasi"), times = 4),
          covariate.labels = c("AFTER", "TREATED", "AFTER\\texttimes TREATED", "LOG\\_MKT\\_CAP", "BM\\_RATIO", "LEVERAGE", "ROA"),
          omit.stat = c("ser", "rsq", "n"),
          add.lines = list(c("Industry fixed effects", rep("Yes", times = 8)),
                           c("Year fixed effects", rep("Yes", times = 8)),
                           c("Treated firm obs.", rep(treated_obs, times = 8)),
                           c("Control firm obs.", rep(control_obs, times = 8)),
                           c("Distinct treated firms", rep(treated_distinct, times = 8)),
                           c("Distinct control firms", rep(control_distinct, times = 8)),
                           c("Observations", rep(obs, times = 8))),
          type = 'latex',
          notes.label = "",
          notes.append = F,
          column.sep.width = "1pt",
          notes = "",
          font.size = "footnotesize",
          no.space = T)


```

\renewcommand\arraystretch{0.63}
\begin{landscape}
\captionsetup{width=1.0\linewidth}
\footnotesize
\begin{longtable}{@{\extracolsep{24pt}}lcccccccc} 
  \caption[Difference-in-differences regression analysis of foreign ownership-specific variables by investor type]{\textbf{Difference-in-differences regression analysis of foreign ownership-specific variables by investor type}\newline\scriptsize This table reports the results of the difference-in-differences regression analysis of ownership-specific variables by different classifications of institutional investor types \citep{bushee2001institutional}. The classification group \textit{Quasi} contains quasi-indexing investors and \textit{Non-quasi} transient and dedicated investors. For all stocks, I compute averages of the dependent variables and control variables in all columns over the quarters [-4,-1] and over the quarters [1,4], with the brokerage closure occurring in quarter 0. The control variables are book-to-market ratio (\textit{BM\_RATIO}), leverage (\textit{LEVERAGE}) and return on assets (\textit{ROA}). I include industry and year fixed effects in all regressions. Standard errors are clustered by the industry and year level and reported in parentheses. \textit{FOR\_OWN} and \textit{FOR\_BREADTH} are winsorized at the top to a maximum of 1. Control variables are winsorized at the top and bottom 1\%. Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. *, ** and *** denote the statistical significance at the 10\%, 5\% and 1\% level, respectively. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.} 
  \label{table_h2_2} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{8}{c}{\textit{Dependent variable:}} \\ 
\cline{2-9} 
\\[-1.8ex] & \multicolumn{2}{c}{FOR\_OWN} & \multicolumn{2}{c}{FOR\_BREADTH} & \multicolumn{2}{c}{FOR\_TO\_INST\_OWN} & \multicolumn{2}{c}{FOR\_TO\_INST\_BREADTH} \\ 
 & Quasi & Non-quasi & Quasi & Non-quasi & Quasi & Non-quasi & Quasi & Non-quasi \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
\hline \\[-1.8ex] 
 AFTER & 0.008$^{***}$ & 0.0001 & 0.001 & $-$0.0001 & 0.008$^{**}$ & $-$0.002 & 0.005 & $-$0.002 \\ 
  & (0.002) & (0.004) & (0.0005) & (0.0004) & (0.004) & (0.006) & (0.006) & (0.008) \\ 
  TREATED & $-$0.0002 & $-$0.001 & 0.00004 & 0.0003$^{***}$ & $-$0.002 & $-$0.003$^{**}$ & $-$0.002$^{*}$ & $-$0.002 \\ 
  & (0.001) & (0.001) & (0.0004) & (0.0001) & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  AFTER\texttimes TREATED & $-$0.001 & 0.0002 & 0.0002 & $-$0.0001 & $-$0.002$^{***}$ & 0.002$^{*}$ & 0.001 & 0.002 \\ 
  & (0.001) & (0.001) & (0.0002) & (0.0001) & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  LOG\_MKT\_CAP & 0.004$^{***}$ & 0.001 & 0.001$^{***}$ & 0.001$^{***}$ & 0.003$^{**}$ & $-$0.0004 & $-$0.001 & 0.002$^{***}$ \\ 
  & (0.001) & (0.0004) & (0.0003) & (0.0001) & (0.001) & (0.001) & (0.002) & (0.001) \\ 
  BM\_RATIO & 0.002 & $-$0.001$^{*}$ & 0.001$^{***}$ & 0.001$^{***}$ & $-$0.0001 & $-$0.001 & 0.002 & 0.001 \\ 
  & (0.002) & (0.001) & (0.0003) & (0.00005) & (0.002) & (0.001) & (0.002) & (0.001) \\ 
  LEVERAGE & 0.004 & $-$0.002 & 0.001$^{**}$ & 0.001$^{***}$ & 0.003 & $-$0.009$^{*}$ & 0.003 & $-$0.003 \\ 
  & (0.002) & (0.003) & (0.0003) & (0.0003) & (0.004) & (0.005) & (0.002) & (0.002) \\ 
  ROA & 0.044$^{***}$ & 0.027$^{***}$ & $-$0.004$^{**}$ & $-$0.004$^{***}$ & $-$0.042$^{***}$ & 0.006 & $-$0.031$^{**}$ & $-$0.007 \\ 
  & (0.012) & (0.004) & (0.002) & (0.001) & (0.013) & (0.015) & (0.013) & (0.008) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Treated firm obs. & 5,424 & 5,424 & 5,424 & 5,424 & 5,424 & 5,424 & 5,424 & 5,424 \\ 
Control firm obs. & 16,176 & 16,176 & 16,176 & 16,176 & 16,176 & 16,176 & 16,176 & 16,176 \\ 
Distinct treated firms & 1,651 & 1,651 & 1,651 & 1,651 & 1,651 & 1,651 & 1,651 & 1,651 \\ 
Distinct control firms & 3,558 & 3,558 & 3,558 & 3,558 & 3,558 & 3,558 & 3,558 & 3,558 \\ 
Observations & 21,600 & 21,600 & 21,600 & 21,600 & 21,600 & 21,600 & 21,600 & 21,600 \\ 
Adjusted R$^{2}$ & 0.261 & 0.083 & 0.653 & 0.736 & 0.166 & 0.088 & 0.273 & 0.155 \\   
\hline 
\hline \\[-1.8ex] 
\multicolumn{9}{r}{} \\ 
\end{longtable}
\end{landscape}

In columns (5)-(8), *TREATED* is negatively associated with *FOR_TO_INST_OWN* for non-quasi investors and on the other hand, negatively associated with *FOR_TO_INST_BREADTH* for quasi investors. Compared to domestic investors, foreign investors' dollar amount holdings increase relatively more in after brokerage closure period. \textit{AFTER\texttimes TREATED} is significantly negative for quasi investors in column (5) and significantly positive for non-quasi investors in column (6). This is counterintuitive to some extent. In general, quasi investors should not react actively to information asymmetry shock of stocks, since their portfolio holdings are fixed to indices. However, index constituents are typically determined based on firm size. As the brokerage closures affect mostly large firms, index rebalancing might be an explanation for quasi investors' negative coefficient. Similar to the main results, *ROA* is significantly negative in columns (5) and (7), and other control variables are mainly in line with the previous findings. 

## 6.4 The results of the quasi-natural experiment by institutional ownership and analyst coverage

In this section, I test the causal effect of asymmetric information on foreign ownership in a subset analysis. As hypothesized in Hypothesis 3, I state that the negative causal effect should be stronger in firms with low institutional ownership or low analyst coverage. I test this with the similar model as in Section 6.2, but sample divided to the lowest and highest quartiles of analyst coverage and institutional ownership. Table \ref{table_h3_1} reports the results of foreign ownership (*FOR_OWN*) and breadth (*FOR_BREADTH*).

``` {r, results='asis', echo = FALSE, eval=FALSE}

library(tidyverse)
library(lfe)
library(stargazer)

did_regression_matched1 <- read_rds("results/did_regression_matched1.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER,
         sic_code = str_sub(sic_code, 1,2)) %>%
  group_by(permno, event_date) %>% 
  mutate(inst_mean = mean(INST_OWN),
         analyst_mean = mean(ANALYST_COVERAGE)) %>% 
  ungroup() %>% 
  mutate(inst_percent = percent_rank(inst_mean),
         analyst_percent = percent_rank(analyst_mean))

did_regression_matched1_low_inst <- did_regression_matched1 %>% 
  filter(inst_percent <= 0.25)

did_regression_matched1_high_inst <- did_regression_matched1 %>% 
  filter(inst_percent >= 0.75)

did_regression_matched1_low_analyst <- did_regression_matched1 %>% 
  filter(analyst_percent <= 0.25)

did_regression_matched1_high_analyst <- did_regression_matched1 %>% 
  filter(analyst_percent >= 0.75)

did_model1 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_inst)

did_model2 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_inst)

did_model3 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_analyst)

did_model4 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_analyst)

did_model5 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_inst)

did_model6 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_inst)

did_model7 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_analyst)

did_model8 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_analyst)

did_list <- list(did_model1, did_model2, did_model3, did_model4,
                 did_model5, did_model6, did_model7, did_model8)

treated_obs <- map_dbl(list(did_regression_matched1_low_inst, did_regression_matched1_high_inst, did_regression_matched1_low_analyst, did_regression_matched1_high_analyst), ~  .x %>% filter(TREATED == 1) %>% 
  group_by(TREATED) %>% summarise(n = n()) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

control_obs <- map_dbl(list(did_regression_matched1_low_inst, did_regression_matched1_high_inst, did_regression_matched1_low_analyst, did_regression_matched1_high_analyst), ~  .x %>% filter(TREATED == 0) %>% 
  group_by(TREATED) %>% summarise(n = n()) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

treated_distinct <- map_dbl(list(did_regression_matched1_low_inst, did_regression_matched1_high_inst, did_regression_matched1_low_analyst, did_regression_matched1_high_analyst), ~  .x %>%
                              filter(TREATED == 1) %>% 
                              group_by(TREATED) %>% summarise(n = n_distinct(permno)) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

control_distinct <- map_dbl(list(did_regression_matched1_low_inst, did_regression_matched1_high_inst, did_regression_matched1_low_analyst, did_regression_matched1_high_analyst), ~  .x %>% filter(TREATED == 0) %>% 
  group_by(TREATED) %>% summarise(n = n_distinct(permno)) %>% ungroup() %>% pluck("n")) %>%
  format(big.mark = ",")

obs <- map_dbl(list(did_regression_matched1_low_inst, did_regression_matched1_high_inst, did_regression_matched1_low_analyst, did_regression_matched1_high_analyst), ~  .x %>%
 summarise(n = n()) %>% ungroup() %>% pluck("n")) %>% 
  format(big.mark = ",")

stargazer(did_list, title = "\\textbf{Difference-in-differences regression analysis of foreign ownership and breadth by institutional ownership and analyst coverage}\\newline\\small This table reports the results",
          label = "table_h3",
          header = F,
          dep.var.labels =c("FOR\\_OWN", "FOR\\_BREADTH"),
          column.labels = rep(c("IO < Q\\textsubscript{0.25}", "IO > Q\\textsubscript{0.75}", "AC < Q\\textsubscript{0.25}", "AC > Q\\textsubscript{0.75}"), times = 2),
          covariate.labels = c("AFTER", "TREATED", "AFTER\\texttimes TREATED", "LOG\\_MKT\\_CAP", "BM\\_RATIO", "LEVERAGE", "ROA"),
          omit.stat = c("ser", "rsq", "n"),
          add.lines = list(c("Industry fixed effects", rep("Yes", times = 8)),
                           c("Year fixed effects", rep("Yes", times = 8)),
                           c("Treated firm obs.", rep(treated_obs, times = 2)),
                           c("Control firm obs.", rep(control_obs, times = 2)),
                           c("Distinct treated firms", rep(treated_distinct, times = 2)),
                           c("Distinct control firms", rep(control_distinct, times = 2)),
                           c("Observations", rep(obs, times = 2))),
          type = 'latex',
          notes.label = "",
          notes.append = F,
          column.sep.width = "1pt",
          notes = "",
          font.size = "footnotesize",
          no.space = T)


did_model1 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_inst)

did_model2 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_inst)

did_model3 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_analyst)

did_model4 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_analyst)

did_model5 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_inst)

did_model6 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_inst)

did_model7 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_low_analyst)

did_model8 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + LOG_MKT_CAP + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1_high_analyst)

did_list <- list(did_model1, did_model2, did_model3, did_model4,
                 did_model5, did_model6, did_model7, did_model8)

stargazer(did_list, title = "\\textbf{Difference-in-differences regression analysis of foreign ownership and breadth by institutional ownership and analyst coverage}\\newline\\small This table reports the results",
          label = "table_h3_1",
          header = F,
          dep.var.labels =c("FOR\\_TO\\_INST\\_OWN", "FOR\\_TO\\_INST\\_BREADTH"),
          column.labels = rep(c("IO < Q\\textsubscript{0.25}", "IO > Q\\textsubscript{0.75}", "AC < Q\\textsubscript{0.25}", "AC > Q\\textsubscript{0.75}"), times = 2),
          covariate.labels = c("AFTER", "TREATED", "AFTER\\texttimes TREATED", "LOG\\_MKT\\_CAP", "BM\\_RATIO", "LEVERAGE", "ROA"),
          omit.stat = c("ser", "rsq", "n"),
          add.lines = list(c("Industry fixed effects", rep("Yes", times = 8)),
                           c("Year fixed effects", rep("Yes", times = 8)),
                           c("Treated firm obs.", rep(treated_obs, times = 2)),
                           c("Control firm obs.", rep(control_obs, times = 2)),
                           c("Distinct treated firms", rep(treated_distinct, times = 2)),
                           c("Distinct control firms", rep(control_distinct, times = 2)),
                           c("Observations", rep(obs, times = 2))),
          type = 'latex',
          notes.label = "",
          notes.append = F,
          column.sep.width = "1pt",
          notes = "",
          font.size = "footnotesize",
          no.space = T)

```

\renewcommand\arraystretch{0.64}
\begin{landscape}
\captionsetup{width=1.0\linewidth}
\footnotesize
\begin{longtable}{@{\extracolsep{22pt}}lcccccccc} 
  \caption[Difference-in-differences regression analysis of foreign ownership-specific variables by institutional ownership and analyst coverage]{\textbf{Difference-in-differences regression analysis of foreign ownership-specific variables by institutional ownership and analyst coverage}\newline\scriptsize This table reports the results of the difference-in-differences regression analysis of ownership-specific variables in subsamples of low (high) institutional ownership and analyst coverage. In Panel A, the dependent variables are foreign ownership (\textit{FOR\_OWN}) and foreign breadth (\textit{FOR\_BREADTH}). In Panel B, the dependent variables are foreign-to-institution ownership (\textit{FOR\_TO\_INST\_OWN}) and foreign-to-institution breadth (\textit{FOR\_TO\_INST\_BREADTH}). In the first (fifth) and second (sixth) column, the sample is restricted to firms that have in each brokerage closure event institutional ownership below first and third quartile, respectively. Similarly, in the third (seventh) and fourth (eighth) column, the sample is restricted to firms with analyst coverage below first and third quartile, respectively. For all stocks, I compute averages of the dependent variables and control variables in all columns over the quarters [-4,-1] and over the quarters [1,4], with the brokerage closure occurring in quarter 0. The control variables are book-to-market ratio (\textit{BM\_RATIO}), leverage (\textit{LEVERAGE}) and return on assets (\textit{ROA}). I include industry and year fixed effects in all regressions. Standard errors are clustered by the industry and year level and reported in parentheses. \textit{FOR\_OWN} and \textit{FOR\_BREADTH} are winsorized at the top to a maximum of 1. Control variables are winsorized at the top and bottom 1\%. Table \ref{table_variable_definitions} in Appendix provides a detailed list of variable definitions. *, ** and *** denote the statistical significance at the 10\%, 5\% and 1\% level, respectively. Sample period: 1997-2010. Sources: CRSP, COMPUSTAT, 13F and IBES.} 
  \label{table_h3_1} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{8}{c}{\textit{Dependent variable:}} \\ 
\cline{2-9} 
\\[-1.8ex] & \multicolumn{4}{c}{FOR\_OWN} & \multicolumn{4}{c}{FOR\_BREADTH} \\ 
 & IO < Q\textsubscript{0.25} & IO > Q\textsubscript{0.75} & AC < Q\textsubscript{0.25} & AC > Q\textsubscript{0.75} & IO < Q\textsubscript{0.25} & IO > Q\textsubscript{0.75} & AC < Q\textsubscript{0.25} & AC > Q\textsubscript{0.75} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
\hline \\[-1.8ex] 
\multicolumn{6}{@{} l}{\textit{Panel A: Foreign ownership and breadth}}
\\
\\
 AFTER & 0.005$^{***}$ & 0.012$^{***}$ & 0.006$^{***}$ & 0.011$^{***}$ & 0.0003$^{***}$ & 0.0004 & 0.0001 & 0.001$^{***}$ \\ 
  & (0.001) & (0.004) & (0.002) & (0.003) & (0.0001) & (0.0004) & (0.0001) & (0.0005) \\ 
  TREATED & 0.001 & 0.003 & $-$0.003 & $-$0.002 & 0.00004 & 0.0004 & $-$0.0002$^{**}$ & 0.0004 \\ 
  & (0.001) & (0.002) & (0.003) & (0.002) & (0.0001) & (0.0004) & (0.0001) & (0.0003) \\ 
  AFTER\texttimes TREATED & $-$0.001 & $-$0.003 & $-$0.0002 & $-$0.004$^{***}$ & 0.0001$^{***}$ & 0.00003 & 0.0002$^{***}$ & $-$0.0002 \\ 
  & (0.001) & (0.003) & (0.001) & (0.001) & (0.00002) & (0.0002) & (0.0001) & (0.0003) \\ 
  LOG\_MKT\_CAP & 0.004$^{***}$ & 0.004$^{**}$ & 0.006$^{***}$ & 0.001 & 0.001$^{***}$ & 0.004$^{***}$ & 0.001$^{***}$ & 0.005$^{***}$ \\ 
  & (0.0005) & (0.002) & (0.002) & (0.001) & (0.0001) & (0.0004) & (0.0002) & (0.0003) \\ 
  BM\_RATIO & 0.001 & $-$0.001 & $-$0.002 & 0.008$^{*}$ & 0.001$^{***}$ & 0.001$^{**}$ & 0.0004$^{***}$ & 0.002$^{***}$ \\ 
  & (0.001) & (0.004) & (0.001) & (0.005) & (0.0001) & (0.001) & (0.0001) & (0.0005) \\ 
  LEVERAGE & $-$0.0001 & $-$0.007 & 0.003 & 0.002 & 0.001$^{**}$ & 0.0001 & 0.0004$^{***}$ & 0.001 \\ 
  & (0.006) & (0.005) & (0.004) & (0.007) & (0.0004) & (0.0004) & (0.0001) & (0.001) \\ 
  ROA & 0.015$^{**}$ & 0.008 & 0.054$^{***}$ & 0.074$^{***}$ & $-$0.004$^{**}$ & $-$0.011$^{***}$ & $-$0.002$^{***}$ & $-$0.008 \\ 
  & (0.007) & (0.033) & (0.015) & (0.028) & (0.002) & (0.001) & (0.001) & (0.005) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Treated firm obs. & 1,050 & 1,412 &   878 & 1,978 & 1,050 & 1,412 &   878 & 1,978 \\ 
Control firm obs. & 4,350 & 3,988 & 4,618 & 3,360 & 4,350 & 3,988 & 4,618 & 3,360 \\ 
Distinct treated firms & 443 & 453 & 411 & 433 & 443 & 453 & 411 & 433 \\ 
Distinct control firms & 1,423 &   991 & 1,681 &   561 & 1,423 &   991 & 1,681 &   561 \\ 
Observations & 5,400 & 5,400 & 5,496 & 5,338 & 5,400 & 5,400 & 5,496 & 5,338 \\ 
Adjusted R$^{2}$ & 0.196 & 0.141 & 0.146 & 0.219 & 0.612 & 0.742 & 0.573 & 0.790 \\
\hline \\[-1.8ex]
\\[-1.83ex] 
 & \multicolumn{8}{c}{\textit{Dependent variable:}} \\ 
\cline{2-9} 
\\[-1.8ex] & \multicolumn{4}{c}{FOR\_TO\_INST\_OWN} & \multicolumn{4}{c}{FOR\_TO\_INST\_BREADTH} \\ 
 & IO < Q\textsubscript{0.25} & IO > Q\textsubscript{0.75} & AC < Q\textsubscript{0.25} & AC > Q\textsubscript{0.75} & IO < Q\textsubscript{0.25} & IO > Q\textsubscript{0.75} & AC < Q\textsubscript{0.25} & AC > Q\textsubscript{0.75} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8)\\ 
\hline \\[-1.8ex] 
\multicolumn{6}{@{} l}{\textit{Panel B: Foreign-to-institution ownership and breadth}}
\\
\\
 AFTER & 0.004 & 0.010$^{**}$ & 0.003 & 0.012$^{***}$ & $-$0.005 & 0.006 & $-$0.006 & 0.012$^{**}$ \\ 
  & (0.003) & (0.004) & (0.003) & (0.005) & (0.004) & (0.004) & (0.004) & (0.005) \\ 
  TREATED & $-$0.005 & 0.003 & $-$0.009 & $-$0.005$^{**}$ & $-$0.008$^{***}$ & 0.002 & $-$0.009$^{**}$ & $-$0.001 \\ 
  & (0.004) & (0.002) & (0.006) & (0.002) & (0.002) & (0.002) & (0.004) & (0.002) \\ 
  AFTER\texttimes TREATED & 0.001 & $-$0.002 & 0.002 & $-$0.005$^{**}$ & 0.008$^{***}$ & 0.001 & 0.008$^{***}$ & $-$0.003$^{*}$ \\ 
  & (0.002) & (0.003) & (0.003) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) \\ 
  LOG\_MKT\_CAP & 0.007$^{***}$ & 0.006$^{***}$ & 0.006$^{***}$ & 0.005$^{***}$ & $-$0.001 & 0.010$^{***}$ & $-$0.002 & $-$0.002 \\ 
  & (0.001) & (0.002) & (0.002) & (0.001) & (0.002) & (0.003) & (0.003) & (0.002) \\ 
  BM\_RATIO & $-$0.002 & $-$0.0002 & $-$0.009$^{**}$ & 0.022$^{**}$ & 0.003 & 0.002 & 0.0003 & 0.001 \\ 
  & (0.003) & (0.004) & (0.004) & (0.009) & (0.003) & (0.002) & (0.004) & (0.003) \\ 
  LEVERAGE & 0.016 & $-$0.011$^{**}$ & 0.004 & $-$0.008 & 0.001 & $-$0.001 & $-$0.006 & $-$0.006 \\ 
  & (0.015) & (0.005) & (0.011) & (0.014) & (0.008) & (0.004) & (0.005) & (0.007) \\ 
  ROA & $-$0.037 & $-$0.006 & $-$0.066 & $-$0.012 & 0.002 & $-$0.108$^{***}$ & $-$0.023 & $-$0.076$^{***}$ \\ 
  & (0.023) & (0.043) & (0.044) & (0.073) & (0.017) & (0.028) & (0.017) & (0.023) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Treated firm obs. & 1,050 & 1,412 &   878 & 1,978 & 1,050 & 1,412 &   878 & 1,978 \\ 
Control firm obs. & 4,350 & 3,988 & 4,618 & 3,360 & 4,350 & 3,988 & 4,618 & 3,360 \\ 
Distinct treated firms & 443 & 453 & 411 & 433 & 443 & 453 & 411 & 433 \\ 
Distinct control firms & 1,423 &   991 & 1,681 &   561 & 1,423 &   991 & 1,681 &   561 \\ 
Observations & 5,400 & 5,400 & 5,496 & 5,338 & 5,400 & 5,400 & 5,496 & 5,338 \\ 
Adjusted R$^{2}$ & 0.123 & 0.150 & 0.076 & 0.195 & 0.109 & 0.374 & 0.067 & 0.404 \\  
\hline 
\hline \\[-1.8ex] 
\multicolumn{9}{r}{} \\ 
\end{longtable}
\end{landscape}

In Panel A, the regression coefficients of *AFTER* and *TREATED* are similar compared to the main quasi-natural experiment results in Table \ref{table_h2_1}. The coefficients of \textit{AFTER}\texttimes\textit{TREATED} provide opposing results to Hypothesis 3. Both institutional ownership and analyst coverage have lower coefficients in the third quartile than in the first quartile for *FOR_OWN* and *FOR_BREADTH*. The coefficient is negative and statistically significant in column (4), implying that foreign institutional investors are more driven away of the treated stocks that have higher analyst coverage. This is contrary to the hypothesis that the negative effect of the information asymmetry shock should be emphasized in stocks with low analyst coverage, since the loss of even one analyst is crucial to the amount of information. Moreover, the coefficients of foreign breadth with low institutional ownership and analyst coverage are positive and statistically significant, compared to close to zero and insignificant coefficients with high institutional ownership and analyst coverage. The control variables are mainly in line with the main results of quasi-natural experiment. Adjusted R^2^ is especially higher in models of high institutional ownership and analyst coverage, although the low sample size somewhat downplays its relevance.

Panel B provides a similar pattern of opposing results. The regression coefficients of \textit{AFTER}\texttimes\textit{TREATED} are smaller with high institutional ownership and analyst coverage in all models. Notably, the dollar amount and number of foreign institutional investors compared to domestic ones are negative and statistically significant, when analyst coverage is high. Overall, the counterintuitive results might be explained by the fact that treated firms are, in general, large firms with high foreign ownership, institutional ownership and analyst coverage. Hence, there is a scope for larger variation in foreign ownership of the treated firms than in samples of low institutional ownership and analyst coverage.

# 7 Robustness tests

In this section, I conduct several robustness tests for the empirical results of this study. First, I test the credibility of the quasi-natural experiment identification. Second, I perform an alternative selection of the control group used in difference-in-differences regression. Finally, as the main results rely on the findings of @kelly2012testing and @derrien2013real that exogenous reductions in analyst coverage results in increased information asymmetry, I examine the difference-in-differences regression analysis with instrumental variable approach in which information asymmetry measure is used as as instrument variable. I present the findings in Appendix.

## 7.1 The credibility of the quasi-natural experiment identification

I test the credibility of the quasi-natural experiment identification by examining the analyst coverage between treatment and control groups around brokerage closures. To keep sample comparable with my previous results and sample size sufficient, the control group is matched with the treatment group by a ratio of 3 and with same covariates. @kelly2012testing use a ratio of 5 and @derrien2013real a ratio of 1 with slightly different covariates, but mostly I find my data processing to replicate their versions. Figure \ref{fig_parallel_trend_analyst} reports the results.

As shown in Figure \ref{fig_parallel_trend_analyst}, analyst coverage for both treatment and control groups increases notably before the event. The pre-treatment parallel trend assumption is mostly satisfied, although the number of analysts increases to some extent relatively more in the treatment group. Notably, the treatment group has ca. 2-3.5 more analysts covering than the control group, although the control group is matched with analyst coverage as one covariate. There is a significant drop in analyst coverage during the event quarter for the treatment group. The control group decreases also, but only slightly compared to the treatment group. Moreover, the drop is limited only to three quarters after the event, as the number of analysts stabilizes after three quarters in the treatment group. Hence, I find supporting evidence that my identification of the quasi-natural experiment is consistent with the data processing methods of @derrien2013real and @kelly2012testing. 

## 7.2 Alternative selection of the control group

As another robustness check, I test the difference-in-differences regression analysis with an alternative selection of the control group. Contrary to the main results of the quasi-natural experiment, I do not match control firms on any covariates with the treatment group. I only require the control firms to be covered one year before the brokerage closure event to keep only actively covered firms. Moreover, control firms must have non-missing observations of dependent and control variables, when merging IBES data set with CRSP, COMPUSTAT and 13F data. Based on this selection, I conduct a similar difference-in-differences regression analysis with observations one year before and after the event. Table \ref{table_h2_nonmatched} presents the results.

Table \ref{table_h2_nonmatched} provides similarly no supporting evidence for the second hypothesis of the negative causal effect between asymmetric information and foreign ownership. In all columns, the regression coefficients of \textit{AFTER\texttimes TREATED} are positive but insignificant. Mostly, foreign ownership and breadth when comparing to whole market or only to institutional investors are associated with large market capitalization. When compared to institutional investors, foreign institutional investors invest relatively more in growth, non-levered and less profitable firms. Moreover, foreign institutional investors invest relatively less in the treated firms, when compared to all institutional investors. Overall, the results are mostly in line with the main results and do not change the conclusion of the difference-in-differences regression results.

## 7.3 The quasi-natural experiment with instrumental variable approach

As the study relies heavily in the main quasi-natural experiment results on the findings of @kelly2012testing and @derrien2013real that exogenous reductions in analyst coverage leads to increased information asymmetry, I test the causal effect of information asymmetry on foreign ownership with instrumental variable approach. In the first-stage regression, I perform a similar difference-in-differences regression, but with an information asymmetry measure as the dependent variable. For the data availability and sufficient sample size reasons, I select only volume coefficient variation (*VCV~USD~*) and bid-ask spread (*BA_SPREAD*) as the dependent variables. I calculate *VCV~USD~* and *BA_SPREAD* in a similar manner with the main data processing but as quarter averages. The first-stage difference-in-differences regression of firm-quarter observations is as follows:

\begin{equation}
\label{eq_iv_1}
\begin{aligned}
IA\_MEASURE_{i,t} &= \beta_0 + \beta_{1}TREATED_{i} + \beta_{2}AFTER_{t} + \beta_{3}AFTER\times TREATED_{i,t}\\ &+ \beta_{5}BM\_RATIO_{i,t} + \beta_{6}LEVERAGE_{i,t} + \beta_{7}ROA_{i,t}\\ &+ YEAR_{t}+ INDUSTRY_{n} + u_{i,t}
\end{aligned}
\end{equation}

In the second-state regression, the fitted values of *IA_MEASURE* are used as an explanatory variable with several control variables. Similar to the baseline regression model, I exclude *LOG_MKT_CAP* from control variables in both first-stage and second-stage regressions due to a potential risk of multicollinearity. The second-state regression model is as follows:

\begin{equation}
\label{eq_iv_2}
\begin{aligned}
FOREIGN_{i,t} &= \beta_0 + \beta_{1}\hat{IA\_MEASURE_{i,t}} + \beta_{2}BM\_RATIO_{i,t}\\ &+ \beta_{3}LEVERAGE_{i,t}+ \beta_{4}ROA_{i,t}\\ &+ YEAR_{t}+ INDUSTRY_{n} + \varepsilon_{i,t}
\end{aligned}
\end{equation}

For comparability, I also examine the relationship of information asymmetry and foreign ownership-specific variables with a similar baseline panel regression (OLS) model but with firm-quarter observations. To test whether instruments *AFTER*, *TREATED* and \textit{AFTER\texttimes TREATED} are weak in relation to information asymmetry measures *VCV~USD~* and *BA_SPREAD*, I follow @stockyogo to examine the instruments' joint significance with clustered standard errors. As a result, I report the first-stage F-statistics. Table \ref{table_h2_iv} presents the results of the regressions.

In Panel A, volume coefficient variation (*VCV~USD~*) is used as the information asymmetry measure. As shown in column (1), the coefficient of *AFTER* is negative and significant, which is consistent with the findings of @lof2018asymmetric that VCV is on average decreasing over time. Similar to @lof2018asymmetric, *TREATED* is only slightly negative. Moreover, the variable of main interest \textit{AFTER\texttimes TREATED} is positive and statistically significant, indicating that information asymmetry of firms that are exposed to exogenous reductions in analyst coverage increases, which is consistent with @lof2018asymmetric. Control variables are mainly in line with my previous results, for instance *LOG_MKT_CAP* and *ROA* are negatively associated with information asymmetry. Based on adjusted R^2^, the model explains variation relatively well.

In OLS regressions, the coefficients of *VCV~USD~* are negative and significant in columns (2) and (4), negative and insignificant in column (6) and positive in column (8), consistent with the baseline regression results with firm-year observations. Nonetheless, *VCV~USD~* is more strongly negatively associated with asymmetric information in the second-stage instrumental variable regressions. This finding suggests that foreign institutional investors are driven away (both in dollar terms and in numbers relative to market or all institutions) from stocks that have experienced increase in information asymmetry due to exogenous reductions in analyst coverage. Hence, the result gives supporting evidence for the second hypothesis.

In Panel B, bid-ask spread (*BA_SPREAD*) is used as the information asymmetry measure. In column (1), different from results in Panel A, there is no average decrease of bid-ask spread over time and coefficient of \textit{AFTER\texttimes TREATED} is negative and insignificant. However, the coefficients of control variables are intuitive and in line with the previous results. Similar to Panel A, the coefficients of *BA_SPREAD* are negative in all OLS regressions and statistically significant in all OLS regressions, except with *FOR_TO_INST_BREADTH* as the dependent variable. However, the regression coefficients of *BA_SPREAD* in the second-stage instrumental variable regressions are positive and statistically insignificant in columns (3), (7) and (9) and negative and insignificant in column (5). Standard errors are relatively large, indicating that the model specification of instrumental regressions with bid-ask spread is problematic.

# 8 Discussion

The empirical results of this study provide strong supporting evidence of the negative relation between information asymmetry and foreign ownership. Consistent with the first hypothesis and previous literature, foreign institutional investors seem to prefer stocks with low information asymmetry, positive profitability and low book-to-market ratio. This result is strong in both dollar amount of foreign institutional holdings and also in the number of foreign institutional investors. Moreover, when comparing foreign institutional investors to domestic institutionals, foreign ones tend to avoid more strongly stocks with high asymmetric information in dollar terms. However, the results are mixed for different information asymmetry proxies, when comparing the number of foreign institutional investors to domestic ones.

Despite the strong evidence in the baseline setting, there is no evidence of the causal effect of information asymmetry on foreign ownership. The positive information asymmetry shock does not lead to a decrease in foreign dollar holdings or in the number of foreign institutional investors, when testing one, two or three years before and after the exogenous information asymmetry shocks. Furthermore, there is no evidence of the causal effect, when examining with different foreign institutional types. Quasi or non-quasi foreign investors do not significantly alter their holdings after the shocks or there is no significant changes in the number of investors. Moreover, this finding is not altered with different selection of the control group. However, the main results rely on the findings of @derrien2013real; @kelly2012testing that the exogenous reductions in analyst coverage due brokerage closures results in increase of information asymmetry. When testing with instrumental regressions, the results give some evidence that the foreign ownership is decreased relatively more in stocks that have an increase in information asymmetry due to the brokerage closures. Overall, the empirical results do not provide sufficient evidence for the second hypothesis that there is a negative causal effect between asymmetric information and foreign ownership.

According to the third hypothesis, the reduction of foreign ownership due to an information asymmetry shock should be emphasized in stocks with low analyst coverage or institutional ownership. Nonetheless, I fail to find support for this hypothesis. Although mainly insignificant and close to zero, the regression coefficients, in fact, give evidence that foreign ownership and breadth are more decreased in cases of high analyst coverage and institutional ownership. These opposing results may be due to that treated firms have high foreign ownership when analyst coverage and institutional ownership is high and therefore there is a possibility for larger variation.

To sum it up, I find strong negative relation between information asymmetry and foreign ownership, consistent with main existing literature. However, I examine the relation more in-depth with multiple information asymmetry proxies and various ownership-specific definitions for dependent variables. I fail to establish a negative causal effect between the aforementioned variables, even with robustness tests and subset analyses of investor types or analyst coverage and institutional ownership. One limitation of this study is not to address the potential reverse causality of the variables. Foreign ownership might be affecting information asymmetry or both variables might be affecting each other. I order to test this, the endogeneity of foreign ownership should be dealt with, for example instrumental variables to capture an exogenous variation. @bena2017foreign instrument foreign ownership with stock additions to the MSCI All Country World Index. However, the reverse causality examination is beyond the scope of this study and therefore I only suggest it for further research.

# 9 Conclusion

\clearpage
\addcontentsline{toc}{section}{References}
