---
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    citation_package: natbib
    keep_tex: true
mainfont: Times New Roman
bibliography: Bibliography.bib
biblio-style: chicagoa
csl: journal-of-financial-economics.csl
link-citations: yes
fontsize: 12pt
geometry: [top=3cm, bottom=2.5cm, right=2.5cm, left=3cm]
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{dcolumn}
- \usepackage{rotating}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{caption}
- \usepackage{tabularx}
- \usepackage{hhline}
- \usepackage{fixltx2e}
- \usepackage{hyperref}
- \usepackage{tocloft}
---

\captionsetup{labelfont=bf}
\newcommand\mycaption[2]{\caption{\textbf{#1}\newline\scriptsize#2}}

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

```
\pagenumbering{roman}
\setcounter{page}{3}
\renewcommand*{\contentsname}{Table of Contents}
\renewcommand{\cftfigfont}{Figure }
\renewcommand{\cfttabfont}{Table }
\tableofcontents
\newpage
\listoftables
\listoffigures
\newpage
\pagenumbering{arabic}

# 1 Introduction

Information asymmetry is a fundamentally important concept in finance and economics, since it influences most interactions between market participants, especially in cases of adverse selection and moral hazard. It is of particular interest to financial economists, as the fundamental reason of financial markets is to aggregate dispersed information into market prices. Hence, it is crucial to understand the effects of information asymmetry on trading behavior of investors and as a result, on the outcomes and operation of securities markets.

The presence of foreign investors has increased prominently in recent decades. For instance, according to the NYSE Fact Book, foreign ownership in US stocks has grown from 3% in 1970 to 11% in 2001. As a result, foreign ownership has drawn an interest from researchers and the existing literature provides studies of the effects of foreign investments on productivity, investment and growth of invested firms [@henry2000stock; @bekaert2005does; @bekaert2011financial] and also on stock price properties like liquidity, return volatility and the cost of capital [e.g. @bekaert2000foreign; @bae2004investibility; @bekaert2007liquidity]. Most of the existing literature finds an inverse relation between asymmetric information and foreign ownership [@jiang2004foreign; @choi2013foreign], using the timing and magnitude of intertemporal return-earnings associations, the probability of informed trading (PIN) and price non-synchronicity as proxy measures for information asymmetry. Furthermore, foreign investors tend to prefer stocks that have characteristics associated with low information asymmetry, such as large size and low leverage [@batten2015foreign].

Despite the findings of the inverse relationship between information asymmetry and foreign ownership, there are different interpretations of the causal effects of these two variables. @jiang2004foreign argue that foreign investors are attracted to stocks with low information asymmetry, since they avoid stocks with cross-corporate holdings. In contrast, @choi2013foreign argue that by improving corporate governance and disclosure quality, foreign investors improve the informativeness of stock prices (i.e. reduce information asymmetry). However, the studies lack a credible identification strategy of the causal effect and thus, this thesis is a first attempt, to the best of my knowledge, to examine the causality, using the quasi-experimental setting of brokerage closures by  @kelly2012testing. Accordingly, I construct a difference-in-differences estimation, using the findings of @kelly2012testing and @derrien2013real that an exogenous decrease in analyst coverage due to these brokerage closures increase the asymmetric information of the covered firms. As a dependent variable, I use various proxies for information asymmetry suggested by the existing literature.

# 2 Literature review

## 2.1 Information asymmetry and analyst coverage

Earlier literature studies asymmetric information in financial markets by examining the strategic behavior of investors. @kyle1985continuous studies the strategic behavior of investors by a market microstructure model in which uninformed trades follow Brownian motion and market makers see only the order imbalance which they fill with matching orders that are crossed at the market-clearing price. Orders are batched and therefore there are no bid and ask prices. The optimal trading behavior for the single informed investor is to exploit his information on trades gradually. In contrast, @glosten1985bid propose a microstructure model in which uninformed orders arrive as a Poisson process and orders are executed individually by market makers. They argue that due to informed investors, there is a positive bid-ask spread even when the market maker is risk-neutral and makes zero profits. 

Several researchers have developed various measures to estimate the magnitude of information asymmetry. Easley et al. (1996) use a market microstructure model inspired by @glosten1985bid in which trade order flows affect the beliefs of market participants. The information of trade order flow is analyzed to estimate the magnitude to which trade order flows convey different information for different securities. As a result, they construct the well-known measure of the probability of informed trading (PIN) of which different researchers have developed various versions [e.g.  @brown2004conference; @brown2007disclosure; @duarte2009pin; @easley2010factoring]. @johnson2017simple assume that informed investors trade more in options than uninformed investors. Based on the premise, they construct the multimarket information asymmetry (MIA) measure with daily trading volume data of stocks and options. @lof2018asymmetric propose an easily computed measure of volume coefficient variation (VCV). They argue that orders of uninformed (informed) liquidity seekers are uncorrelated (perfectly correlated) and informed orders need to be matched by market makers. From the distribution of total trading volume, they construct functions of the proportion of informed trade and show that the coefficient of variation (the ratio of standard deviation to the mean) of trading volume increases monotonically in the proportion of informed trade.

A great amount of literature finds that equity research analysts produce relevant and valuable information for investors and firms [e.g., @womack1996brokerage; @barber2001can; @jegadeesh2004analyzing; @loh2010analyst]. Furthermore, as providers of information of the covered firms, analysts are also monitoring these firms [@moyer1989security; @chung1996impact] and they help to reduce information asymmetry [@bushman2001financial; @healy2001information]. Accordingly, @kelly2012testing find in a quasi-experimental research setting that an exogenous decrease in analyst coverage of a firm results in an increase of information asymmetry. Subsequently, many researchers have applied the setting of @kelly2012testing to study the effects of exogenous variation in analyst coverage on corporate policies [@derrien2013real], innovation [@he2013dark] and corporate tax aggressiveness [@allen2016analyst].

## 2.2 Foreign ownership and information asymmetry

Foreign investors are generally thought to be less informed of local stock markets than local investors among finance practitioners and academics. Domestic investors are found to have better information and support from regulators. For instance, the home bias, the volatility of capital flows and herding among foreign investors are explained to be due to superior information of domestic investors as well as to regulators’ bias against foreign investors [@choe2005domestic]. Although the literature of early 2000s provides some opposite evidence of information asymmetry between domestic and foreign investors [@grinblatt2000investment; @seasholes2000smart], the most recent studies support the traditional view that foreign investors are at an information disadvantage compared to domestic investors [@hau2001location; @choe2005domestic; @dvovrak2005domestic]. 

Compared to large literature of describing information advantages of domestic and foreign investors, the relationship of foreign ownership and information asymmetry is less studied. @jiang2004foreign find evidence of inverse relation between foreign ownership and information asymmetry in Japanese markets by focusing on the relation between the level of foreign shareholdings and a measurable consequence of information asymmetry of which they use the timing and magnitude of intertemporal return-earnings associations. Furthermore, they provide evidence that foreign investors tend to avoid stocks with high cross-corporate holdings. However, @choi2013foreign report that high foreign ownership is associated with high information asymmetry using a bid-ask spread as a proxy for information asymmetry. In contrast, [FIX:] @he2013large use a well-known measure of the probability of informed trading (PIN) and price non-synchronicity as proxies for information asymmetry when examining the connection between foreign ownership and information asymmetry with a cross-sectional dataset of firms in 40 markets in 2002. They find, as well, that firms with large foreign ownership typically have more informative stock prices (i.e. low information asymmetry) but they rather strongly, given that they limit their conclusion only to a cross-sectional regression results, assume that large foreign ownership causes low information asymmetry. 

I contribute to the existing literature by examining the relationship of foreign ownership and information asymmetry not just with a panel regression but also with a difference-in-differences research setting of brokerage closures [@kelly2012testing] which cause an exogenous shock to the analyst coverage of a firm’s stock. @kelly2012testing and @derrien2013real argue that an exogenous decrease in analyst coverage causes an increase in information asymmetry of the covered firm. As a result, the research setting of brokerage closures enables me to assess the causal effect between information asymmetry and foreign ownership. Previous studies of information asymmetry and foreign ownership [@jiang2004foreign; @choi2013foreign; @he2013large] do not examine causality profoundly, which makes this thesis a first attempt, to the best of my knowledge, to study the causal effect of information asymmetry on foreign ownership. In addition, I test the general relationship of these two with panel regressions by using various proxies for information asymmetry such as PIN by various researchers [@brown2004conference; @brown2007disclosure; @duarte2009pin; @easley2010factoring], MIA [@johnson2017simple] and VCV [@lof2018asymmetric].


# 3 Hypotheses

In this thesis, I study the effect of information asymmetry on foreign ownership in US stock markets. In particular, I examine how the foreign ownership of US stocks are affected by an exogenous reduction in analyst coverage using a credible quasi-experiment of brokerage closures [@kelly2012testing]. Moreover, I test the general relationship of foreign ownership and information asymmetry with alternative proxy measures for information asymmetry in a panel regression setting. Based on these research settings, I construct the following hypotheses:

*H1: Stocks with higher information asymmetry are associated with low foreign ownership*

*H2: An exogenous increase in information asymmetry of stocks results in a decrease of foreign ownership*

*H3: The reduction of foreign ownership due to an exogenous information asymmetry shock is emphasized in stocks with low institutional ownership and analyst coverage*

The first hypothesis is mainly supported by the existing literature. (fix: @jiang2004foreign and @he2013large find an inverse connection between foreign ownership and information asymmetry using the timing and magnitude of intertemporal return-earnings associations in Japanese markets and the probability of informed trading in multiple countries as proxies for information asymmetry, respectively). In contrast, @choi2013foreign provide opposite results with a bid-ask spread in Chinese markets as a corresponding proxy.

Although the existing literature supports the hypothesis of the inverse relation between information asymmetry and foreign ownership, few studies address the causal relationship of these two variables directly as described in the second hypothesis. Based on their overall results, @jiang2004foreign argue that foreign investors are attracted to firms with low information asymmetry in Japanese markets. (FIX: @he2013large interpret similar results of the inverse relation to be due to a view that foreign investors contribute positively to the informativeness of stock prices). However, they point out that the potential reverse causality may drive their results but find it conceptually less likely. They argue that foreign investors could improve corporate governance and disclosure policies of firms of the invested firms. In the spirit of Granger causality test, they run a predictive regression with a one-year lag of dependent variable and find results to be consistent with foreign ownership Granger-causing price informativeness. @batten2015foreign find in Vietnamese markets that foreign investors prefer firms of which characteristics are associated with low information asymmetry, such as large size, low leverage and high book-to-market ratio to overcome the information disadvantage compared to domestic investors. Furthermore, their finding is in line with previous studies of home bias that find foreign investors preferring firms with comfortable characteristics like large size or low leverage [@kang1997there; @dahlquist2001direct].

The existing literature finds that institutional investors can act as active monitors of management by directly intervening in a firm’s operations [@shleifer1986large; @gillan2003corporate; @ferreira2008colors]. As a result of monitoring, information asymmetry of a stock is reduced. Accordingly, less uninformed investors like foreign investors consider institutional ownership as a convincing signal that information asymmetry risk of a given stock is mitigated [@luong2015]. Similarly, @lof2018asymmetric argue that an exogenous decrease of analyst coverage is a greater shock for a firm that initially has a low analyst coverage. Hence, the third hypothesis is largely supported by existing literature.


# 4 Data

## 4.1 Sample Selection


Since the country information of the institutions in the 13F data is only from June 1997, I limit the sample to include US listed firms (NYSE, AMEX and Nasdaq) during the period of 1997-2017. Data for foreign, domestic and institutional shareholdings is retrieved from Thomson Reuters institutional holdings (form 13F) database. To calculate the stock price related control variables, the information asymmetry proxies *BID_ASK_SPREAD*, *VCV* and foreign, domestic and institutional ownership measures, I gather stock price information from the Center for Research in Security Prices (CRSP). Accounting related control variables are collected from COMPUSTAT. The 13F data is merged with CRSP by matching the 8-digit CUSIP identifier from 13F to the 8-digit NCUSIP from CRSP. I use CRSP-COMPUSTAT Merged Database (CCM) to merge CRSP and COMPUSTAT datasets. Firm-year estimates of information asymmetry proxies *PIN~BHL~* [@brown2004conference], *PIN~BH~* [@brown2007disclosure], *PIN~EHO~* [@easley2010factoring], *PIN~DY~* [@duarte2009pin], *Adjusted PIN* and firm-day estimates of *MIA* [@johnson2017simple] are collected from the cited authors’ websites [^1]. Information asymmetry measures are merged with the baseline sample by using the CRSP’s Permanent Issue Number (PERMNO) as a linking identifier.

[^1]:Firm-year observations of PINBH, PINBHL, PINEHO and PINDY are made available
by Søren Hvidkjær (https://sites.google.com/site/hvidkjaer/data), Stephen Brown (http://scholar.rhsmith.umd.edu/sbrown/pin-data) and Jefferson Duarte (http://www.owlnet.rice.edu/~jd10/),
respectively. Daily firm-level observations of MIA are made available by Travis Johnson (http://travislakejohnson.com/data.html).


## 4.2 Constructing the variables

I extract foreign ownership data from Thomson Reuters institutional holdings (form 13F) s34 master file. I define two variables *FOREIGN_HOLDINGS* and *FOREIGN_BREADTH* of which the former is defined as an annual average of the shares of a firm held by foreign institution at the end of each quarter of the year divided by the firm’s total shares outstanding at the end of each quarter. The latter is defined as an annual average of the number of distinct foreign institutions holding shares in the firm at the end of each quarter of the year divided the total number of institutions in the 13F database at the end of each quarter [@chen2002breadth; @lof2018asymmetric]. I retrieve shares outstanding data from CRSP monthly file. I also construct the variables for total institutional ownership *INSTITUTIONAL_HOLDINGS* and *INSTITUTIONAL_BREADTH* in a similar manner. In comparison of the firm-year level data set in the baseline research setting, I construct the variables for the quasi-experimental research sample, I construct the variables similarly but at the firm-quarter level.  

I obtain data for information asymmetry measures of annual firm-level PIN and daily firm-level MIA observations from the cited researchers’ publicly available websites. I construct the firm-year observations of MIA by calculating the annual average of daily observations for each firm. Data for proxy measure VCV is retrieved from CRSP daily stock file. Following Lof and van Bommel (2018), I construct the annual firm-level observations of VCV by computing the fraction of the annual standard deviation of daily trading volumes and the annual average of daily trading volumes. I require firms to have at least 200 days with a positive trading volume in a year. Similarly, I calculate the *VCV* using three different measures of trading volume: volume in US dollars, volume market shares and turnover.

I gather control variables data from COMPUSTAT quarter fundamentals and CRSP monthly stock files. I compute *LOG_MARKET_CAP* by multiplying market price of each stock by the shares outstanding at the end of each quarter, converting it to an annual average and taking the logarithm of this measure. *BM_RATIO* is an annual average of the stock's book value of equity divided by the market value at the end of each quarter. *LEVERAGE* is an annual average of the stock's total debt divided by total assets at the end of each quarter. *ROA* is an annual average of the stock's net income divided by total assets at the end of each quarter. I use SIC codes from CRSP to capture the corresponding industry for each stock.

## 4.3 The quasi-natural experiment

For the quasi-natural experiment, I limit the time period of the original sample to 1997-2011 to cover the time period of 22 distinct brokerage closures from June 2000 until January 2008 listed in Appendix A of Kelly and Ljungqvist (2012) plus three years of pre- and post-treatment periods. I identify stocks that lose an analyst covering the firm because of the brokerage closures which provide a source of exogenous variation for the analyst coverage. The list is matched with an analyst coverage data retrieved from the Institutional Brokers’ Estimate System (IBES) detail file. 

To construct the sample of treated firms, I filter out firms that are not covered by analysts employed in the brokerage houses listed in Appendix A of @kelly2012testing. Following @derrien2013real, I require for the treated firms to be covered by an analyst at least one year before the disappearance dates to filter out firms that are not actively covered by the analysts. Furthermore, following @kelly2012testing and @derrien2013real, I only retain firms for which the analyst has not “stopped” his estimate before the corresponding broker disappearance date to eliminate the potential endogeneity problem. For instance, if an analyst terminates the coverage of firms unrelated to the brokerage closure before the disappearance date (e.g. anticipating changes in corporate policies), the decision is endogenous. I collect the data for stopped estimates from IBES stop file. Since the brokerage closure dates listed by @kelly2012testing and corresponding disappearance dates do not coincide completely, I follow @derrien2013real, @he2013dark and @lof2018asymmetric to construct a three-month gap before and after the event date. As a result, I estimate the dependent variables and explanatory variables for each stock in a given quarter by subtracting (adding) three months from the event date and finding the previous (next) available quarter value for before and after measures, respectively. Moreover, I define the variable *ANALYST_COVERAGE* as the number of distinct analysts covering a firm in a given quarter.





# 5 Methodology

To empirically examine the first hypothesis of the thesis, I use a panel regression model for the baseline sample. A difference-in-differences regression model is employed to test the second and third hypotheses. 

## 5.1 The panel regression model

I test the relation of foreign ownership and information asymmetry by using the following panel regression model of firm-year observations:

\begin{equation}\label{eq_baseline}
\begin{aligned}
FOREIGN\_OWNERSHIP_{i,t} &= \beta_0 + \beta_{1}INFORMATION\_ASYMMETRY_{i,t} + \beta_{3}BM\_RATIO_{i,t}\\ &+ \beta_{4}LEVERAGE_{i,t} + \beta_{5}ROA_{i,t}\\ &+ \sum_{t=1}^T YEAR_t + \sum_{n=1}^N INDUSTRY_n + \epsilon_{i,t}
\end{aligned}
\end{equation}

Foreign_ownership is measured by either of the two variables: Foreign_holdings (defined as shares of a firm held by foreign institution, as a percentage of the firm’s shares outstanding at the end of each year) and Foreign_breadth (defined as the number of distinct foreign institutions holding shares in the firm, as a percentage of the total number of institutions in the 13F database at the end of each year [@chen2002breadth; @lof2018asymmetric]). Information_asymmetry is, similarly, measured by one of the various proxy variables: PIN_BHL, PINBH, PINEHO, PINDY, Adjusted_PIN, MIA, C2, and VCV. Due to each combination of list variables Foreign_ownership and Information_asymmetry, I have results from 14 different regressions. LogMktCap is the logarithm of market capitalization at the end of each year. BM_ratio is the book value of equity divided by the market value at the end of each year. Leverage is the total debt divided by total assets at the end of each year. I also include year and industry fixed effects.

## 5.2 The difference-in-differences regression model

I examine the effect of an exogenous increase in information asymmetry on foreign ownership of a firm by using the following difference-in-differences regression of firm-quarter observations:

\begin{equation}
\label{eq_didh2}
\begin{aligned}
FOREIGN\_OWNERSHIP_{i,t} &= \beta_0 + \beta_{1}TREATED_{i} + \beta_{2}AFTER_{t} + \beta_{3}AFTER\times TREATED_{i,t}\\ &+ \beta_{5}BM\_RATIO_{i,t} + \beta_{6}LEVERAGE_{i,t} + \beta_{7}ROA_{i,t}\\ &+ \sum_{t=1}^T YEAR_t + \sum_{n=1}^N INDUSTRY_n + \epsilon_{i,t}
\end{aligned}
\end{equation}


Similarly, as in the panel regression model, Foreign_ownership is a list of variables Foreign_holdings and Foreign_breadth. Treated is a dummy variable indicating observations of firms that are in the treatment group. After is defined as a dummy variable for observations that occur after each brokerage closure event. The variable of interest is the interaction term of these two variables or the difference-in-differences estimator which captures the effect of treatment. Moreover, I include year and industry fixed effects.

# 6 Results

In this section, I report the empirical results of the effect of information asymmetry on foreign ownership. First in Section 6.1, I present the results of the general relation between foreign ownership and information asymmetry with the baseline panel regression setting (Hypothesis 1). Second in Section 6.2, I study the causal effect of the exogenous increase in information asymmetry on foreign ownership by difference-in-differences panel regression setting (Hypothesis 2). Then, I examine the second hypothesis more in-depth by a subset analysis of the different institutional investor types. Finally, in Section 6.3 I test the causal effect in cases of low analyst coverage and low institutional ownership (Hypothesis 3).

## 6.1 Baseline setting results

In this section, I report the results of the baseline setting. First, I examine the relation between the variables used in baseline setting by a correlation matrix. Table \ref{table_cor_matrix} reports the results of annual firm-level correlations between the variables used in baseline panel regression model (Equation \ref{eq_baseline}). Each value is a time-series average of within-year correlations (Pearson). The total sample time period extends from 1997 to 2017. However, this holds true for all variables except *PIN~DY~* (1997-2004), *PIN~DY_ADJ~* (1997-2004), *PSOS~DY~* (1997-2004),
*PIN~EHO~* (1997-2001), *PIN~BHL~* (1997-2010), *PIN~BH~* (1997-2010), MIA (1997-2015).

Variable *FOR_OWN* is negatively correlated with all information asymmetry measures, which is consistent with the first hypothesis. The negative relation is the strongest with the different probability of informed trading measures and the least strong with *MIA*. Moreover, the correlations of *FOR_OWN* with the control variables of different firm characteristics is intuitive and in line with the existing literature. Foreign investors tend to own firms with larger market capitalization, greater profitability and smaller book-to-market ratios (i.e. value stocks). However, foreign ownership has a positive relation with leverage, implying a preference of more in-debt firms. The relation between foreign ownership and total institutional ownership is positive, indicating that foreign investors have similar stockholdings with institutional investors in general. Accordingly, *FOR_BREADTH* has similar but stronger correlations with other variables as *FOR_OWN*. 

Information asymmetry measures are strongly positively correlated with each other, which is consistent and implies that they capture similar explanatory characteristics. Only *PSOS~DY~* has a negative correlation with another information asymmetry measure *MIA* and largely explained by the fact that it is a measure of illiquidity unrelated to asymmetric information [@duarte2009pin]. All control variables except *LOG_MKT_CAP* have relatively weak correlations with the information asymmetry measures, which enables me to use them as explanatory in a regression model with a low risk of multicollinearity. As a result, I choose to exclude *LOG_MKT_CAP* from subsequent regression models due to a potential risk of multicollinearity. 

\begingroup
\renewcommand\arraystretch{2.5}
\renewcommand\captionsetup{justification=raggedright,
                           width=\linewidth}
```{r, results='asis'}
library(tidyverse)
library(stargazer)
library(kableExtra)
library(huxtable)
cor_matrix <- read_rds("results/cor_matrix.rds")
kable(cor_matrix, "latex", linesep = "", caption.short = "Correlations between sample variables", caption = "\\textbf{Correlations between sample variables}\\newline\\scriptsize This table reports the correlations between different institutional ownership, information asymmetry and accounting related control variables of the baseline sample. Each correlation estimate is the annual average of the within-year of (Pearson) correlations. \\textit{FOR\\_OWN} and \\textit{INST\\_OWN} are the annual averages of the firm's shares held by (foreign) institutions at the end of each quarter of the year divided by the firm's total shares outstanding at the end of each quarter. \\textit{FOR\\_BREADTH} and \\textit{INST\\_BREADTH} are the annual averages of the number of the firm's distinct (foreign) institutional shareholders at the end of each quarter divided by the total number of distinct institutional shareholders in 13F database at the end of each quarter (Chen et al., 2002; Lof and Bommel, 2018). The annual firm-levels of information asymmetry are mainly estimated by various researchers. \\textit{BA\\_SPREAD} is the annual average of the daily firm-level observations of bid-ask spreads (i.e. the difference of ask and bid price divided by the closing price). \\textit{PIN\\textsubscript{BHL}} is estimated by Brown et al (2004). \\textit{PIN\\textsubscript{BH}} is estimated by Brown and Hillegeist (2007). \\textit{PIN\\textsubscript{EHO}} is estimated by Easley et al. (2010). \\textit{PIN\\textsubscript{DY}}, \\textit{PIN\\textsubscript{DY\\_ADJ}} and the illiquidity measure \\textit{PSOS\\textsubscript{DY}} are estimated by Duarte and Young (2009). \\textit{MIA} is the annual average of the firm-day observations estimated by Johnson and So (2017). \\textit{VCV\\textsubscript{USD}}, \\textit{VCV\\textsubscript{MKT}} and \\textit{VCV\\textsubscript{TO}} are the fractions of the annual standard deviation of daily firm-level trading volumes and the annual average of daily firm-level trading volumes Lof and Bommel (2018). Trading volumes for \\textit{VCV\\textsubscript{USD}}, \\textit{VCV\\textsubscript{MKT}} and \\textit{VCV\\textsubscript{TO}} are calculated in US dollars, as a fraction of total market volume on the same day and as a daily turnover, respectively. The accounting related variables are \\textit{LOG\\_MKT\\_CAP} (the annual average of the firm-quarter observations of logarithm of market capitalization) \\textit{BM\\_RATIO} (the annual average of the firm-quarter observations of book equity divided by market capitalization), \\textit{LEVERAGE} (the annual average of the firm-quarter observations of debt divided by total assets) and \\textit{ROA} (the annual average of the firm-quarter observations of net income divided by total assets. All institutional ownership and breadth variables and control variables are winsorized at the top and bottom 1\\%. Sample: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors' websites. \\label{table_cor_matrix}",
      booktabs = T, align = "c") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), position = "left") %>%
  landscape()
```
\endgroup


I extend the analysis of the correlation matrix by examining the effect of information asymmetry on foreign ownership in a panel regression setting The dependent variable in every regression model FOR_OWN is the annual average of the foreign ownership for each stock. Different information asymmetry measures are used separately as explanatory variables. The control variables are different measures of firm characteristics. I also include industry and year fixed effects. Table \ref{table_h1_base} reports the results.

Similar to the findings of correlations in Table \ref{table_cor_matrix}, the empirical results of the panel regression models in Table \ref{table_h1_base} support Hypothesis 1 and the findings by @jiang2004foreign, @baik2013liability and @batten2015foreign of the negative relation between foreign ownership and asymmetric information. In Panel A, The regression coefficients of information asymmetry measures are negative in all models and statistically significant at the 1% level in all regression models except with bid-ask spread as the information asymmetry measure. Based on column (3), a 1 percentage point increase in information asymmetry (PIN~DY_ADJ~) leads to a decrease of about 0.10% in foreign ownership *ceteris paribus*. Based on all models, a 1 percentage point increase in information asymmetry results, on average, in a decrease of about 0.05% in foreign ownership *ceteris paribus*. Overall, the negative relation is stronger with the probability of informed trading measures than with bid-ask spread, multimarket information asymmetry or volume coefficient of variation. Based on the results of adjusted R^2^, models with different probability of informed trading measures and MIA have the best explanatory power.

```{r, results='asis', message = FALSE, warning=FALSE, eval = FALSE}
## baseline regression table h1 panel a: FOR_OWN and panel b:FOR_BREADTH
## code chunk produces tex file which is used in output
library(tidyverse)
library(stargazer)
library(lfe)
library(kableExtra)
library(starpolishr)
baseline_regression_raw <- read_rds("results/baseline_regression_raw.rds")

baseline_regression <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_OWN) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

baseline_regression2 <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_BREADTH) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

rnm <- function(df, ia_meas, dep_meas) {
  rnm_list <- set_names(c("ia_measure", "dep_measure"), syms(c(ia_meas, dep_meas)))
  rename(df, !!!rnm_list)
}

model_function <- function(df, ia_meas, dep_meas) {
  f <- dep_measure ~ ia_measure + BM_RATIO + LEVERAGE +
    ROA |year + sic_code|0|year + sic_code
  f[[2]] <- sym(dep_meas)
  f[[3]][[2]][[2]][[2]][[2]][[2]][[2]] <- sym(ia_meas)
  felm(f, data = df)
}

baseline_names <- mutate(baseline_regression,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))

baseline_names2 <- mutate(baseline_regression2,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))


 star1 <-  stargazer(baseline_names$model,
           header = F,
           column.labels =c("FOR\\_OWN"),
           label = "table_h1_base",
           dep.var.labels.include = F,
           notes.label = "",
           notes.append = F,
           notes = "",
           column.separate = c(11),
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign ownership", type = "latex")

 star2 <- stargazer(baseline_names2$model,
           header = F,
           #label = "table_h1_for_breadth",
           notes.label = "",
           notes.append = F,
           notes = "",
           column.labels =c("FOR_BREADTH"),
           dep.var.labels.include = F,
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign breadth", type = "latex")

a <- star_panel(star1, star2,
                        panel.names = c("Foreign ownership", "Foreign breadth"), same.summary.stats = F)

starpolishr::star_tex_write(a, file = "my_tex_file2.tex", headers = TRUE)

```


\begingroup
\renewcommand\arraystretch{0.55}
\begin{landscape}
\captionsetup{width=1.02\linewidth}
\scriptsize
\begin{longtable}{@{\extracolsep{5pt}}lccccccccccc}
  \caption[Panel regression analysis of foreign ownership and foreign breadth]{\textbf{Panel regression analysis of foreign ownership and foreign breadth}\newline\scriptsize This table reports the results of the annual firm-level panel regression models. In Panel A, the dependent variable (\textit{FOR\_OWN}) is the annual average of the firm's shares held by foreign institutions at the end of each quarter divided by the firm's total shares outstanding at the end of each quarter. In Panel B, the dependent variable (\textit{FOR\_BREADTH}) is the annual average of the number of the firm's distinct foreign institutional shareholders at the end of each quarter divided by the total number of distinct institutional shareholders in 13F database at the end of each quarter (Chen et al., 2002; Lof and Bommel, 2018). The explanatory variables of interest are the various annual firm-level estimates of information asymmetry. \textit{BA\_SPREAD} is the annual average of the daily firm-level observations of bid-ask spreads (i.e. the difference of ask and bid price divided by the closing price). \textit{PIN\textsubscript{BHL}} is estimated by Brown et al (2004). \textit{PIN\textsubscript{BH}} is estimated by Brown and Hillegeist (2007). \textit{PIN\textsubscript{EHO}} is estimated by Easley et al. (2010). \textit{PIN\textsubscript{DY}}, \textit{PIN\textsubscript{DY\_ADJ}} and the illiquidity measure \textit{PSOS\textsubscript{DY}} are estimated by Duarte and Young (2009). \textit{MIA} is the annual average of the firm-day observations estimated by Johnson and So (2017). \textit{VCV\textsubscript{USD}}, \textit{VCV\textsubscript{MKT}} and \textit{VCV\textsubscript{TO}} are the fractions of the annual standard deviation of daily firm-level trading volumes and the annual average of daily firm-level trading volumes Lof and Bommel (2018). Trading volumes for \textit{VCV\textsubscript{USD}}, \textit{VCV\textsubscript{MKT}} and \textit{VCV\textsubscript{TO}} are calculated in US dollars, as a fraction of total market volume on the same day and as a daily turnover, respectively. The control variables are \textit{BM\_RATIO} (the annual average of the firm-quarter observations of book equity divided by market capitalization), \textit{LEVERAGE} (the annual average of the firm-quarter observations of debt divided by total assets) and \textit{ROA} (the annual average of the firm-quarter observations of net income divided by total assets. I include industry and year fixed effects in all regressions. Standard errors are clustered by the industry and year level and reported in parantheses. All institutional ownership, breadth and control variables are winsorized at the top and bottom 1\%. *, ** and *** denote the statistical significance at the 10\%, 5\% and 1\% level, respectively. Sample: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors' websites.}
   \label{table_h1_base} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
  & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_OWN} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.8ex] 
\\[-2.0ex] \multicolumn{12}{@{} l}{Panel A: Foreign ownership}
 \\
 \\[-1.5ex]
 BA\_SPREAD & $-$0.004 &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.004) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY &  & $-$0.072$^{***}$ &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.014) &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY\_ADJ &  &  & $-$0.095$^{***}$ &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.017) &  &  &  &  &  &  &  &  \\ 
  PSOS\_DY &  &  &  & $-$0.041$^{***}$ &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.010) &  &  &  &  &  &  &  \\ 
  PIN\_EHO &  &  &  &  & $-$0.086$^{***}$ &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.015) &  &  &  &  &  &  \\ 
  PIN\_BHL &  &  &  &  &  & $-$0.079$^{***}$ &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.016) &  &  &  &  &  \\ 
  PIN\_BH &  &  &  &  &  &  & $-$0.083$^{***}$ &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.014) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.038$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.007) &  &  &  \\ 
  VCV\_USD &  &  &  &  &  &  &  &  & $-$0.009$^{***}$ &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.001) &  &  \\ 
  VCV\_MKT &  &  &  &  &  &  &  &  &  & $-$0.009$^{***}$ &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.001) &  \\ 
  VCV\_TO &  &  &  &  &  &  &  &  &  &  & $-$0.010$^{***}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.001) \\ 
  BM\_RATIO & $-$0.008$^{***}$ & $-$0.003$^{***}$ & $-$0.003$^{***}$ & $-$0.005$^{***}$ & $-$0.003$^{***}$ & $-$0.005$^{***}$ & $-$0.003$^{***}$ & 0.00002 & $-$0.006$^{***}$ & $-$0.006$^{***}$ & $-$0.006$^{***}$ \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  LEVERAGE & 0.004$^{*}$ & 0.007$^{***}$ & 0.007$^{***}$ & 0.008$^{***}$ & 0.003$^{***}$ & 0.003 & 0.004$^{**}$ & 0.010$^{***}$ & 0.004 & 0.004 & 0.004 \\ 
  & (0.003) & (0.002) & (0.002) & (0.002) & (0.001) & (0.002) & (0.002) & (0.003) & (0.003) & (0.003) & (0.003) \\ 
  ROA & 0.095$^{***}$ & 0.078$^{***}$ & 0.080$^{***}$ & 0.078$^{***}$ & 0.060$^{***}$ & 0.068$^{***}$ & 0.069$^{***}$ & 0.088$^{***}$ & 0.074$^{***}$ & 0.075$^{***}$ & 0.079$^{***}$ \\ 
  & (0.012) & (0.009) & (0.010) & (0.009) & (0.009) & (0.007) & (0.008) & (0.011) & (0.008) & (0.008) & (0.008) \\ 
\cline{2-12} \\[-2.0ex]
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 110,998 & 15,532 & 15,532 & 15,532 & 9,965 & 79,095 & 79,208 & 21,017 & 95,241 & 95,241 & 95,241 \\ 
Adjusted R$^{2}$ & 0.210 & 0.406 & 0.399 & 0.367 & 0.398 & 0.282 & 0.298 & 0.317 & 0.246 & 0.246 & 0.246 \\ 
\\[-1.83ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_BREADTH} \\ 
\\[-1.83ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.83ex]
\\[-2.0ex] \multicolumn{12}{@{} l}{Panel B: Foreign breadth}
 \\
 \\[-1.5ex]
BA\_SPREAD & $-$0.001 &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.001) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY &  & $-$0.014$^{***}$ &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.003) &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY\_ADJ &  &  & $-$0.021$^{***}$ &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.003) &  &  &  &  &  &  &  &  \\ 
  PSOS\_DY &  &  &  & $-$0.006$^{***}$ &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.002) &  &  &  &  &  &  &  \\ 
  PIN\_EHO &  &  &  &  & $-$0.018$^{***}$ &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.002) &  &  &  &  &  &  \\ 
  PIN\_BHL &  &  &  &  &  & $-$0.013$^{***}$ &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.002) &  &  &  &  &  \\ 
  PIN\_BH &  &  &  &  &  &  & $-$0.013$^{***}$ &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.002) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.028$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.002) &  &  &  \\ 
  VCV\_USD &  &  &  &  &  &  &  &  & $-$0.002$^{***}$ &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.0002) &  &  \\ 
  VCV\_MKT &  &  &  &  &  &  &  &  &  & $-$0.002$^{***}$ &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.0002) &  \\ 
  VCV\_TO &  &  &  &  &  &  &  &  &  &  & $-$0.002$^{***}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.0002) \\ 
  BM\_RATIO & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.0003$^{***}$ & $-$0.0005$^{**}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ & $-$0.001$^{***}$ \\ 
  & (0.0001) & (0.0002) & (0.0002) & (0.0002) & (0.0001) & (0.0001) & (0.0001) & (0.0002) & (0.0001) & (0.0001) & (0.0001) \\ 
  LEVERAGE & 0.002$^{***}$ & 0.003$^{***}$ & 0.002$^{***}$ & 0.003$^{***}$ & 0.002$^{***}$ & 0.001$^{***}$ & 0.002$^{***}$ & 0.005$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ \\ 
  & (0.0004) & (0.001) & (0.001) & (0.001) & (0.0003) & (0.0002) & (0.0003) & (0.001) & (0.0004) & (0.0004) & (0.0004) \\ 
  ROA & 0.013$^{***}$ & 0.013$^{***}$ & 0.013$^{***}$ & 0.013$^{***}$ & 0.008$^{***}$ & 0.006$^{***}$ & 0.007$^{***}$ & 0.021$^{***}$ & 0.010$^{***}$ & 0.009$^{***}$ & 0.010$^{***}$ \\ 
  & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.001) & (0.001) & (0.003) & (0.002) & (0.002) & (0.002) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 110,998 & 15,532 & 15,532 & 15,532 & 9,965 & 79,095 & 79,208 & 21,017 & 95,241 & 95,241 & 95,241 \\ 
Adjusted R$^{2}$ & 0.265 & 0.382 & 0.400 & 0.323 & 0.386 & 0.371 & 0.366 & 0.493 & 0.320 & 0.321 & 0.321 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{12}{r}{} \\ 
\end{longtable}  
\end{landscape}
\endgroup

The control variables in Panel A are mainly statistically significant and in line with the existing literature. Book-to-market ratio (*BM_RATIO*) is negative and statistically significant at the 1% level in all regression models except in the model with MIA as the explanatory variable. This implies that foreign investors are driven way of the stocks with relatively high book-to-market ratio (i.e. value stocks). Book-to-market ratio is used as a measure of risk in many asset pricing models [e.g., @fama1993common; @carhart1997persistence; @pastor2003liquidity], which, in addition to my results, support the findings of @ko2007characteristics and @lin2003foreign that foreign investors avoid riskier firms with high book-to-market ratios. Moreover, the regression coefficients of ROA are positive and statistically significant at the 1% level in all models, implying that foreign investors prefer firms with positive probability. Based on column (1), an increase of 100 basis point in return on assets results in an increase of about 0.09 percentage points in foreign ownership *ceteris paribus*. The regression coefficients of leverage are mainly positive. LEVERAGE is positive and statistically significant in six out of eleven models, positive and statistically insignificant in four out of eleven models and negative and statistically significant once. Hence, an increase in leverage is mostly associated with an increase in foreign ownership. The results mostly contradicts the findings of foreign investors' preference on low debt ratio firms by @kang1997there and @dahlquist2001direct.

Panel B reports the results of regressing foreign breadth on information asymmetry measures. The results follow similar pattern with foreign ownership results in Panel A. The regression coefficients of coefficients of information asymmetry are negative in all models and statistically significant at the 1% level in all models except with bid-ask spread as the information asymmetry measure. Based on column (8), a 100 basis point increase in information asymmetry (*MIA*) is associated with ca. 0.03 percentage points decrease in foreign breadth *ceteris paribus*. In general, a 1 percentage point increase in information asymmetry results in 0.001-0.03 percentage points decrease of foreign ownership. Based on adjusted R^2^, the explanatory power is, in general, better than with models in Panel A. Notably, the model with *MIA* clearly explains variation better than other models, which differs from the results in Panel A. 

In addition to information asymmetry measures, the control variables in Panel B follow similar pattern with Panel A. Book-to-market ratio is negative and statistically significant at the 1% level in all models, leverage is mainly positive and statistically significant and return on assets is positive and statistically significant at the 1% level in all models. Similar to Panel A, the results support the findings of @ko2007characteristics and @lin2003foreign that foreign investors seek stocks with comfortable characteristics except the results of leverage. In general, the results of Table \ref{table_h1_base} support strongly the first hypothesis of inverse relation between foreign ownership and information asymmetry.

In addition to inspecting general market-level foreign ownership and breadth measures, I extend the analysis by comparing foreign ownership against institutional ownership for a given stock in a given time. In particular, I define a variable *FOR_TO_INST_OWN* which is a measure of the annual average of the firm's shares held by foreign institutions at the end of each quarter divided by the firm's shares held by total institutions at the end of each quarter. This enables me to examine whether foreign institutional shareholders have stronger or weaker dislike of information intensive stocks than institutional shareholders in general. Similarly, I define a variable *FOR_TO_INST_BREADTH* which is a measure of the annual average of the number of the firm's distinct foreign institutional shareholders at the end of each quarter divided by the number of the firm's of distinct institutional shareholders at the end of each quarter. I test the dependent variables with the same panel regression models as in Table \ref{table_h1_base}. Table \ref{table_h1_for_to_inst} reports the results.


``` {r, results='asis', message = FALSE, warning=FALSE, eval = FALSE}
library(tidyverse)
library(stargazer)
library(lfe)
library(kableExtra)
library(starpolishr)

baseline_regression_raw <- read_rds("results/baseline_regression_raw.rds")

baseline_regression <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_TO_INST_OWN) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

baseline_regression2 <- baseline_regression_raw %>%
  gather(ia_measure_name, ia_measure, BA_SPREAD:VCV_TO) %>%
  gather(dep_measure_name, dep_measure, FOR_TO_INST_BREADTH) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(dep_measure_name, ia_measure_name) %>%
  nest()

rnm <- function(df, ia_meas, dep_meas) {
  rnm_list <- set_names(c("ia_measure", "dep_measure"), syms(c(ia_meas, dep_meas)))
  rename(df, !!!rnm_list)
}

model_function <- function(df, ia_meas, dep_meas) {
  f <- dep_measure ~ ia_measure + BM_RATIO + LEVERAGE +
    ROA |year + sic_code|0|year + sic_code
  f[[2]] <- sym(dep_meas)
  f[[3]][[2]][[2]][[2]][[2]][[2]][[2]] <- sym(ia_meas)
  felm(f, data = df)
}

baseline_names <- mutate(baseline_regression,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))

baseline_names2 <- mutate(baseline_regression2,
                         data_named = pmap(list(data, ia_measure_name, dep_measure_name), rnm),
                         model = pmap(list(data_named, ia_measure_name, dep_measure_name), model_function))

star1 <-  stargazer(baseline_names$model,
           header = F,
           column.labels =c("FOR\\_TO\\_INST\\_OWN"),
           label = "table_h1_for_to_inst",
           dep.var.labels.include = F,
           notes.label = "",
           notes.append = F,
           notes = "",
           column.separate = c(11),
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign-to-institution ownership and breadth ratios", type = "latex")

 star2 <- stargazer(baseline_names2$model,
           header = F,
           column.labels =c("FOR\\_TO\\_INST\\_BREADTH"),
           notes.label = "",
           notes.append = F,
           notes = "",
           dep.var.labels.include = F,
           omit.stat = c("ser", "rsq"),
           font.size = "tiny",
           no.space = T,
           add.lines = list(c("Industry fixed effects", rep("Yes", times = 11)),
                            c("Year fixed effects", rep("Yes", times = 11))),
           title = "Panel regression analysis of foreign-to-institution breadth ratio ", type = "latex")

a <- star_panel(star1, star2,
                        panel.names = c("Foreign-to-institution ownership ratio", "Foreign-to-institution breadth ratio"), same.summary.stats = F)


starpolishr::star_tex_write(a, file = "my_tex_file3.tex", headers = TRUE)

```

\begingroup
\renewcommand\arraystretch{0.54}
\begin{landscape}
\captionsetup{width=1.02\linewidth}
\scriptsize
\begin{longtable}{@{\extracolsep{5pt}}lccccccccccc}
  \caption[Panel regression analysis of foreign-to-institution ownership and breadth ratios]{\textbf{Panel regression analysis of foreign-to-institution ownership and breadth ratios}\newline\scriptsize This table reports the results of the annual firm-level panel regression models. In Panel A, the dependent variable (\textit{FOR\_TO\_INST\_OWN}) is the annual average of the firm's shares held by foreign institutions at the end of each quarter divided by the firm's shares held by institutions in total at the end of each quarter. In Panel B, the dependent variable (\textit{FOR\_TO\_INST\_BREADTH}) is the annual average of the distinct number of the firm's foreign institutional investors at the end of each quarter divided by the distinct number of the firm's institutional investors in total at the end of each quarter. The explanatory variables of interest are the various annual firm-level estimates of information asymmetry. \textit{BA\_SPREAD} is the annual average of the daily firm-level observations of bid-ask spreads (i.e. the difference of ask and bid price divided by the closing price). \textit{PIN\textsubscript{BHL}} is estimated by Brown et al (2004). \textit{PIN\textsubscript{BH}} is estimated by Brown and Hillegeist (2007). \textit{PIN\textsubscript{EHO}} is estimated by Easley et al. (2010). \textit{PIN\textsubscript{DY}}, \textit{PIN\textsubscript{DY\_ADJ}} and the illiquidity measure \textit{PSOS\textsubscript{DY}} are estimated by Duarte and Young (2009). \textit{MIA} is the annual average of the firm-day observations estimated by Johnson and So (2017). \textit{VCV\textsubscript{USD}}, \textit{VCV\textsubscript{MKT}} and \textit{VCV\textsubscript{TO}} are the fractions of the annual standard deviation of daily firm-level trading volumes and the annual average of daily firm-level trading volumes Lof and Bommel (2018). Trading volumes for \textit{VCV\textsubscript{USD}}, \textit{VCV\textsubscript{MKT}} and \textit{VCV\textsubscript{TO}} are calculated in US dollars, as a fraction of total market volume on the same day and as a daily turnover, respectively. The control variables are \textit{BM\_RATIO} (the annual average of the firm-quarter observations of book equity divided by market capitalization), \textit{LEVERAGE} (the annual average of the firm-quarter observations of debt divided by total assets) and \textit{ROA} (the annual average of the firm-quarter observations of net income divided by total assets. I include industry and year fixed effects in all regressions. Standard errors are clustered by the industry and year level and reported in parantheses. All institutional ownership, breadth and control variables are winsorized at the top and bottom 1\%. *, ** and *** denote the statistical significance at the 10\%, 5\% and 1\% level, respectively. Sample: 1997-2017. Sources: CRSP, COMPUSTAT, 13F and the cited authors' websites.}
  \label{table_h1_for_to_inst} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_TO\_INST\_OWN} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.8ex] 
\\[-2.0ex] \multicolumn{12}{@{} l}{Panel A: Foreign-to-institution ownership ratio}
 \\
 \\[-1.5ex]
 BA\_SPREAD & $-$0.002 &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.002) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY &  & $-$0.011 &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.040) &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY\_ADJ &  &  & $-$0.026 &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.048) &  &  &  &  &  &  &  &  \\ 
  PSOS\_DY &  &  &  & $-$0.001 &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.021) &  &  &  &  &  &  &  \\ 
  PIN\_EHO &  &  &  &  & 0.054 &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.066) &  &  &  &  &  &  \\ 
  PIN\_BHL &  &  &  &  &  & $-$0.030 &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.019) &  &  &  &  &  \\ 
  PIN\_BH &  &  &  &  &  &  & $-$0.032 &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.028) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.056$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.012) &  &  &  \\ 
  VCV\_USD &  &  &  &  &  &  &  &  & $-$0.007$^{***}$ &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.002) &  &  \\ 
  VCV\_MKT &  &  &  &  &  &  &  &  &  & $-$0.007$^{***}$ &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.002) &  \\ 
  VCV\_TO &  &  &  &  &  &  &  &  &  &  & $-$0.009$^{***}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.002) \\ 
  BM\_RATIO & $-$0.011$^{***}$ & $-$0.006$^{***}$ & $-$0.006$^{***}$ & $-$0.007$^{**}$ & $-$0.009$^{***}$ & $-$0.011$^{***}$ & $-$0.010$^{***}$ & 0.004 & $-$0.010$^{***}$ & $-$0.010$^{***}$ & $-$0.010$^{***}$ \\ 
  & (0.002) & (0.002) & (0.002) & (0.003) & (0.002) & (0.002) & (0.002) & (0.003) & (0.002) & (0.002) & (0.002) \\ 
  LEVERAGE & $-$0.002 & 0.0004 & 0.00003 & 0.001 & $-$0.002 & $-$0.005 & $-$0.004 & 0.006 & $-$0.004 & $-$0.004 & $-$0.004 \\ 
  & (0.005) & (0.004) & (0.004) & (0.004) & (0.006) & (0.005) & (0.005) & (0.007) & (0.005) & (0.005) & (0.005) \\ 
  ROA & 0.006 & $-$0.030 & $-$0.031 & $-$0.028 & $-$0.043 & $-$0.044$^{***}$ & $-$0.046$^{***}$ & $-$0.029 & $-$0.024 & $-$0.023 & $-$0.024 \\ 
  & (0.025) & (0.037) & (0.038) & (0.038) & (0.050) & (0.015) & (0.015) & (0.033) & (0.023) & (0.023) & (0.024) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 110,998 & 15,532 & 15,532 & 15,532 & 9,965 & 79,095 & 79,208 & 21,017 & 95,241 & 95,241 & 95,241 \\ 
Adjusted R$^{2}$ & 0.095 & 0.088 & 0.088 & 0.087 & 0.100 & 0.098 & 0.096 & 0.219 & 0.109 & 0.109 & 0.110 \\
\\[-1.83ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable:}} \\ 
\cline{2-12} 
 & \multicolumn{11}{c}{FOR\_TO\_INST\_BREADTH} \\ 
\\[-1.83ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.83ex]
\\[-2.0ex] \multicolumn{12}{@{} l}{Panel B: Foreign-to-institution breadth ratio}
 \\
 \\[-1.5ex]
BA\_SPREAD & $-$0.002 &  &  &  &  &  &  &  &  &  &  \\ 
  & (0.002) &  &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY &  & 0.081$^{**}$ &  &  &  &  &  &  &  &  &  \\ 
  &  & (0.033) &  &  &  &  &  &  &  &  &  \\ 
  PIN\_DY\_ADJ &  &  & 0.092$^{**}$ &  &  &  &  &  &  &  &  \\ 
  &  &  & (0.038) &  &  &  &  &  &  &  &  \\ 
  PSOS\_DY &  &  &  & 0.047$^{**}$ &  &  &  &  &  &  &  \\ 
  &  &  &  & (0.019) &  &  &  &  &  &  &  \\ 
  PIN\_EHO &  &  &  &  & 0.167$^{***}$ &  &  &  &  &  &  \\ 
  &  &  &  &  & (0.054) &  &  &  &  &  &  \\ 
  PIN\_BHL &  &  &  &  &  & 0.013 &  &  &  &  &  \\ 
  &  &  &  &  &  & (0.019) &  &  &  &  &  \\ 
  PIN\_BH &  &  &  &  &  &  & 0.038 &  &  &  &  \\ 
  &  &  &  &  &  &  & (0.030) &  &  &  &  \\ 
  MIA &  &  &  &  &  &  &  & $-$0.025$^{***}$ &  &  &  \\ 
  &  &  &  &  &  &  &  & (0.009) &  &  &  \\ 
  VCV\_USD &  &  &  &  &  &  &  &  & $-$0.005$^{*}$ &  &  \\ 
  &  &  &  &  &  &  &  &  & (0.003) &  &  \\ 
  VCV\_MKT &  &  &  &  &  &  &  &  &  & $-$0.005$^{*}$ &  \\ 
  &  &  &  &  &  &  &  &  &  & (0.003) &  \\ 
  VCV\_TO &  &  &  &  &  &  &  &  &  &  & $-$0.006$^{*}$ \\ 
  &  &  &  &  &  &  &  &  &  &  & (0.003) \\ 
  BM\_RATIO & $-$0.005$^{*}$ & 0.002 & 0.002 & 0.004 & $-$0.002 & $-$0.001 & $-$0.003$^{*}$ & 0.004$^{**}$ & $-$0.005$^{***}$ & $-$0.005$^{***}$ & $-$0.004$^{***}$ \\ 
  & (0.003) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) \\ 
  LEVERAGE & 0.004 & 0.002 & 0.002 & 0.001 & $-$0.003 & $-$0.001 & $-$0.001 & 0.014$^{***}$ & 0.003 & 0.003 & 0.003 \\ 
  & (0.004) & (0.003) & (0.004) & (0.004) & (0.004) & (0.003) & (0.003) & (0.005) & (0.004) & (0.004) & (0.004) \\ 
  ROA & 0.003 & $-$0.054$^{*}$ & $-$0.058$^{*}$ & $-$0.054$^{*}$ & $-$0.055 & $-$0.050$^{***}$ & $-$0.045$^{***}$ & 0.0002 & $-$0.019 & $-$0.018 & $-$0.017 \\ 
  & (0.026) & (0.029) & (0.030) & (0.030) & (0.041) & (0.015) & (0.014) & (0.022) & (0.019) & (0.019) & (0.020) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 110,998 & 15,532 & 15,532 & 15,532 & 9,965 & 79,095 & 79,208 & 21,017 & 95,241 & 95,241 & 95,241 \\ 
Adjusted R$^{2}$ & 0.117 & 0.118 & 0.111 & 0.111 & 0.168 & 0.097 & 0.098 & 0.448 & 0.150 & 0.150 & 0.151 \\
\hline 
\hline \\[-1.8ex] 
\multicolumn{12}{r}{} \\ 
\end{longtable}  
\end{landscape}
\endgroup

In Panel A, the regression coefficients of asymmetric information variables are all negative except the model with *PIN~EHO~* as the explanatory variable. The results are statistically significant at the 1% level in models with *MIA* and all *VCV* variables as explanatory variables. The results give more supporting evidence of the negative relation between foreign ownership and information asymmetry. Based on the results, foreign investors are more prone to avoid information intensive stocks compared to institutional investors on average. Based on column (8), a 1 percentage point increase in information asymmetry is associated with 0.05 percentage point decrease in ownership of foreign institutions against total institutions. The models with statistically significant results (*MIA* and *VCV*) have the best explanatory power according to the results of adjusted R^2^.

The results of the control variable coefficients are mixed. Book-to-market ratio (*BM_RATIO*) is negative and statistically significant at the 1% level in all regression models except with *MIA* as the explanatory variable. The results are mainly in line with the previous results and existing literature, implying that foreign institutional investors prefer more non-value stocks compared to institutional investors on average. The coefficients of *LEVERAGE* are mainly statistically insignificant, positive in five out eleven models and negative in six out of eleven models. Hence, the results of *LEVERAGE* provide nothing conclusive. The results of *ROA* are to some extent surprising. The coefficients are negative in all models except in *BA_SPREAD* as the explanatory variable and statistically significant at the 1% level in two models. The results imply that foreign institutional investors are more prone to hold less profitable stocks compared to institutional investors on average.

In Panel B, the regression coefficients of asymmetric information variables provide mixed results. The coefficients are negative and statistically significant with models of *PIN~DY~*, *PIN~DY_ADJ~*, *PSOS~DY~* and *PIN~EHO~* and positive and statistically significant with models of *MIA*, *VCV~USD~*,  *VCV~MKT~* and *VCV~TO~*. Hence, it is difficult to derive solid conclusions of the results. However, according to adjusted R^2^, the models with *MIA* and different *VCV* measures as explanatory variables have better explanatory power. In particular, the model with *MIA* has adjusted R^2^ of 0.448 which is clearly better than any other model. Moreover, the sample size in models with *MIA* and *VCV* is notably larger than with *PIN~DY~*, *PIN~DY_ADJ~*, *PSOS~DY~* and *PIN~EHO~*. 

Control variables in Panel B provide mixed results. *BM_RATIO* is negative in seven out of eleven models and statistically significant in five out of eleven models. It is positive and statistically significant in two out of eleven models. Hence, the results primarily suggests that foreign institutional investors are relatively more driven away of the value stocks than institutional investors in general. *LEVERAGE* is positive and statistically significant in five out of eleven models, implying foreign institutional investors' relatively larger tendency towards more levered stocks than institutional investors in general. This is counterintuitive in the light of the results by @kang1997there and @dahlquist2001direct that foreign investors prefer low debt ratio firms. The regression coefficients of *ROA* follow a similar negative and statistically significant pattern than in Panel B. This finding suggests that foreign institutional investors hold relatively less profitable stocks than institutional investors in general.

## 6.2 The results of the quasi-natural experiment

In this section, I report the general results of the quasi-natural experiment. First, I examine the evolution of the dependent variables foreign ownership (*FOR_OWN*) and foreign breadth (*FOR_BREADTH*) between the treatment and control groups in the twelve quarters (i.e. three years) before and after the brokerage closures that act as exogenous shock events of information asymmetry. The treated firms are firms that lose an analyst due to these brokerage closures. The control firms are selected using propensity score matching that matches each treatment firm to three control firms (nearest neighbor) on multiple covariates (twelve quarter before the event): logarithm of market capitalization, book-to-market ratio and analyst coverage. Figure \ref{fig_parallel_trend1} presents the results.

``` {r parallel_trend1, message = FALSE, warning=FALSE, eval=FALSE}

library(tidyverse)

parallel_trend1 <- read_rds("results/did_regression_matched_raw.rds") %>% 
  mutate(TREATED = if_else(TREATED == 1, "Treated", "Control")) %>% 
  group_by(TREATED, quarter_index) %>% 
  summarise(FOR_OWN = mean(FOR_OWN),
            FOR_BREADTH = mean(FOR_BREADTH)) %>% 
  ungroup()

ggplot(parallel_trend1, aes(quarter_index, FOR_OWN, color = TREATED)) +
  ggtitle("Panel A: Foreign ownership") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend1a.pdf", 
       width = 8, height = 4, units = "in")

ggplot(parallel_trend1, aes(quarter_index, FOR_BREADTH, color = TREATED)) +
  ggtitle("Panel B: Foreign breadth") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend1b.pdf", 
       width = 8, height = 4, units = "in")
  
```

\begin{figure}[!htb]
\centering
\includegraphics[width = \linewidth]{figures/parallel_trend1a.pdf}
\includegraphics[width = \linewidth]{figures/parallel_trend1b.pdf}
\caption[Foreign ownership and breadth between the treatment and control groups around brokerage closures]{\textbf{Foreign ownership and breadth between the treatment and control groups around brokerage closures}\newline\scriptsize This figure presents the evolution of the mean of firm-quarter observations of foreign ownership (\textit{FOR\_OWN}) in Panel A and foreign breadth (\textit{FOR\_BREADTH}) in Panel B during the twelve quarters (i.e. three years) before and after an exogenous decrease in analyst coverage due to the 22 distinct brokerage closures listed by Kelly and Ljungqvist (2012). I impose a three-month gap over the events so that foreign ownership estimates are from quarters -13:-1 and 1:13, with the brokerage closure occurring in the quarter 0. The sample consists of 1603 distinct treated firms and 3521 control firms. Control firms are matched using propensity score matching (nearest neighbor) that matches each treatment firm to three control firms by multiple covariates (twelve quarters before the event): logarithm of market capitalization (\textit{LOG\_MKT\_CAP}), book-to-market ratio (\textit{BM\_RATIO}) and number of distinct analysts covering the firm (\textit{ANALYST\_COVERAGE}). The firm-quarter observations of foreign ownership and foreign breadth are winsorized at the top and bottom 1\%. Sample period: 1997- 2010. Sources: CRSP, COMPUSTAT, 13F and IBES.}
\label{fig_parallel_trend1}
\end{figure}

As shown in Panel A, foreign ownership between the treatment and control groups follow an increasing but parallel trend before the event. This validates the assumption of pre-treatment parallel trend between treatment and control groups. However, there is no evidence of a post-treatment decline of foreign ownership in the treatment group or a significant post-treatment difference in mean between the two groups. Foreign ownership of both groups continue increasing, although the control group slightly catches the treatment group in the post-treatment period. Abrupt changes in foreign ownership during the event quarters 5 and 10 are largely caused by changes in foreign ownership during 2003. These changes are further illustrated in Figure XX in Appendix XX with event-specific plots.

Panel B provides the results of the evolution of foreign breadth between the treatment and control groups. Similar to Panel A, foreign breadth follows an increasing but parallel trend between the groups before the event, which validates the assumption of pre-treatment parallel trend. The increasing and parallel trend follows also after the event and there is no significant decrease in foreign ownership for the treatment group. There also no evidence of a significant post-treatment difference in mean between the two groups. Therefore, the results of Figure \ref{fig_parallel_trend1} do not support the second hypothesis that an exogenous increase in information asymmetry results in a decrease of foreign ownership. 

I extend the analysis of the quasi-experimental setting by implementing a difference-in-differences regression analysis of foreign ownership and foreign breadth. Compared to results in Figure \ref{fig_parallel_trend1}, this enables me to control for other variables and include year and industry fixed effects. 

``` {r, results='asis', echo = FALSE, eval=FALSE}

library(tidyverse)
library(lfe)
library(stargazer)

did_regression_matched1 <- read_rds("results/did_regression_matched1.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER)
did_regression_matched2 <- read_rds("results/did_regression_matched2.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER)
did_regression_matched3 <- read_rds("results/did_regression_matched3.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER)

did_model1 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model2 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model3 <- felm(FOR_OWN ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_model7 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model8 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model9 <- felm(FOR_BREADTH ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_list <- list(did_model1, did_model2, did_model3, did_model7, did_model8, did_model9)

stargazer(did_list, title = "\\textbf{Difference-in-differences regression analysis of foreign ownership and breadth}\\newline\\small This table reports the results of the difference-in-differences regression analysis of foreign ownership and breadth. The explanatory variables are \\textit{AFTER}.",
          label = "table_h2_1",
          header = F,
          dep.var.labels =c("FOR\\_OWN", "FOR\\_BREADTH"),
          column.labels = rep(c("-1:1 years", "-2:2 years", "-3:3 years"), times = 2),
          covariate.labels = c("AFTER", "TREATED", "AFTER\\texttimes TREATED", "BM\\_RATIO", "LEVERAGE", "ROA"),
          omit.stat = c("ser", "rsq"),
          add.lines = list(c("Industry fixed effects", rep("Yes", times = 6)),
                           c("Year fixed effects", rep("Yes", times = 6))),
          type = 'latex',
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          no.space = T)

```

\renewcommand\arraystretch{0.89}
\captionsetup{width=1.0\linewidth}
\begin{table}[htbp]
  \caption[Difference-in-differences regression analysis of foreign ownership and breadth]{\textbf{Difference-in-differences regression analysis of foreign ownership and breadth}\newline\small This table reports the results of the difference-in-differences regression analysis of foreign ownership and breadth. The sample consists of 1240 distinct treated stocks and 3500 distinct control firms, . The explanatory variables are \textit{AFTER}} 
  \label{table_h2_1} 
\small 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & \multicolumn{3}{c}{FOR\_OWN} & \multicolumn{3}{c}{FOR\_BREADTH} \\ 
 & -1:1 years & -2:2 years & -3:3 years & -1:1 years & -2:2 years & -3:3 years \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 AFTER & 0.009$^{***}$ & 0.013$^{***}$ & 0.016$^{***}$ & 0.001$^{**}$ & 0.001$^{***}$ & 0.002$^{***}$ \\ 
  & (0.003) & (0.004) & (0.003) & (0.0003) & (0.0002) & (0.0002) \\ 
  TREATED & 0.003$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ & 0.002$^{***}$ \\ 
  & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) & (0.001) \\ 
  AFTER\texttimes TREATED & $-$0.002$^{**}$ & $-$0.002 & $-$0.001 & $-$0.0002$^{*}$ & 0.00001 & 0.0002 \\ 
  & (0.001) & (0.002) & (0.001) & (0.0001) & (0.0002) & (0.0002) \\ 
  BM\_RATIO & $-$0.002 & $-$0.002 & $-$0.003$^{**}$ & $-$0.002$^{***}$ & $-$0.003$^{***}$ & $-$0.003$^{***}$ \\ 
  & (0.003) & (0.002) & (0.002) & (0.0003) & (0.0004) & (0.0004) \\ 
  LEVERAGE & 0.006 & 0.007$^{**}$ & 0.008$^{**}$ & 0.003$^{***}$ & 0.004$^{***}$ & 0.004$^{***}$ \\ 
  & (0.004) & (0.003) & (0.003) & (0.001) & (0.001) & (0.001) \\ 
  ROA & 0.095$^{***}$ & 0.111$^{***}$ & 0.122$^{***}$ & 0.020$^{**}$ & 0.025$^{***}$ & 0.026$^{***}$ \\ 
  & (0.034) & (0.029) & (0.030) & (0.009) & (0.009) & (0.008) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 17,138 & 18,067 & 18,560 & 17,138 & 18,067 & 18,560 \\ 
Adjusted R$^{2}$ & 0.342 & 0.363 & 0.362 & 0.390 & 0.402 & 0.411 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{7}{r}{} \\ 
\end{tabular} 
\end{table}

``` {r parallel_trend2, message = FALSE, warning=FALSE, eval=FALSE}

library(tidyverse)

parallel_trend1 <- read_rds("results/did_regression_matched_raw.rds") %>% 
  mutate(TREATED = if_else(TREATED == 1, "Treated", "Control")) %>% 
  group_by(TREATED, quarter_index) %>% 
  summarise(FOR_TO_INST_OWN = mean(FOR_TO_INST_OWN),
            FOR_TO_INST_BREADTH = mean(FOR_TO_INST_BREADTH)) %>% 
  ungroup()

ggplot(parallel_trend1, aes(quarter_index, FOR_TO_INST_OWN, color = TREATED)) +
  ggtitle("Panel A: Foreign-to-institution ownership") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend2a.pdf", 
       width = 8, height = 4, units = "in")

ggplot(parallel_trend1, aes(quarter_index, FOR_TO_INST_BREADTH, color = TREATED)) +
  ggtitle("Panel B: Foreign-to-institution breadth") +
  geom_line() +
  labs(x = "Event quarter", color = "") +
  geom_vline(xintercept=0) +
  theme_classic() +
  theme(plot.title = element_text(size=9, face="italic")) +
  scale_color_grey(start = 0.55, end = 0)

ggsave("figures/parallel_trend2b.pdf", 
       width = 8, height = 4, units = "in")
  
```

\begin{figure}[!htb]
\centering
\includegraphics[width = \linewidth]{figures/parallel_trend2a.pdf}
\includegraphics[width = \linewidth]{figures/parallel_trend2b.pdf}
\caption[Foreign-to-institution ownership and breadth between the treatment and control groups around brokerage closures]{\textbf{Foreign-to-institution ownership and breadth between the treatment and control groups around brokerage closures}\newline\scriptsize This figure presents the evolution of the mean of firm-quarter observations of foreign ownership (\textit{FOR\_OWN}) in Panel A and foreign breadth (\textit{FOR\_BREADTH}) in Panel B during the twelve quarters (i.e. three years) before and after an exogenous decrease in analyst coverage due to the 22 distinct brokerage closures listed by Kelly and Ljungqvist (2012). I impose a three-month gap over the events so that foreign ownership estimates are from quarters -13:-1 and 1:13, with the brokerage closure occurring in the quarter 0. The sample consists of 1603 distinct treated firms and 3521 control firms. Control firms are matched using propensity score matching (nearest neighbor) that matches each treatment firm to three control firms by multiple covariates (twelve quarters before the event): logarithm of market capitalization (\textit{LOG\_MKT\_CAP}), book-to-market ratio (\textit{BM\_RATIO}) and number of distinct analysts covering the firm (\textit{ANALYST\_COVERAGE}). The firm-quarter observations of foreign ownership and foreign breadth are winsorized at the top and bottom 1\%. Sample period: 1997- 2010. Sources: CRSP, COMPUSTAT, 13F and IBES.}
\label{fig_parallel_trend2}
\end{figure}


``` {r, results='asis', echo = FALSE, eval=FALSE}

library(tidyverse)
library(lfe)
library(stargazer)

did_regression_matched1 <- read_rds("results/did_regression_matched1.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER)
did_regression_matched2 <- read_rds("results/did_regression_matched2.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER)
did_regression_matched3 <- read_rds("results/did_regression_matched3.rds") %>%
  mutate(AFTER_TREATED = TREATED * AFTER)

did_model1 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model2 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model3 <- felm(FOR_TO_INST_OWN ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_model7 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched1)

did_model8 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched2)

did_model9 <- felm(FOR_TO_INST_BREADTH ~ AFTER + TREATED + AFTER_TREATED + BM_RATIO +
                     LEVERAGE + ROA|year + sic_code|0|year + sic_code,
                   data = did_regression_matched3)

did_list <- list(did_model1, did_model2, did_model3, did_model7, did_model8, did_model9)

stargazer(did_list, title = "\\textbf{Difference-in-differences regression analysis of foreign-to-institutions ownership and breadth}\\newline\\small This table reports the results of the difference-in-differences regression analysis of foreign-to-institution ownership and breadth. The explanatory variables are \\textit{AFTER}.",
          label = "table_h2_2",
          header = F,
          dep.var.labels =c("FOR\\_TO\\_INST\\_OWN", "FOR\\_TO\\_INST\\_BREADTH"),
          column.labels = rep(c("-1:1 years", "-2:2 years", "-3:3 years"), times = 2),
          covariate.labels = c("AFTER", "TREATED", "AFTER\\texttimes TREATED", "BM\\_RATIO", "LEVERAGE", "ROA"),
          omit.stat = c("ser", "rsq"),
          add.lines = list(c("Industry fixed effects", rep("Yes", times = 6)),
                           c("Year fixed effects", rep("Yes", times = 6))),
          type = 'latex',
          notes.label = "",
          notes.append = F,
          notes = "",
          font.size = "small",
          no.space = T)

```

\renewcommand\arraystretch{0.89}
\captionsetup{width=1.0\linewidth}
\begin{table}[htbp]
  \caption[Difference-in-differences regression analysis of foreign-to-institution ownership and breadth]{\textbf{Difference-in-differences regression analysis of foreign-to-institution ownership and breadth}\newline\small This table reports the results of the difference-in-differences regression analysis of foreign-to-institution ownership and breadth. The sample consists of 1601 distinct treated stocks and 3500 distinct control firms, . The explanatory variables are \textit{AFTER}} 
  \label{table_h2_2} 
\small 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & \multicolumn{3}{c}{FOR\_TO\_INST\_OWN} & \multicolumn{3}{c}{FOR\_TO\_INST\_BREADTH} \\ 
 & -1:1 years & -2:2 years & -3:3 years & -1:1 years & -2:2 years & -3:3 years \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 AFTER & 0.007$^{**}$ & 0.010$^{*}$ & 0.013$^{***}$ & 0.004 & 0.009$^{*}$ & 0.014$^{***}$ \\ 
  & (0.004) & (0.006) & (0.004) & (0.005) & (0.005) & (0.005) \\ 
  TREATED & 0.0001 & $-$0.0005 & $-$0.001 & $-$0.002 & $-$0.001 & $-$0.001 \\ 
  & (0.002) & (0.002) & (0.002) & (0.002) & (0.002) & (0.001) \\ 
  AFTER\texttimes TREATED & $-$0.003$^{***}$ & $-$0.002 & $-$0.001 & 0.001 & 0.001 & 0.001 \\ 
  & (0.001) & (0.002) & (0.002) & (0.001) & (0.002) & (0.002) \\ 
  BM\_RATIO & 0.001 & 0.001 & $-$0.002 & 0.002 & $-$0.0002 & $-$0.001 \\ 
  & (0.003) & (0.002) & (0.002) & (0.001) & (0.002) & (0.002) \\ 
  LEVERAGE & $-$0.006 & $-$0.003 & $-$0.002 & 0.003 & 0.003 & 0.003 \\ 
  & (0.008) & (0.007) & (0.007) & (0.005) & (0.005) & (0.005) \\ 
  ROA & $-$0.00003 & 0.014 & 0.016 & $-$0.046$^{**}$ & $-$0.040 & $-$0.041 \\ 
  & (0.047) & (0.038) & (0.037) & (0.020) & (0.025) & (0.028) \\ 
 \hline \\[-1.8ex] 
Industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 17,138 & 18,067 & 18,560 & 17,138 & 18,067 & 18,560 \\ 
Adjusted R$^{2}$ & 0.235 & 0.255 & 0.249 & 0.322 & 0.340 & 0.352 \\ 
\hline 
\hline \\[-1.8ex] 
\multicolumn{7}{r}{} \\ 
\end{tabular} 
\end{table}


\newpage

\addcontentsline{toc}{section}{References}

# References
